
<!-- This .Rmd file is set up to run either independently by checking for 
the presence of necessary objects in the global environment and running 
related scripts if not, or also as a child to the "main-doc". For that latter
reason, comments and headings that are not relevant to a final report to
pubic audiences are suppressed or moved to code chunks that can optionally be 
`echo`ed as desired. -->

```{r}
# run scripts for necessary packages and objects as necessary
if (!"meanNA"        %in% objects()) source("settings--main.R", echo = FALSE)
if (!"my_state_abbr" %in% objects()) source("method--read-customization-file.R", echo = FALSE)
if (!"bin_age"       %in% objects()) source("method--general-helper-functions.R", echo = FALSE)
if (!"calc_cps_transitions" %in% objects()) source_rmd("method--nowcasting-functions.Rmd", echo = FALSE)
```

```{r load data for now-casting run}
# Load prepped data
for (f in c("geo", "cps", "acs5", "pop")) {
  load(file = glue("{output_path}{f}_data_{my_output_tag}.Rda"))
}

# Load SAE estimates
load(file = glue("{output_path}sae_sensitivity_estimates_{my_output_tag}.Rda")) 
```


## Implement the Now-Casting Method

This method considers community factors of households for predicting potential transition into eligibility status. In addition to accounting for "vulnerability" factors such as baseline poverty status, this method can also consider factors like education, race/ethnicity, or general industries employing local workers.

While the SAE method is limited in how much detail it can estimate for 2019 with validity, this method uses other measures by assuming that ACS 5-year measures are applicable to 2019. For some measures like adult educational attainment and race/ethnicity, we believe that this assumption is defensible.


```{r develop select subsets of cps pre-post data for use}

recent_cps_months <- 
  cps_trans %>% 
  pull(YEAR_MONTH_p) %>% 
  setdiff("NA-NA") %>% 
  unique() %>% 
  sort(decreasing = TRUE)

most_recent_months <- 
  recent_cps_months %>% 
  .[1:3]

# This is an expansion currently targeted for running mid-summer when seeking
# CPS post-period status aligned with roughly the school year.
# /!\ Refinements are anticipated and welcome.
last_september_i <- match(glue("{base_year+1}-09"), recent_cps_months)
most_recent_sy_months <- 
  recent_cps_months %>% 
  .[1:last_september_i]

cps_reg_sample_most_recent    <- filter(cps_trans, YEAR_MONTH_p %in% most_recent_months)
cps_reg_sample_most_recent_sy <- filter(cps_trans, YEAR_MONTH_p %in% most_recent_sy_months)
cps_reg_sample_allbase        <- filter(cps_trans, YEAR == base_year)

```

```{r pivot SAE measures wide}
# Reshape the SAE data wide for the sake of prediction
# Preserve only the values needed for now-casting:
# - tract
# - value of the SAE category predicted to that level
# - estimated share
# This is reshaped wide for each value to be used in prediction, when applying 
# coefficients estimated via analysis of CPS

pivot_sae_wide <- function(sae_spec, share_var) {
  sae_spec[["sae_out_decompress"]] %>% 
    select(
      all_of(c("GEOID", "vc_value", share_var))
    ) %>% 
    mutate(
      vc_value = paste0("share_", vc_value) %>% 
        str_replace_all("%|\\+", "") %>% 
        str_replace_all("-", "_")
    ) %>%
    pivot_wider(
      id_cols = c("GEOID"), 
      names_from = vc_value, 
      values_from = share_var
    )
}
```

```{r develop list of predictors for transition/now-casting}

# Set control lists

# /!\ Other predictors to consider building include:
# - labor force participation
# - employment status
# - race/ethnicity and
# - industry of employment

# These are all fields relevant to predicting post-period status

sae_controls_workstatus <- 
  c("rEmpl_Male", "rEmpl_Female",
    "rUnmarriedFemaleHh", "rUnmarriedMaleHh")

transition_pred_vars_acs5 <- 
  c("rEduc_LtHs", "rEduc_SomeColl", "rEduc_Coll", "rEduc_Grad",
    "rUnmarriedFemaleHh", "rUnmarriedMaleHh")

# Set reference group categories
transition_pred_vars_toomit <- 
  c("rEduc_Hs", "rMarried")
  # These values are removed because they are colinear with other predictors
  # However, in some specifications we add them back in and remove the intercept
  # to, in effect, estimate average levels associated with each stats.

stopifnot(
  all(
    c(sae_controls_workstatus, transition_pred_vars_acs5, transition_pred_vars_toomit) %in%
    colnames(acs5tract)
  )
)
```

```{r subset acs 5-year data that is relevant based on the specification}

# Subset to variables selected for "now"-casting, as well as SAE measures
# for later reference
acs5_keep_vars <- 
  c("GEOID", "COUNTYFIP",
    #"nAge0to19", "nAge20to64", "nAge65plus",
    # /!\ Removing age data, since population counts are merged in separately
    transition_pred_vars_acs5, transition_pred_vars_toomit,
    sae_controls_list) %>% 
  unlist() %>% 
  unique()

acs5tract_reg <- 
  acs5tract %>% 
  select(all_of(acs5_keep_vars))

if (exists("my_county_fip")) {
  acs5tract_reg <- 
    acs5tract_reg %>% 
    filter(
      COUNTYFIP == my_county_fip
    )
}
```

```{r subset population data to useful content}
pop_for_nowcast <- 
  pop_age_t_calib_wide %>% 
  select(GEOID, 
         # nAge0to19, nAge20to64, 
         nAge0to18, nAge19to25, nAge26to44, nAge45to64,
         nAge65plus) %>% 
  mutate(
    # nAge0to19_se  = 0,
    # nAge20to64_se = 0,
    nAge0to18_se  = 0,
    nAge19to25_se = 0,
    nAge26to44_se = 0,
    nAge45to64_se = 0,
    nAge65plus_se = 0
  )
  
```


```{r set a function for estimating a single run of transition estimation}
estimate_transition_counts <- 
  function(
    sae_spec_name, 
    share_calc_var, 
    outcome_var, 
    transition_data, 
    age_prefix,
    work_field = "bWork_metHrsThresh_elig",
    spouse_field = "bSpousePresent"
      # /*\ The default for these last two arguments may be worth examining, and/or
      # adjusting via function calls in the implementation
    ) {
   
  sae_wide <- 
    pivot_sae_wide(
      get(sae_spec_name),
      share_calc_var
    )
  
  # Ensure that the fields in the sae data are represented in the cps data
  vc_vals <- cn(sae_wide) %>% setdiff("GEOID")
  for (vc_val in vc_vals) {
    
    # Extract work information if present
    cWork <- str_extract(vc_val, "(_WorkElig|NotWorkElig)")
    
    # Extract spouse information if present
    cSpouse <- str_extract(vc_val, "(_SpousePresent|NoSpousePresent)")
    
    # Extract all incpov information if present
    # If `prog` is mentioned, we take it to refer to the base program eligibility
    # threshold, and replace it with that information that the user has specified
    vIncpov <- str_extract_all(vc_val, "\\d+|prog") %>% unlist()
    vIncpov[vIncpov == "prog"] <- as.character(local_prog_incratio_base)
    vIncpov <- as.numeric(vIncpov)
    
    # Build program eligibility 
    # At present, this code rebuilds flags for eligibility in the `cps_trans`
    # data that parallel the SAE fields (and thus the category encodings from the)
    # ACS1 data, using the name
    # /!\ It may be worth considering whether this approach or requiring a parallel
    # construction more intentionally built in the CPS data transform code is
    # more desirable ... the approach is relatively more preferable, the more that
    # the CPS (and ACS1) builds are automated, e.g. to the extent that user
    # input sets the build of categorizations without need for user input
    transition_data <- 
      transition_data %>% 
      .[j = c(vc_val) := 
          # Build work eligibility qualifier if indicated
          case_when(
            is.na(cWork)              ~ 1,
            str_detect(cWork, "Not")  ~ 1 - get(work_field),
            TRUE                      ~     get(work_field)
          ) *
          
          # Build presence of spouse if indicated
          case_when(
            is.na(cSpouse)            ~ 1,
            str_detect(cSpouse, "No") ~ 1 - get(spouse_field),
            TRUE                      ~     get(spouse_field)
          ) *
          
          # Note: 01b bins income using [lower, upper) inclusions -- i.e., 
          # closed lower limit, open upper. We do this by hand because between()
          # uses closed lower and upper (likely a very small point).
          case_when(
            length(vIncpov) == 0 ~  1,
            length(vIncpov) == 1 ~  fam_incpov_ratio_b*100 >= vIncpov[1],
            TRUE                 ~ (fam_incpov_ratio_b*100 >= vIncpov[1])*(fam_incpov_ratio_b*100 < vIncpov[2])
          )]
      
  }
  
  # Check constructions
  if (FALSE) {
    vc_val <- "share_0_50"
    # <run the above>
    transition_data[j = .N, by = .(fn = share_0_50, hand = 1*(fam_incpov_ratio_b <= .5))] %>% unique()
    
    vc_val <- "share_WorkElig_100_ccdf"
    # <run the above>
    transition_data[j = .N, by = .(fn = share_WorkElig_100_ccdf, hand = 1*(ccdf_elig_loose)*between(fam_incpov_ratio_b, 1, local_ccdf_incratio_base/100))] %>% unique()
    
    vc_val <- "share_NotWorkElig_400"
    # <run the above>
    transition_data[j = .N, by = .(fn = share_NotWorkElig_400, hand = 1*(!ccdf_elig_loose)*(fam_incpov_ratio_b >= 4))] %>% unique()
    
    vc_val <- "share_NotWorkElig_SpousePresent"
    # <run the above>
    transition_data[j = .N, by = .(fn = share_NotWorkElig_SpousePresent, hand = 1*(!ccdf_elig_loose)*(spouse_present))] %>% unique()
  }
   
  # Merge ACS5-derived predictors into the input SAE data 
  pred_data <- 
    sae_wide %>% 
    merge(
      acs5tract_reg,
      by = "GEOID",
      all.x = TRUE
    ) %>% 
    # Merge in population data not already found in the ACS5 data
    merge(
      pop_for_nowcast %>% 
        select(
          all_of(
            c("GEOID", 
              setdiff(cn(pop_for_nowcast), cn(acs5tract_reg))
            )
          )
        ),
      by = "GEOID",
      all.x = TRUE
    ) %>%
    merge(
      geo_crosswalk[j = .(GEOID, PUMA)] %>% unique(),
      by = "GEOID",
      all.x = TRUE
    ) %>% 
    data.table()
  
  pred_controls <- 
    c(transition_pred_vars_acs5,
      vc_vals
    ) %>% 
    unique() %>% 
    setdiff(transition_pred_vars_toomit)
  
  est_apply_trans(
    cps_trans_data  = transition_data,
    outcome_var     = outcome_var,
    pred_vars       = pred_controls,     
    vars_for_uncond = setdiff(vc_vals, transition_pred_vars_toomit),
    sae_acs5_vals   = pred_data, 
    count_var       = glue("{age_prefix}"),     
    count_se_var    = glue("{age_prefix}_se")
  )
  
}
```

For each count category of deep poverty, in poverty (i.e. Head Start eligibility), below 200% FPL, and `r local_ccdf_name_short`-eligibility, we implement sensitivities across:

1. Selection of CPS Cohorts -- those in line with the full base year, versus the most recent data from the three most recent monthly cohorts
2. Samples of geography of CPS households -- subsetting by those in metro areas, versus no subsampling
3. Various specifications of the SAE method, including separate implementations by age of children

```{r implement now-casting and harvest prediction outputs}

nowcast_out <- NULL
nowcast_betas_out <- NULL

# Loop across CPS 
for (cps_recency in c("most_recent", "allbase")) { # , "sy"
  
  # Note: unlike `case_match()`, the RHS of the conditions can return an
  # object that doesn't conform to the first argument
  cps_reg_data <- 
    switch(
      cps_recency,
      "most_recent" = cps_reg_sample_most_recent,
      "sy"          = cps_reg_sample_most_recent_sy,
      "allbase"     = cps_reg_sample_allbase
    )
  
  # Loop across CPS subsamples
  for (cps_geo_subsample in c("none", "metros")) {
    
    # Select subsample of CPS data, if applicable
    cps_reg_data_sample <- 
      switch(
        cps_geo_subsample,
        "none"   = cps_reg_data,
        "metros" = cps_reg_data[METRO %in% 2:4]
      )
    
    for (sae_spec in specs) {
      
      # Determine which outcomes to run with each SAE sensitivity specification.
      # We may want to be more selective, given both run-times and sensibilities
      # around modeling choices.
      # `age_prefix` is used for both acs5 and population data
      
      ages <- str_extract(sae_spec, "\\d+")
      if (ages == "019") {
        age_prefix <- "nAge0to19"
        cps_reg_use <- filter(cps_reg_data_sample, between(AGE,  0, 19))
        
      } else if (ages == "2064") {
        age_prefix <- "nAge20to64"
        cps_reg_use <- filter(cps_reg_data_sample, between(AGE, 20, 64))
        
      } else if (ages == "018") {
        age_prefix <- "nAge0to18"
        cps_reg_use <- filter(cps_reg_data_sample, between(AGE,  0, 18))
        
      } else if (ages == "1925") {
        age_prefix <- "nAge19to25"
        cps_reg_use <- filter(cps_reg_data_sample, between(AGE, 19, 25))
        
      } else if (ages == "2644") {
        age_prefix <- "nAge26to44"
        cps_reg_use <- filter(cps_reg_data_sample, between(AGE, 26, 44))
        
      } else if (ages == "4564") {
        age_prefix <- "nAge45to64"
        cps_reg_use <- filter(cps_reg_data_sample, between(AGE, 45, 64))
        
      } else if (ages == "65plus") {
        age_prefix <- "nAge65plus"
        cps_reg_use <- filter(cps_reg_data_sample, AGE >= 65)
      }
      
      share_calc_var_use <- 
        ifelse(
          use_only_sae_model_estimates,
          "share_model_redis_pct01_infl",
          "share_fh_redis_pct01_infl"
        )
      
      if (str_detect(sae_spec, "inc$")) {
        # Using the poverty estimates to predict poverty-related eligibility, 
        # as well as CCDF eligibility because why not. Also there's reason to 
        # believe that more parsimonious specifications may do better.
        outcome_vars <- 
          c(
            "bIncpov_le130", 
            "bIncpov_le138", 
            "bIncpov_le205"
          )
        
      } else if (str_detect(sae_spec, "incwork$")) {
        outcome_vars <- str_subset(cn(cps_reg_use), "bProg_eligThresh_incpov_")
      }
    
      for (outcome_var in outcome_vars) {

        # print(glue("Running CPS recency {cps_recency}, CPS geo subsample {cps_geo_subsample}, ",
        #            "sae_spec {sae_spec}, outcome variable {outcome_var}"))
        
        # browser() 
        count_est_output <- 
          estimate_transition_counts(
            sae_spec_name   = glue("sae_results_{sae_spec}"),
            share_calc_var  = share_calc_var_use,
            outcome_var     = outcome_var,
            transition_data = cps_reg_use,
            age_prefix      = age_prefix
          )
        
        add_run_details <- function(x) {
          mutate(
            x,
            sae_spec          = sae_spec,
            cps_base_recency  = cps_recency,
            cps_geo_subsample = cps_geo_subsample,
            outcome_var       = outcome_var
          )
        }
        
        # Collect count estimates
        nowcast_out <-
          bind_rows(
            nowcast_out,
            add_run_details(count_est_output[[1]])
          )
        
        # Collect betas
        nowcast_betas_out <- 
          bind_rows(
            nowcast_betas_out,
            add_run_details(count_est_output[[2]])
          )
        
      } # end loop across outcomes
    } # end loop across SAE specifications
  } # end loop across cps geo subsample
} # end loop across cps recency

nowcast_betas_out <- data.table(nowcast_betas_out)
```

```{r reorganize metadata in the nowcast output}
nowcast_out_labeled <- 
  nowcast_out %>% 
  mutate(
    age = str_extract(sae_spec, "\\d+"),
    age = 
      case_match(
        age,
        "019"    ~ "Age0to19",
        "2064"   ~ "Age20to64",
        
        "018"    ~ "Age0to18",
        "1925"   ~ "Age19to25",
        "2644"   ~ "Age26to44",
        "4564"   ~ "Age45to64",
        "65plus" ~ "Age65plus"
      ),
    sae_spec = str_replace(sae_spec, "\\d+_", "")
  )
```

```{r examine share estimates outside of [0.0-1.0] and truncate}
if (developer_mode) {
  # Examine frequency of 
  nowcast_out_labeled %>% 
    summarize(
      .by = c(sae_spec, outcome_var),
      elig_share_lt0 = mean(elig_share < 0) %>% percent(accuracy = .1),
      elig_share_gt1 = mean(elig_share > 1) %>% percent(accuracy = .1)
    )
  
  # Examine magnitude of negative share estimates
  nowcast_out_labeled %>% 
    filter(elig_share < 0) %>% 
    select(elig_share) %>% 
    summary()
  
  # Visually examine which SAE and ACS5 values are associated with negative
  # estimates
  nowcast_out_labeled %>% 
    filter(elig_share < 0) %>% 
    View()
    # From a quick look, it simply seems that this is the case for tracts with 
    # very high shares of high income (>400% FPL) households
}

nowcast_out_trunc <- 
  nowcast_out_labeled %>% 
  mutate(
    elig_count = ifelse(elig_share < 0, 0, elig_count),
    elig_share = ifelse(elig_share < 0, 0, elig_share)
  )
  # Standard errors are preserved given the very small adjustment of negative
  # values to zero. And although non-0 standard errors are not well behaved,
  # they are preserved given that they are necessary to reflect noise when
  # these values are aggregated up.
  
```



```{r save final results from now-casting}
# Pull out key information of now-casting output from the larger set of output
# which has more contextual fields
key_nowcast_out <- 
  nowcast_out_trunc %>% 
  select(
    GEOID, outcome_var, 
    elig_share, elig_share_se, 
    elig_count, elig_count_se,
    sae_spec, cps_base_recency, cps_geo_subsample
  )

save(
  key_nowcast_out,
  nowcast_out_trunc,
  nowcast_betas_out,
  most_recent_months,
  most_recent_sy_months,
  file = glue("{output_path}Eligibility estimates using conditional transition ratio - {my_output_tag}.Rda")
)
```

<!-- ### Examine Estimated Betas from the Now-Casting -->

<!-- We next examine estimated parameters from analysis of post-period measures the CPS. -->

<!-- ```{r function to compare conditional and unconditional betas} -->
<!-- compare_betas <- function(betas, title, subtitle, comp_var, comp_var_label, print_table = FALSE, save_tag = "") { -->
<!--   if (print_table) { -->
<!--     betas %>%  -->
<!--       arrange(trans_spec) %>%  -->
<!--       transmute( -->
<!--         Term = term,  -->
<!--         `Comp Var` = get(comp_var), -->
<!--         Estimate = round(estimate, 3), -->
<!--         `p-value` = round(p.value, 4) -->
<!--       ) %>%  -->
<!--       kable() %>%  -->
<!--       print() -->
<!--   }   -->

<!--   if ("uncond" %in% betas$trans_spec) { -->
<!--     common_vars <-  -->
<!--       betas %>%  -->
<!--       filter(trans_spec == "uncond") %>%  -->
<!--       pull(term) %>%  -->
<!--       unique()   -->
<!--     betas <-  -->
<!--       filter(betas, -->
<!--              term %in% common_vars) -->
<!--   } -->

<!--   betas <-  -->
<!--     betas %>%  -->
<!--     mutate(var_label = label_vars(term)) -->

<!--   my_plot <- -->
<!--     betas %>%  -->
<!--     ggplot( -->
<!--       aes_string( -->
<!--         x = "var_label", -->
<!--         y = "estimate", -->
<!--         fill = comp_var) -->
<!--     ) + -->
<!--     geom_bar( -->
<!--       stat = "identity", -->
<!--       position = "dodge" -->
<!--     ) + -->
<!--     geom_errorbar( -->
<!--       aes( -->
<!--         ymin = estimate - 1.96*std.error, -->
<!--         ymax = estimate + 1.96*std.error -->
<!--       ), -->
<!--       width = 0.1, -->
<!--       position = position_dodge(.9) -->
<!--     ) + -->
<!--     scale_fill_discrete( -->
<!--       name = comp_var_label -->
<!--       # breaks = c("cond", "uncond"), -->
<!--       # labels = c("Conditional", "Unconditional") -->
<!--     ) + -->
<!--     labs( -->
<!--       title = title, -->
<!--       subtitle = subtitle, -->
<!--       x = "", -->
<!--       y = "Estimated Coefficient" -->
<!--     ) + -->
<!--     coord_flip() +  -->
<!--     theme_minimal() + -->
<!--     theme( -->
<!--       axis.text = element_text(size = 11), -->
<!--       legend.position = "bottom" -->
<!--     ) -->

<!--   if (save_tag != "") { -->
<!--     ggsave( -->
<!--       plot = my_plot,  -->
<!--       filename = glue("{output_path}nowcasting_coefficients_{my_output_tag}_{save_tag}.png") -->
<!--     ) -->
<!--   } -->

<!--   return(my_plot) -->

<!-- } -->
<!-- ``` -->

<!-- Comparing conditional vs unconditional estimates of SAE measures. -->

<!-- ```{r compare now-casting betas, results = "asis"} -->
<!-- compare_betas( -->
<!--   betas =  -->
<!--     filter( -->
<!--       nowcast_betas_out, -->
<!--       outcome_var       == "incpov_le100_post_adj", -->
<!--       sae_spec          == "incpov_ctrls_mix_05", -->
<!--       cps_base_recency  == "most_recent", -->
<!--       cps_geo_subsample == "none" -->
<!--     ), -->
<!--   title = "Now-Casting Coefficients Predicting Head Start Elig: Conditional vs Unconditional", -->
<!--   comp_var = "trans_spec", -->
<!--   comp_var_label = "Control Specification" -->
<!-- ) -->
<!-- # Note -- this has limited value, since the choice of reference values for the -->
<!--   # conditional drives the comparison. This machinery may be more worth examining -->
<!--   # results for the same regression specification, but with different CPS subsets -->

<!-- compare_betas( -->
<!--   betas =  -->
<!--     filter( -->
<!--       nowcast_betas_out, -->
<!--       outcome_var      == "incpov_le100_post_adj", -->
<!--       sae_spec         == "incpov_ctrls_mix_05", -->
<!--       cps_base_recency == "most_recent", -->
<!--       trans_spec       == "cond" -->
<!--     ), -->
<!--   title = "Now-Casting Coefficients Predicting Head Start Elig: Comparison Across CPS Subsets", -->
<!--   subtitle = case_when(my_output_tag == "IL" ~ "", -->
<!--                        TRUE ~ ""), -->
<!--   comp_var = "cps_geo_subsample", -->
<!--   comp_var_label = "CPS Geographic Subset", -->
<!--   save_tag = "hs_comp-geo-subset" -->
<!-- ) -->

<!-- compare_betas( -->
<!--   betas =  -->
<!--     filter( -->
<!--       nowcast_betas_out, -->
<!--       outcome_var       == "incpov_le100_post_adj", -->
<!--       sae_spec %in% c("incpov_ctrls_mix_05", "incpov_ctrls_mix_612"), -->
<!--       cps_base_recency  == "most_recent", -->
<!--       cps_geo_subsample == "none", -->
<!--       trans_spec        == "cond" -->
<!--     ), -->
<!--   title = "Now-Casting Coefficients Predicting Head Start Elig: Comparison Across Estimation for 0-5 vs 6-12", -->
<!--   subtitle = case_when(my_output_tag == "IL" ~ "", -->
<!--                        TRUE ~ ""), -->
<!--   comp_var = "sae_spec", -->
<!--   comp_var_label = "Age", -->
<!--   save_tag = "hs_comp-age05-vs-612" -->
<!-- ) -->

<!-- compare_betas( -->
<!--   betas =  -->
<!--     filter( -->
<!--       nowcast_betas_out, -->
<!--       outcome_var       == "incpov_le100_post_adj", -->
<!--       sae_spec          == "incpov_ctrls_mix_05", -->
<!--       cps_geo_subsample == "none", -->
<!--       trans_spec        == "cond" -->
<!--     ), -->
<!--   title = "Now-Casting Coefficients Predicting Head Start Elig: Comparison Across CPS Recency", -->
<!--   subtitle = case_when(my_output_tag == "IL" ~ "", -->
<!--                     TRUE ~ ""), -->
<!--   comp_var = "cps_base_recency", -->
<!--   comp_var_label = "CPS Base Recency", -->
<!--   save_tag = "hs_comp-cps-recency" -->
<!-- ) -->

<!-- compare_betas( -->
<!--   betas =  -->
<!--     filter( -->
<!--       nowcast_betas_out, -->
<!--       outcome_var       == glue("ccdf_elig_incratio_{local_ccdf_incratio_base}"), -->
<!--       sae_spec          == "ccdf_wk_pov_05", -->
<!--       cps_geo_subsample == "none", -->
<!--       trans_spec        == "cond" -->
<!--     ), -->
<!--   title = "IL" ~ "Comparison of Estimated CCDF Now-Casting Coefficients Across CPS Recency", -->
<!--   subtitle = case_when(my_output_tag == "IL" ~ "", -->
<!--                     TRUE ~ ""), -->
<!--   comp_var = "cps_base_recency", -->
<!--   comp_var_label = "CPS Base Recency", -->
<!--   save_tag = "ccdf_comp-base-recency" -->
<!-- ) -->
<!-- ``` -->


<!-- ### Examine Sensitivities via Direct Examination of Estimates -->

<!-- ```{r generate functions for building and plotting comparisons of share estimates} -->

<!-- keep_cols <- c("GEOID", "cps_base_recency", "cps_geo_subsample", "sae_spec", "outcome_var") -->

<!-- build_trans_sensitivity_comp <- function(data, comp_col, base_val) { -->

<!--   # Note: we compare shares rather than counts, because the former is more directly -->
<!--   # model-related. The latter can get swamped by different sizes of tracts (and -->
<!--   # thus inflate correlations). -->
<!--   data_sub <- data[j = c(keep_cols, "elig_share", "elig_share_se"), -->
<!--                    with = FALSE] -->

<!--   data_left <-  -->
<!--     data_sub[get(comp_col) == base_val] %>%  -->
<!--     select(-comp_col) %>%  -->
<!--     rename(elig_base    = elig_share, -->
<!--            elig_base_se = elig_share_se) %>%  -->
<!--     mutate(base = glue("{comp_col} == {base_val}")) -->

<!--   comp <-  -->
<!--     data_left %>%  -->
<!--     merge(data_sub[get(comp_col) != base_val]) %>%  -->
<!--     .[j = `:=`(diff    = elig_share - elig_base, -->
<!--                diff_se = sqrt(elig_share_se^2 + elig_base_se^2))] -->

<!--   return(comp) -->
<!-- } -->

<!-- plot_trans_sensitivity_comp <- function(data, comp_col, base_val) { -->

<!--   comp <- build_trans_sensitivity_comp(data, comp_col, base_val) -->

<!--   comp %>%  -->
<!--     ggplot( -->
<!--       aes( -->
<!--         x = elig_base, -->
<!--         y = elig_share) -->
<!--     ) + -->
<!--     geom_point( -->
<!--       alpha = 0.1 -->
<!--     ) + -->
<!--     geom_abline( -->
<!--       color = "blue" -->
<!--     ) + -->
<!--     scale_x_continuous( -->
<!--       labels = percent -->
<!--     ) + -->
<!--     scale_y_continuous( -->
<!--       labels = percent -->
<!--     ) + -->
<!--     facet_wrap( -->
<!--       as.formula(glue("~ {paste(setdiff(keep_cols, 'GEOID'), collapse = ' + ')}")) -->
<!--     ) + -->
<!--     labs( -->
<!--       x = base_val -->
<!--     ) + -->
<!--     theme_minimal() -->

<!-- } -->
<!-- ``` -->

<!-- ```{r compare SAE specifications for HS prediction} -->
<!-- plot_trans_sensitivity_comp( -->
<!--   nowcast_out[outcome_var == "incpov_le100_post_adj" & cps_base_recency == "most_recent" & age == "age_0to5"], -->
<!--   comp_col = "sae_spec", -->
<!--   base_val = "incpov_ctrls_mix") + -->
<!--   labs( -->
<!--     x = "Full Income/Poverty Controls, with Employment Adjustment", -->
<!--     y = "Comparison Share Estimate" -->
<!--   ) -->
<!-- ``` -->

<!-- ```{r compare SAE specifications for CCAP prediction} -->
<!-- # plot_trans_sensitivity_comp(nowcast_out[outcome_var == glue("ccdf_elig_incratio_{local_ccdf_incratio_base}") & age == "age_0to5"], -->
<!-- #                             comp_col = "sae_spec", -->
<!-- #                             base_val = "ccdf_wk_pov") + -->
<!-- #   labs(title = case_when(my_output_tag == "IL" ~ "For CCDF Eligibility, Work and Spouse Specification consistently produces lower estimates", -->
<!-- #                          TRUE ~ ""), -->
<!-- #        x = "Specification: Work and Poverty", -->
<!-- #        y = "Specification: Work and Spouse Present") -->
<!-- ``` -->

<!-- ```{r compare CPS subsetting sensitivity for HS prediction - spec 1} -->
<!-- plot_trans_sensitivity_comp(nowcast_out[outcome_var == "incpov_le100_post_adj" & sae_spec == "incpov_ctrls_mix" & age == "age_0to5"], -->
<!--                             comp_col = "cps_geo_subsample", -->
<!--                             base_val = "none") + -->
<!--   labs(title = case_when(my_output_tag == "IL" ~ "For Head Start, Sensitivities Seem Reasonably Consistent, Except for Simplest Spec", -->
<!--                          TRUE ~ ""), -->
<!--        x = "No CPS Subsampling", -->
<!--        y = "Use of only Metro Areas in CPS") -->
<!-- ``` -->

<!-- ```{r compare CPS subsetting sensitivity for HS prediction - spec 2} -->
<!-- plot_trans_sensitivity_comp(nowcast_out[outcome_var == "incpov_le100_post_adj" & sae_spec == "incpov_ctrls_mix" & age == "age_0to5"], -->
<!--                             comp_col = "cps_base_recency", -->
<!--                             base_val = "most_recent") + -->
<!--   labs(title = case_when(my_output_tag == "IL" ~ "For HS, Using the 2020 Baseline yields 25% lower eligibility estimates", -->
<!--                          TRUE ~ ""), -->
<!--        x = "Use of Most Recent CPS Months", -->
<!--        y = "Use of CPS 2020 Baseline") -->
<!-- ``` -->

<!-- ```{r check correlations between SAE specifications for each other sensitivity} -->
<!-- comp_sae <-  -->
<!--   build_trans_sensitivity_comp(nowcast_out[age == "age_0to5"], -->
<!--                                comp_col = "sae_spec", -->
<!--                                base_val = "incpov_ctrls_mix") -->

<!-- comp_sae[j = .(rho = cor(elig_base, elig_share)), -->
<!--          by = .(sae_spec, outcome_var, cps_base_recency, cps_geo_subsample)] %>%  -->
<!--   .[order(rho)] -->
<!-- ``` -->

<!-- ```{r scatterplot of differences and errors across specifications} -->
<!-- ggplot(comp_sae[cps_base_recency == "most_recent" & cps_geo_subsample == "none"], -->
<!--        aes(x = elig_base, -->
<!--            y = diff, -->
<!--            color = sae_spec)) + -->
<!--   geom_point() + -->
<!--   geom_errorbar(aes(ymin = diff - 1.96*diff_se, -->
<!--                     ymax = diff + 1.96*diff_se), -->
<!--                 width = .1) + -->
<!--   geom_hline(yintercept = 0) + -->
<!--   facet_wrap(~ sae_spec + outcome_var) + -->
<!--   labs(x = "Base Estimate", -->
<!--        y = "Diff: Spec vs Base", -->
<!--        title = case_when(my_output_tag == "IL" ~ "", -->
<!--                          TRUE ~ ""), -->
<!--        subtitle = "For most recent CPS cohorts") + -->
<!--   theme_minimal() + -->
<!--   theme(legend.position = "bottom") -->
<!-- ``` -->


<!-- <!-- By outcome and method, which are statistically different from the "by 100%" with detailed controls? --> -->

<!-- ```{r calculate percent of statistical differences between methods} -->
<!-- comp_sae[j = .(pct_diff_stat_sig = mean(abs(diff/diff_se) > 1.96) %>% percent()), -->
<!--                      by = .(sae_spec, outcome_var, cps_base_recency, cps_geo_subsample)] -->
<!-- ``` -->

<!-- <!-- How do the methods compare with respect to standard errors? --> -->

<!-- ```{r} -->
<!-- ggplot(comp_sae, -->
<!--        aes(x = sae_spec, -->
<!--            y = elig_share_se, -->
<!--            color = sae_spec)) + -->
<!--   #geom_violin() + -->
<!--   geom_boxplot() + -->
<!--   facet_grid(~ outcome_var, -->
<!--              scales = "free") + -->
<!--   theme_minimal() + -->
<!--   theme(axis.text.x = element_text(angle = 90)) -->
<!-- ``` -->
