
<!-- This .Rmd file is set up to run either independently by checking for 
the presence of necessary objects in the global environment and running 
related scripts if not, or also as a child to the "main-doc". For that latter
reason, comments and headings that are not relevant to a final report to
pubic audiences are suppressed or moved to code chunks that can optionally be 
`echo`ed as desired. -->

```{r}
# set flags for running this script
print_documentation <- FALSE
```

```{r}
# run scripts for necessary packages and objects as necessary
if (!"meanNA"        %in% objects()) source("settings--main.R", echo = FALSE)
if (!"my_state_abbr" %in% objects()) source("method--read-customization-file.R", echo = FALSE)
if (!"bin_age"       %in% objects()) source("method--general-helper-functions.R", echo = FALSE)

load(glue("{output_path}geo_data_{my_output_tag}.Rda"))

source("method--pull-and-process-acs5.R")

acs5_filename <- glue("{output_path}acs5_variables_{my_output_tag}.csv")
if (!file.exists(acs5_filename)) {
  source("pull--acs5-general-data.R")
}
```


# Pull and Develop ACS 5-Year Data

```{r}

if (!exists("my_county_fip")) {
  county_arg <- NULL
} else {
  county_arg <- my_county_fip
}

pull_my_table <- 
  function(
    my_table) {
    pull_table(
      my_table,
      state = my_state_abbr, 
      county = county_arg,
      year = acs5_year
    )
  }
```


## Total Population

```{r}
acs5_pop_pull <- pull_my_table("B01003")
    
inspect_fields(
  acs5_pop_pull, 
  show_all_combos = TRUE
)

acs5_pop <- 
  acs5_pop_pull %>% 
  select(
    GEOID,
    tot_pop    = estimate,
    tot_pop_se = se
  )

```


## Sex by Age

```{r}
acs5_sex_by_age_pull <- pull_my_table("B01001")
    
inspect_fields(
  acs5_sex_by_age_pull, 
  show_all_combos = TRUE
)

acs5_pop_by_age <- 
  acs5_sex_by_age_pull %>% 
  filter(
    age != "All"
  ) %>% 
  construct_fields(
    numerator = "age"
  )
  
```


## Population Under 18 Years of Age

```{r}

acs5_pop_lt18_pull <- pull_my_table("B09001")
    
inspect_fields(
  acs5_pop_lt18_pull, 
  show_all_combos = TRUE
)

acs5_pop_by_age_lt18 <- 
  acs5_pop_lt18_pull %>% 
  filter(
    age != "All",
    residence_type != "InGQ"
  ) %>% 
  construct_fields(
    numerator = "age"
  )

```


## Poverty Status in Past 12 Months by Sex by Age

```{r}
acs5_pov_bySexAge_pull <- pull_my_table("B17001")
    
inspect_fields(
  acs5_pov_bySexAge_pull, 
  show_all_combos = TRUE
)

acs5_pov_bySexAge <- 
  acs5_pov_bySexAge_pull %>% 
  filter(
    age != "All",
  ) %>% 
  construct_fields(
    numerator = "pov_status",
    by_vars = c("sex", "age")
  )

# Check
acs5_pov_bySexAge %>% 
  select(matches("^r.+Female_Age0to5")) %>% 
  head()

```


## Poverty status in past 12 months by household type by number of related children under 18

```{r}

acs5_pov_byNumKids_pull <- pull_my_table("B17012")

inspect_fields(
  acs5_pov_byNumKids_pull, 
  show_all_combos = TRUE
)

acs5_hhtype <- 
  acs5_pov_byNumKids_pull %>% 
  filter(
    own_kids_under18 == "All",
    pov_status != "All",
    !family_type %in% c("All", "Unmarried")
  ) %>% 
  construct_fields(
    numerator = "family_type"
  )

```


## Age by Ratio of Income to Poverty

```{r}

acs5_incpov_byage_pull <- pull_my_table("B17024")
    
inspect_fields(
  acs5_incpov_byage_pull, 
  show_all_combos = TRUE
)

acs5_incpov_byage_prep <- 
  acs5_incpov_byage_pull %>% 
  mutate(
    age =
      case_when(
        age == "Age0to6"                         ~ "Age0to6",
        str_detect(age, "Age(6to11|12to17)")     ~ "Age6to17",
        str_detect(age, "Age(18|25|35|45|55)to") ~ "Age18to64",
        str_detect(age, "Age(65|75)to")          ~ "AgeGe65",
        TRUE                                     ~ age
      )
  )

acs5_incpov_byage <- 
  acs5_incpov_byage_prep %>% 
  mutate(
    inc_to_pov_ratio = 
      case_when(
        str_detect(inc_to_pov_ratio, "Pov(50|75)to") ~ "IncPov50to100",
        TRUE ~ inc_to_pov_ratio
      )
  ) %>% 
  filter(
    age != "All",
    inc_to_pov_ratio != "All"
  ) %>% 
  construct_fields(
    numerator = "inc_to_pov_ratio",
    by_vars = "age"
  )

#stopifnot(all(acs5_incpov_byage %>% select(matches("^r.+_Age0to6")) %>% apply(1, sum) == 1))

# Create a different partition
acs5_incpov_byage_alt <- 
  acs5_incpov_byage_prep %>% 
  filter(
    age != "All",
    inc_to_pov_ratio != "All"
  ) %>% 
  mutate(
    inc_to_pov_ratio_alt = 
      case_when(
        str_detect(inc_to_pov_ratio, "Pov(0|50|75)to")          ~ "IncPov0to100",
        str_detect(inc_to_pov_ratio, "(100|125|150|175|185)to") ~ "IncPov100to199",
        str_detect(inc_to_pov_ratio, "(200|300)to")             ~ "IncPov200to399",
        str_detect(inc_to_pov_ratio, "(400to|500)")             ~ "IncPov400plus"
      )
  )

# Check the reassignment
if (FALSE) {
  acs5_incpov_byage_alt %>% select(matches("inc_to")) %>% unique()
}

acs5_incpov_byage_alt <- 
  acs5_incpov_byage_alt %>% 
  construct_fields(
    numerator = "inc_to_pov_ratio_alt",
    by_vars = "age"
  )

#stopifnot(all(acs5_incpov_byage_alt %>% select(matches("^r.+_Age0to6")) %>% apply(1, sum) == 1))

# Combine the different partitions
acs5_incpov_byage_out <- 
  merge(
    x = acs5_incpov_byage,
    y = acs5_incpov_byage_alt,
    by = "GEOID"
  )

```

## Ratio of Income to Poverty Level of Families in the Last 12 Months

```{r}

acs5_incpov_fam_pull <- pull_my_table("B17026")
    
inspect_fields(
  acs5_incpov_fam_pull, 
  show_all_combos = TRUE
)

acs5_incpov_byage <- 
  acs5_incpov_fam_pull %>% 
  filter(
    inc_to_pov_ratio != "All"
  ) %>% 
  construct_fields(
    numerator = "inc_to_pov_ratio"
  )

# Create an alternate partition
acs5_incpov_byage <- 
  acs5_incpov_fam_pull %>% 
  filter(
    inc_to_pov_ratio != "All"
  )

```

## Hispanic or Latino Origin by Race

```{r}
acs5_raceeth_pull <- pull_my_table("B03002")
    
inspect_fields(
  acs5_raceeth_pull, 
  show_all_combos = TRUE
)

acs5_raceeth4 <- 
  acs5_raceeth_pull %>% 
  filter(
    race != "All",
    hispanic != "Hisp"
  ) %>% 
  mutate(
    raceeth4 = 
      case_when(
        hispanic == "Hisp" ~ "Hisp",
        race     == "Wh"   ~ "White",
        race     == "Aa"   ~ "Black",
        TRUE               ~ "Other"
      )
  ) %>% 
  construct_fields(
    numerator = "raceeth4"
  )


```

<!-- ## Sex of Workers by Means of Transportation to Work -->

<!-- ```{r} -->
<!-- B08006 -->
<!-- ``` -->

<!-- ## Aggregate travel time to work of Workers by Sex -->

<!-- ```{r} -->
<!-- B08013 -->
<!-- ``` -->

<!-- ## Grandparents Living with Own Grandchildren Under 18 by Responsibility for Own Grandchildren by Presence of Parent of Grandchildren and Age of Grandparent -->

<!-- ```{r} -->
<!-- B10051 -->
<!-- ``` -->

<!-- ## Households with grandparent living with own grandchildren under 18 years by responsibility for own grandchildren by presence of grandchildren and presence of parent of grandchildren -->

<!-- ```{r} -->
<!-- B10063  -->
<!-- ``` -->


## Sex by Age by Employment Status for the Population 16 and Over

```{r}
acs5_empl_pull <- pull_my_table("B23001")
    
inspect_fields(
  acs5_empl_pull, 
  show_all_combos = TRUE
)

acs5_empl_prep_Age22to64 <- 
  acs5_empl_pull %>% 
  filter(
    sex != "All",
    #str_detect(age, "Age(22|25|30|35|45|55|60|62)to")
    str_detect(age, "Age25|Age30")
    # /!\ Need to remove this after performing checks against the old acs5 constructions
  )

acs5_empl <- 
  acs5_empl_prep_Age22to64 %>% 
  filter(
    lfp == "InLF",
    pop == "Civilian",
    status != "All"
  ) %>% 
  construct_fields(
    numerator = "status", 
    by_vars = c("sex")
  ) %>% 
  select(
    -matches("Unempl")
  )

acs5_empl_inclMilit <- 
  acs5_empl_prep_Age22to64 %>% 
  mutate(
    status = if_else(pop == "Military", "Empl", status),
    status = 
      case_match(
        status, 
        "Empl" ~ "EmplInclMilit", 
        .default = status
      )
  ) %>% 
  filter(
    lfp == "InLF",
    pop %in% c("Civilian", "Military"),
    status != "All"
  ) %>% 
  construct_fields(
    numerator = "status", 
    by_vars = c("sex")
  ) %>% 
  select(
    -matches("Unempl")
  )

acs5_lfrate <- 
  acs5_empl_prep_Age22to64 %>% 
  filter(
    (lfp == "InLF" & pop == "Civilian") |
    (lfp == "NotInLF"),
    status == "All"
  ) %>% 
  select(
    -pop, -status
  ) %>% 
  construct_fields(
    numerator = "lfp", 
    by_vars = c("sex")
  )

acs5_lfrate_inclMilit <- 
  acs5_empl_prep_Age22to64 %>% 
  filter(
    lfp != "All",
    pop == "All"
  ) %>%
  mutate(
    lfp = 
      case_match(
        lfp,
        "InLF" ~ "InLFOrMilit",
        "NotInLF" ~ "NotInLFOrMilit"
      )
  ) %>% 
  construct_fields(
    numerator = "lfp", 
    by_vars = c("sex")
  ) %>% 
  select(
    -matches("NotIn")
  )

```

## Sex by Educational Attainment for Population 25 Years and Older

```{r}
acs5_edattain_pull <- pull_my_table("B15002")
    
inspect_fields(
  acs5_edattain_pull, 
  show_all_combos = TRUE
)

acs5_edattain_bySex <- 
  acs5_edattain_pull %>% 
  filter(
    sex != "All"
  ) %>% 
  construct_fields(
    numerator = "ed_attain",
    by_vars = "sex"
  )

acs5_edattain <- 
  acs5_edattain_pull %>% 
  filter(
    sex != "All"
  ) %>% 
  construct_fields(
    numerator = "ed_attain"
  )

```


```{r collect}
acs5_tomerge <- 
  list(
    acs5_pop_by_age, 
    acs5_pop_by_age_lt18, 
    #acs5_pov_bySexAge, 
    acs5_incpov_byage_out, 
    acs5_raceeth4, 
    acs5_hhtype,
    acs5_empl, 
    acs5_empl_inclMilit,
    acs5_lfrate, 
    acs5_lfrate_inclMilit, 
    acs5_edattain,
    acs5_edattain_bySex
  )

# Retain only rate and std err of rate calculations
acs5_tomerge <- lapply(acs5_tomerge, \(x) select(x, matches("GEOID|^(r|se_r|w|n)")))

merge_reduce <- function(x, y) merge(x, y, by = "GEOID")

acs5 <- Reduce(merge_reduce, acs5_tomerge)
```

```{r merge new pulls to old construction}
acs5_old <- read.csv(glue("{output_path}acs5_variables_{my_output_tag}.csv"))
acs5_comp <- 
  merge(
    acs5,
    acs5_old,
    by.x = "GEOID",
    by.y = "geo_val")
```


```{r build comparions}
# Key fields, from 02a
acs5_checks <- 
  tribble(
    ~acs5_old,                  ~acs5_new,
    "incpov_lt6_r0to50_est",    "rIncPov0to50_Age0to6",
    "incpov_lt6_r50to100_est",  "rIncPov50to100_Age0to6",
    "incpov_lt6_r100to199_est", "rIncPov100to199_Age0to6",
    "incpov_lt6_r200to299_est", "rIncPov200to299_Age0to6",
    "f_lesshs_est",             "rEdLtHs_Female",
    'm_lesshs_est',             "rEdLtHs_Male",
    "f_hsgrad_est",             "rEdHs_Female",
    "m_hsgrad_est",             "rEdHs_Male",
    "f_somecoll_est",           "rEdSomeColl_Female",
    "m_somecoll_est",           "rEdSomeColl_Male",
    "f_coll_est",               "rEdColl_Female",
    "m_coll_est",               "rEdColl_Male",
    "pctMarried_est",           "rMarried",
    "pctMale_noSp_est",         "rUnmarriedMaleHh",
    "pctFemale_noSp_est",       "rUnmarriedFemaleHh",
    "employrate_m_a2534_est",   "rEmplInclMilit_Male",
    "employrate_f_a2534_est",   "rEmplInclMilit_Female",
    "lfrate_m_a2534_est",       "rInLF_Male",
    "lfrate_f_a2534_est",       "rInLF_Female"
  )


for (r in 1:nrow(acs5_checks)) {
  check <- acs5_checks[r,]
  my_plot <- 
    acs5_comp %>% 
    ggplot() + 
    aes(
      x = get(check$acs5_old),
      y = get(check$acs5_new)
    ) + 
    geom_point() + 
    geom_abline() +
    labs(
      x = check$acs5_old,
      y = check$acs5_new
    )
  print(my_plot)
}

acs5_comp %>% filter(GEOID == GEOID[1]) %>% select(matches("wEmplInclMilit_Male|employrate_m_a2534_count"))

```





## Details of ACS 5-Year Aggregate Data Development

```{r read ACS 5-year data and add miscellaneous constructions not handled in the pull}
acs5tract <- 
  fread(acs5_filename) %>% 
  # Keep tracts with non-zero population.
  .[(endyear == max(endyear)) & (tot_families_count > 0)] %>%
  mutate(raceeth_wh_est   = raceeth_wh_h_est + raceeth_wh_nonh_est,
         raceeth_wh_se    = sqrt(raceeth_wh_h_se^2 + raceeth_wh_nonh_se^2),
         raceeth_wh_se    = se_col_sum(raceeth_wh_h_se, raceeth_wh_nonh_se),
         raceeth_wh_count = raceeth_wh_h_count + raceeth_wh_nonh_count,
         
         raceeth_bl_est   = raceeth_bl_h_est + raceeth_bl_nonh_est,
         raceeth_bl_se    = se_col_sum(raceeth_bl_h_se, raceeth_bl_nonh_se),
         raceeth_bl_count = raceeth_bl_h_count + raceeth_bl_nonh_count,
         
         raceeth_h_est    = raceeth_amind_h_est + raceeth_as_h_est + raceeth_bl_h_est + 
           raceeth_mult_h_est + raceeth_oth_h_est + raceeth_pacisl_h_est + raceeth_wh_h_est,
         raceeth_h_se     = se_col_sum(raceeth_amind_h_se, raceeth_as_h_se, 
                                       raceeth_bl_h_se, raceeth_mult_h_se, raceeth_oth_h_se,
                                       raceeth_pacisl_h_se, raceeth_wh_h_se),
         raceeth_h_count = raceeth_amind_h_count + raceeth_as_h_count + raceeth_bl_h_count + 
           raceeth_mult_h_count + raceeth_oth_h_count + raceeth_pacisl_h_count +
           raceeth_wh_h_count,
         
         ed_lths_n     = m_lesshs_est  * m_lesshs_count   + f_lesshs_est  * f_lesshs_count,
         ed_hs_n       = m_hsgrad_est  * m_hsgrad_count   + f_hsgrad_est  * f_hsgrad_count,
         ed_somecoll_n = m_somecoll_est* m_somecoll_count + f_somecoll_est* f_somecoll_count,
         ed_coll_n     = m_coll_est    * m_coll_count     + f_coll_est    * f_coll_count,
         ed_lths     = ed_lths_n     / (m_lesshs_count   + f_lesshs_count),
         ed_hs       = ed_hs_n       / (m_hsgrad_count   + f_hsgrad_count),
         ed_somecoll = ed_somecoll_n / (m_somecoll_count + f_somecoll_count),
         ed_coll     = ed_coll_n     / (m_coll_count     + f_coll_count)) %>% 
  data.table()

```


```{r prepare ACS 5-year geographic identifiers - tract-level}
acs5tract <- 
  acs5tract %>%
  .[j = geo_val_string := str_pad(geo_val, width = 11, side = "left", pad = 0)] %>%
  .[j = `:=`(STATEFIP  = substr(geo_val_string, 1, 2),
             COUNTYFIP = substr(geo_val_string, 3, 5),
             TRACTFIP  = substr(geo_val_string, 6, 11),
             YEAR = endyear)] %>%
  rename(GEOID = geo_val_string) %>% 
  select(-one_of("source", "endyear", "geo", "geo_val", "NAME")) %>%
  # Set order of the rows
  setorder(YEAR, STATEFIP, COUNTYFIP, TRACTFIP) %>%
  # Set order of the columns
  setcolorder(c("YEAR", "STATEFIP", "COUNTYFIP", "TRACTFIP"))
```

<!-- ### Aggregate ACS 5-Year Data to the PUMA level -->

<!-- Tract-level ACS5 data are aggregated to the PUMA-level for use in certain sensitivities of the Small Area Estimation method which develop estimates at the PUMA level (although our end goal is to get to smaller geographic levels.) -->

```{r prepare ACS 5-year geographic identifiers - PUMA-level}
# Add PUMA identifiers to tract-level 5-year aggregate data set. Drop tract identifiers.
acs5puma <- 
  merge(acs5tract, 
        geo_crosswalk, 
        by = c("STATEFIP", "COUNTYFIP", "TRACTFIP", "GEOID"), 
        all.x = TRUE) %>%
  filter(!is.na(PUMA)) %>%
  select(-COUNTYFIP, -TRACTFIP) %>%
  setorder(YEAR, STATEFIP, PUMA) %>%
  setcolorder(c("YEAR", "STATEFIP", "PUMA"))
```

<!-- For tract-level average/share variables, store "stubs" of variable names in a list. -->

<!-- Multiply tract-level average/share variables by corresponding tract-level denominator count variables to produce tract-level numerator count variables. -->

<!-- Recall that original _count variables from the ACS input files store tract-level denominator count variables.
/!\ This is an aspects of naming conventions that is confusing and is worth reconsidering for clarity in on-going work -->

```{r prepare ACS 5-year geographic identifiers}

avg_list <- str_subset(cn(acs5puma), "_est$") %>% str_remove(., "_est")

check <- copy(acs5puma)

# Go through all variables and adjust them to be suitable for summing where:
# * "_est" is converted to a numerator count, 
# * "_se" is converted to a variance
# * "_count" is left as is. That's the denominator.
for (var_name in avg_list) {
  # /!\ Kludge to ignore fields that don't match conventions
  if (str_detect(var_name, "Male_noSp|Female_noSp|^Married|pctMarried|^famtype")) next
  acs5puma <- 
    acs5puma %>% 
    .[, paste0(var_name, "_est") := eval(parse(text=paste0(var_name, "_est")))*eval(parse(text=paste0(var_name, "_count")))] %>%
    .[, paste0(var_name, "_se")  := eval(parse(text=paste0(var_name, "_se")))^2]
}

if (FALSE) {
  acs5puma[PUMA == 3401, str_subset(cn(acs5puma), "r0to50"), with = FALSE]
  check[j = numer := incpov_r0to50_est*incpov_r0to50_count]
  check[PUMA== 3401, .(numer)]  
}

# Perform the sum
acs5puma <-
  acs5puma %>%
  .[, lapply(.SD, sumNA), 
    by = .(YEAR, STATEFIP, PUMA),
    .SDcols = str_subset(cn(acs5puma), "_est$|_count$|_se$")]

if (FALSE) {
  acs5puma[PUMA == 3401, str_subset(cn(acs5puma), "r0to50"), with = FALSE]
  check[PUMA == 3401, .(sum(numer), sum(incpov_r0to50_count))]  
}

# Construct PUMA-level average/share variables by taking the ratio of the PUMA-level numerator count variable and the PUMA-level denominator count variable.
# Construct PUMA-level standard errors by taking the square root of the PUMA-level variance.

for (var_name in avg_list) {
  # /!\ Kludge to ignore fields that don't match conventions
  if (str_detect(var_name, "Male_noSp|Female_noSp|^Married|pctMarried|^famtype")) next
  acs5puma <-
    acs5puma %>%
    # /!\ Could improve readability with glue(), and ep <- function(x) eval(parse(text = x))
    .[, paste0(var_name, "_est") := eval(parse(text=paste0(var_name, "_est")))/eval(parse(text=paste0(var_name, "_count")))] 
}

if (FALSE) {
  acs5puma[PUMA == 3401, str_subset(cn(acs5puma), "r0to50"), with = FALSE]
  check[PUMA == 3401, sum(numer) / sum(incpov_r0to50_count)]  
}

se_list <- str_subset(cn(acs5puma), "_se$") %>% str_remove(., "_se")
for (var_name in se_list) {
  # /!\ Kludge to ignore fields that don't match conventions
  if (str_detect(var_name, "Male_noSp|Female_noSp|^Married|pctMarried|^famtype")) next
  acs5puma <-
    acs5puma %>%
    .[, paste0(var_name, "_se") := sqrt(eval(parse(text=paste0(var_name, "_se"))))]
}

```

```{r compare the tract- and puma-level data, eval = developer_mode}
acs5comp <- 
  acs5tract %>% 
  merge(geo_crosswalk %>% select(GEOID, PUMA),
        by = "GEOID") %>% 
  merge(acs5puma,
        by = "PUMA")

# Looks right
ggplot(acs5comp, aes(incpov_r0to50_est.y, incpov_r0to50_est.x)) + 
  geom_point(alpha = 0.2) +
  geom_smooth()

# Audit the construction of the acs5puma
acs5tract_test <- 
  acs5tract %>% 
  merge(geo_crosswalk %>% select(GEOID, PUMA),
        by = "GEOID") %>% 
  mutate(incpov_r0to50_num = incpov_r0to50_est*incpov_r0to50_count) %>% 
  group_by(PUMA) %>% 
  summarize(wgt = sum(incpov_r0to50_count),
            n   = sum(incpov_r0to50_num)) %>% 
  mutate(r   = n / wgt) %>% 
  merge(acs5puma %>% select(PUMA, incpov_r0to50_est, incpov_r0to50_count),
        by = "PUMA")
#View(acs5tract_test %>% select(wgt, n, r, incpov_r0to50_est, incpov_r0to50_est))
```

```{r}
save(acs5tract, acs5puma,
     file = glue("{output_path}acs5_data_{my_output_tag}.Rda"))
```

```{r prepare county argument for fresh pull of acs5 data}
if (exists("my_county_fip")) county_val <- my_county_fip else county_val <- NULL
```

```{r fresh pull of both income and work status tables}
# "Age by Ratio of Income to Poverty Level In the Past 12 Months"
acs5_incpov_byage_raw    <- pull_table("B17024", state = my_state_abbr, county = county_val, year = acs5_year)

# "Presence of Own Children Under 18 Years by Family Type by Employment Status"
acs5_famconfig_wKids_raw <- pull_table("B23007", state = my_state_abbr, county = county_val, year = acs5_year)

```

```{r determine closest fpl cutoff to ccdf eligibility threshold}
ccdf_inc_thresh_fpl <- get_fpl_thresh_for_ccdf()

# Determine which inc-to-pov value from the tables is closest to the ccdf fpl
# cutoff
acs5_income_cutpoints <- c(0, 50, 75, 100, 125, 150, 175, 185, 200, 300, 400, 500)
dev <- 
  (acs5_income_cutpoints - ccdf_inc_thresh_fpl) %>% 
  abs()

nearest_incpov_cutpoint_to_ccdf <- 
  acs5_income_cutpoints[which(dev == min(dev))]
```

```{r perform basic incpov calculations}
acs5_incpov_byage_wide <- 
  construct_fields(
    df = acs5_incpov_byage_raw,
    numerator = "inc_to_pov_ratio",
    by_vars = "age",
    subset_cond = "age %in% c('Age0to6', 'Age6to11')",
    subset_descr = "")

acs5_incpov_byage <- 
  construct_fields(
    df = acs5_incpov_byage_raw,
    numerator = "inc_to_pov_ratio",
    by_vars = "age",
    subset_cond = "age %in% c('Age0to6', 'Age6to11')",
    subset_descr = "", 
    wide = FALSE)
```

```{r construct desired work eligibility field}
inspect_fields(acs5_famconfig_wKids_raw)

# /!\ These constructions have problems with respect handling complicated
# and non-parallel hierarchies in the "InLfp" field
# acs5_workelig_withKids_old_wide <- 
#   construct_fields(
#     df = acs5_famconfig_wKids_raw,
#     subset_cond = "own_kids_under18 == 'SomeKidsUnder18'",
#     #denom_subset = "status == 'All'",
#     numerator = "status", 
#     numerator_vals = c("HusbandEmplWifeEmpl", "Empl"),
#     numerator_lab  = c("WorkEligFam"),
#     subset_descr = "")
# 
# acs5_workelig_withKids_old <- 
#   construct_fields(
#     df = acs5_famconfig_wKids_raw,
#     subset_cond = "own_kids_under18 == 'SomeKidsUnder18' & !(family_type == 'Married' & lfp %in% c('HusbandInLfp', 'HusbandNotInLfp'))",
#     #denom_subset = "status == 'All'",
#     numerator = "status", 
#     numerator_vals = c("HusbandEmplWifeEmpl", "Empl"),
#     numerator_lab  = c("WorkEligFam"),
#     subset_descr = "",
#     wide = FALSE)

# Calculating work eligibility by hand
acs5_workelig_withKids_denom <- 
  acs5_famconfig_wKids_raw %>% 
  filter(own_kids_under18 == "SomeKidsUnder18",
         family_type %in% c("Married", "UnmarriedMaleHh", "UnmarriedFemaleHh"),
         lfp == "All",
         status == "All")

acs5_workelig_withKids_num <- 
  acs5_famconfig_wKids_raw %>% 
  filter(own_kids_under18 == "SomeKidsUnder18",
         (family_type == "Married" & status == "HusbandEmplWifeEmpl") | 
         (str_detect(family_type, "Unmarried") & status == "Empl"))

acs5_workelig_withKids <- 
  merge(acs5_workelig_withKids_num   %>% summarize(nEmpl = sum(estimate), .by = GEOID),
        acs5_workelig_withKids_denom %>% summarize(nAll  = sum(estimate), .by = GEOID),
        by = "GEOID") %>% 
  mutate(r = nEmpl / nAll,
         n = nEmpl,
         w = nAll,
         status = "WorkEligFam")

acs5_workelig_withKids <- 
  bind_rows(acs5_workelig_withKids,
            acs5_workelig_withKids %>% mutate(r = 1 - r, n = w - n, status = "NotWorkEligFam")) 

# Audit the constructions here
if (FALSE) {
  my_g <- acs5_workelig_withKids$GEOID[1]
  
  acs5_workelig_withKids_old %>% filter(GEOID == my_g)  
  acs5_workelig_withKids     %>% filter(GEOID == my_g)  
  
  acs5_famconfig_wKids_raw %>% filter(GEOID == my_g, own_kids_under18 == "SomeKidsUnder18") %>% select(-variable, -se, -geography, -table, -GEOID) %>% as.data.frame()
  
  # All families: 367
  # Married: HusbandEmplWifeEmpl -- 130
  # UnmarriedMaleHh: Empl = 28
  # UnmarriedFemaleHh: Empl = 102
  # Hand calc: (130+28+102)/367 = 70.8% ... this is below the 36% calculation
  # Solutions -- 
  # 1. either need to add handling in the meta data for these cases, or
  # 2. split the calculations for married and for single families? 
  #    - not sure if/how well this would work given the issues with the InLfp field
  # 3. ... Maybe do this fully by hand?
  
  # New example -- 
  # All families: 186
  # Married: HusbandEmplWifeEmpl -- 88
  # UnmarriedMaleHh: Empl = 19
  # UnmarriedFemaleHh: Empl = 9
  # Hand calc: (88+19+9)/186 = 62.3% ... WOking Fam est is 42%
  
}

```


```{r merge together data sets intended for estimating ccdf eligibility}
merge_by_geoid <- function(x, y) {
  # Remove duplicate fields
  non_dup_fields <- c(cn(y)[!cn(y) %in% cn(x)], "GEOID")
  merge(x, y %>% select(one_of(non_dup_fields)), by = "GEOID", all = TRUE)
}
# acs5_ccdf <-
#   Reduce(merge_by_geoid,
#          list(acs5_incpov_byage_wide, acs5_workelig_withKids_wide))

save(list = c("acs5_incpov_byage", "acs5_workelig_withKids"), 
     file = glue("{output_path}acs5_ccdf_{my_output_tag}.Rda"))
```


