
<!-- This .Rmd file is set up to run either independently by checking for 
the presence of necessary objects in the global environment and running 
related scripts if not, or also as a child to the "main-doc". For that latter
reason, comments and headings that are not relevant to a final report to
pubic audiences are suppressed or moved to code chunks that can optionally be 
`echo`ed as desired. -->

```{r}
# set flags for running this script
print_documentation <- FALSE
```

```{r}
# run scripts for necessary packages and objects as necessary
if (!"meanNA"        %in% objects()) source("settings--main.R", echo = FALSE)
if (!"my_state_abbr" %in% objects()) source("method--read-customization-file.R", echo = FALSE)
if (!"bin_age"       %in% objects()) source("method--general-helper-functions.R", echo = FALSE)

Sys.setenv(census_api_key = census_key)
# Check to see that the expected key is output in your R console
Sys.getenv("census_api_key")

options(scipen=999)

```



# Hard Calibration Method for Population Estimation -- ACS5 and ACS1

This code develops counts of individuals by age, by tract as of the year of the most recent ACS 1-year release. It does this by taking age-by-tract counts from the most recent ACS5 release, which of course represents many years, and calibrates the totals to match the corresponding PUMA. This is a "hard" calibration in the sense that we ask the across-tract totals to match the PUMA sum exactly, even though each construct is measured with noise (which should be considered in a more balanced, "soft" calibration approach).

```{r}
# Load prepped data
for (f in c("geo", "acs1", "acs5")) {
  load(file = glue("{output_path}{f}_data_{my_output_tag}.Rda"))
}
```


```{r select acs5 age counts}
ageCounts_t <- 
  acs5tract %>% 
  select(
    matches("GEOID|^nAge")
  )
```

```{r merge PUMA into tract-level data}

ageCounts_pt <- 
  merge(
    ageCounts_t,
    geo_crosswalk %>% select(GEOID, PUMA) %>% unique(),
    by = "GEOID"
  )

stopifnot(nrow(ageCounts_t) == nrow(ageCounts_pt))
```


```{r function to build acs1 counts within age range}
get_puma_totals <- function(bounds) {
  
  stopifnot(all(setdiff(bounds, Inf) %in% acs1_elig$AGEP))
  acs1_elig %>% 
    filter(
      between(AGEP, bounds[1], bounds[2])
    ) %>% 
    summarize(
      .by = PUMA,
      n_p_to = sum(PWGTP)
    )
}

stopifnot(
  get_puma_totals(c(0, 5)) %>% 
    filter(PUMA == acs1_elig$PUMA[1]) %>% 
    pull(n_p_to) == 
    acs1_elig %>% 
    filter(
      0 <= AGEP, 
      AGEP <= 5
    ) %>% 
    summarize(
      .by = PUMA,
      n_p_to = sum(PWGTP)
    ) %>% 
    filter(
      PUMA == acs1_elig$PUMA[1]
    ) %>% 
    pull(n_p_to)
)
```

```{r function to get ages from variable name}
get_age_bounds <- function(age_var) {
  if (str_detect(age_var, "\\dto\\d")) {
    bounds <-
      str_extract_all(
        age_var, 
        "\\d+"
      ) %>% 
      unlist() %>% 
      as.numeric()
  } else if (str_detect(age_var, "[Ll]t\\d")) {
    ub <- 
      str_extract(
        age_var, 
        "\\d+"
      ) %>% 
      as.numeric()
    bounds <- c(0, ub - 1)
  } else if (str_detect(age_var, "\\dplus")) {
    lb <- 
      str_extract(
        age_var, 
        "\\d+"
      ) %>% 
      as.numeric()
    bounds <- c(lb, Inf)
  }
  return(bounds)
}

stopifnot(get_age_bounds("rAge0to19")  == c( 0, 19))
stopifnot(get_age_bounds("rAge20to64") == c(20, 64))
stopifnot(get_age_bounds("rAge65plus") == c(65, Inf))
```


```{r function to calibrate}

calibrate_counts <- function(age_var) {
  
  my_bounds <- get_age_bounds(age_var)
  age_counts_p <- get_puma_totals(my_bounds)
  
  ageCounts_pt %>% 
    mutate(
      .by = PUMA,
      n_p_from = sum(get(age_var))
    ) %>% 
    merge(
      age_counts_p,
      by = "PUMA"
    ) %>% 
    mutate(
      calib_mult = n_p_to / n_p_from,
      calib = get(age_var) * calib_mult
    )
}

# Sanity checks
if (FALSE) {
  # my_n_field <- "nAge0to19"
  my_n_field <- "nAge65plus"
  x <- calibrate_counts(my_n_field)
  x %>% select(PUMA, calib_mult) %>% unique() %>% pull(calib_mult) %>% hist()
  x %>% 
    filter(
      PUMA %in% unique(PUMA)[1:5]
    ) %>% 
    ggplot() +
    aes(
      x = get(my_n_field),
      y = calib
    ) + 
    geom_point() + 
    geom_abline() +
    facet_wrap(
      ~PUMA
    )
}

```


```{r}
batch_calibrations <- function(age_vars) {
  calibs <- 
    lapply(
      age_vars,
      \(a) {
        calibrate_counts(a) %>% 
          select(GEOID, calib) %>% 
          mutate(
            age_var = a,
            year = base_year
          )
      }
    )
  bind_rows(calibs)
}

pop_age_t_calib <- 
  batch_calibrations(
    c(
      "nAge0to19",
      "nAge20to64",
      "nAge65plus",
      
      "nAge0to4",
      "nAge5to8",
      "nAge9to15",
      "nAge16to18",
      "nAge19to25",
      "nAge26to34",
      "nAge35to44",
      "nAge45to54",
      "nAge55to64"
    )
  )

pop_age_t_calib_wide <- 
  pop_age_t_calib %>% 
  pivot_wider(
    id_cols = "GEOID",
    values_from = "calib",
    names_from = "age_var"
  )
```


```{r save long-by-year population data}
save(
  pop_age_t_calib, pop_age_t_calib_wide,
  file = glue("{output_path}pop_data_{my_output_tag}.Rda")
)
```



