
<!-- This .Rmd file is set up to run either independently by checking for 
the presence of necessary objects in the global environment and running 
related scripts if not, or also as a child to the "main-doc". For that latter
reason, comments and headings that are not relevant to a final report to
pubic audiences are suppressed or moved to code chunks that can optionally be 
`echo`ed as desired. -->

```{r}
# set flags for running this script
print_documentation <- FALSE
```

```{r}
# run scripts for necessary packages and objects as necessary
if (!"meanNA"        %in% objects()) source("settings--main.R", echo = FALSE)
if (!"my_state_abbr" %in% objects()) source("method--read-customization-file.R", echo = FALSE)
if (!"bin_age"       %in% objects()) source("method--general-helper-functions.R", echo = FALSE)

Sys.setenv(census_api_key = census_key)
# Check to see that the expected key is output in your R console
Sys.getenv("census_api_key")

options(scipen=999)

```

```{r identify relevant fips codes for population pulls}
my_state_fip <- 
  fips_codes %>% 
  filter(state == my_state_abbr) %>% 
  pull(state_code) %>% 
  unique()

if ("my_county" %in% objects()) {
  my_county_fip <- 
    fips_codes %>% 
    filter(state == my_state_abbr, 
           str_detect(county, my_county)) %>% 
    pull(county_code) %>% 
    unique() 
}

if (exists("my_county_fip")) {
  county_arg <- as.numeric(my_county_fip)
} else {
  county_arg <- NULL
}

```

### Estimating Overall Population Counts for Young Children

This code pulls together data from the [2020 Census Demographic and Housing Characteristics](https://api.census.gov/data/2020/dec/dhc/variables.html) and [2010 SF1 Census files](https://api.census.gov/data/2010/dec/sf1.html) to get population by age group to use in projecting population counts for young children through `r glue('{base_year + 1}')` .

<!-- * For a really helpful video on pulling redistricting data see - https://www.census.gov/library/video/2021/adrm/accessing-2020-census-redistricting-data-through-the-census-data-api-tables-and-group-calls.html -->

2020 Population

* Use 2020 Census DHC to get single-age population data at the tract level

2010 Population

* Use 2010 Census SF1 to get single-age population data at the block group level 
* Use NHGIS 2010-block-groups-to-2020-tract crosswalk to obtain 2010 pop counts for 2020 tracts

```{r develop metadata for the 2020 DHC data}
# Load variables for 2020 DHC
# Also available at https://api.census.gov/data/2020/dec/dhc/variables.html
var_dhc_2020 <- load_variables(2020, dataset = "dhc")

# Filter variables
var_dhc_2020 <- 
  var_dhc_2020 %>% 
  # P14: Count by single-year age for the population under 20 years (available at the block/tract level)
  filter(str_detect(name, "^P14")) %>%
  mutate(age = str_extract(label, "\\d+"),
         age = as.numeric(age) - str_detect(label, "Under"),
         sex = case_when(str_detect(label, "Female") ~ "female",
                         str_detect(label, "Male")   ~ "male",
                         TRUE                        ~ "all")) %>% 
  filter(age %in% 0:17,
         !(sex == "all"))

# Examine the mapping
if (FALSE) {
  var_dhc_2020 %>% 
    select(label, age, sex)
}
```


```{r pull single-age population counts aged 0 - 17 from 2020 DHC}
#Tract-level pop count by age
pop_tract_2020_dhc <-
  get_decennial(
    geography = "tract",
    variables = var_dhc_2020$name,
    year      = 2020,
    sumfile   = "dhc",
    state     = my_state_fip,
    county    = county_arg,
    geometry  = F) %>% 
  merge(var_dhc_2020 %>% select(-label, -concept),
        by.x = "variable",
        by.y = "name",
        all = TRUE) %>% 
  rename(GEOID_TR20 = GEOID)
```

```{r establish an age grouping function for use in all recodings below}
group_census_ages <- function(age) {
  case_when(age %in% 0:5         ~ as.character(age),
            between(age,  6, 12) ~ "612",
            between(age, 13, 17) ~ "1317",
            TRUE                 ~ NA)
}
```


```{r generate pop est by age groups using DHC}
pop_age_groups_2020_dhc <-
  pop_tract_2020_dhc %>% 
  select(-variable, NAME) %>%
  mutate(agegroup = group_census_ages(age)) %>% 
  summarise(value = sum(value),
            .by = c(GEOID_TR20, agegroup))

```

## Census Population Data from 2010 Summary File 1

```{r develop metadata for the 2021 SF1 data}
# Load variables for 2010 SF1
var_sf1_2010 <- load_variables(2010, dataset = "sf1")

# Filter variables
var_sf1_2010 <- 
  var_sf1_2010 %>% 
  filter(str_detect(name, "P014")) %>% #name, ("PCT012|P012|P014")
  mutate(age = str_extract(label, "\\d+"),
         age = as.numeric(age) - str_detect(label, "Under"),
         #age = ifelse(is.na(age), "all", age),
         sex = case_when(str_detect(label, "Female") ~ "female",
                         str_detect(label, "Male")   ~ "male",
                         TRUE                        ~ "all")) %>% 
  filter(age %in% 0:17,
         !(sex == "all"))

# Examine the mapping
if (FALSE) {
  var_sf1_2010 %>% 
    select(label, age, sex)
}
```


```{r pull single-age population counts aged 0 - 17 from 2010 SF1}
# Block-group-level pop count by age
pop_bg_2010_sf1 <-
  get_decennial(
    geography = "block group",
    variables = var_sf1_2010$name,
    year      = 2010,
    sumfile   = "sf1",
    state     = my_state_fip,
    county    = county_arg,
    geometry  = F) %>% 
  merge(var_sf1_2010 %>% select(-label, -concept),
        by.x = "variable",
        by.y = "name",
        all = TRUE) %>% 
  rename(GEOID_BG10 = GEOID) %>%
  mutate(GEOID_TR10 = str_sub(GEOID_BG10, 1, 11)) # get tract-level GEOID

```

```{r develop 2010 block group to 2020 tract crosswalk}
# See https://www.nhgis.org/geographic-crosswalks#from-block-groups
# Download crosswalks from 2010 block groups to 2020 census tracts
# url: https://data2.nhgis.org/crosswalks/nhgis_bg2010_tr2020.zip 
# It's necessary to sign in to download

xwk_bg2010_tr2020 <-
  read_nhgis(glue("{input_path}nhgis_bg2010_tr2020.zip")) %>% 
  # wt_pop: Expected proportion of source zone's `population` located in target zone
  select(GEOID_BG10 = bg2010ge, 
         GEOID_TR20 = tr2020ge, 
         wt_pop) %>%
  mutate(statefip = as.character(substr(GEOID_TR20, 1, 2))) %>%
  filter(statefip == {my_state_fip})

# Confirm that all necessary geographies are represented
stopifnot(all(   pop_bg_2010_sf1$GEOID_BG10 %in% xwk_bg2010_tr2020$GEOID_BG10))
stopifnot(all(pop_tract_2020_dhc$GEOID_TR20 %in% xwk_bg2010_tr2020$GEOID_TR20))

```

```{r implement use of crosswalk}
pop_bg2010_tr2020_agegroup <- 
  pop_bg_2010_sf1 %>% 
  summarise(value = sum(value),
            .by = c(GEOID_BG10, age)) %>%
  merge(xwk_bg2010_tr2020,
        by = "GEOID_BG10",
        all.x = T) %>%
  mutate(pop_tr2020 = (value*wt_pop)) %>%
  mutate(agegroup = group_census_ages(age)) %>%
  summarise(est_2010 = sum(pop_tr2020),
            .by = c(GEOID_TR20, agegroup))

```

```{r recode remaining zeros in the 2010 final}
if (any(sapply(pop_bg2010_tr2020_agegroup, function(x) mean(is.na(x)) %>% sort()) != 0)) {
  pop_bg2010_tr2020_agegroup <-
    pop_bg2010_tr2020_agegroup %>% 
    mutate(est_2010 = replace_na(est_2010, 0)) 
}
```


```{r check recoding of remaining zeros in the 2010 final, eval = developer_mode}
sapply(pop_bg2010_tr2020_agegroup, function(x) mean(is.na(x)) %>% sort())  
```

### Combine 2010 and 2020 at tract level to prep for interpolation of years between Census

```{r merge tract-level estimates}
pop_2010_2020_tract <-
  pop_age_groups_2020_dhc %>% 
  rename(est_2020 = value) %>% 
  merge(pop_bg2010_tr2020_agegroup,
        by = c("GEOID_TR20",   "agegroup"),
        all.x = TRUE) %>%
  pivot_longer(cols = c("est_2010", "est_2020"),
               names_to = "variable",
               values_to = "pop_est") %>%
  separate(variable, 
           into = c("pop","year")) %>%
  select(-pop) %>% 
  # Set minimum population of 1
  mutate(pop_est = ifelse(pop_est < 1, 1, pop_est))

```


### Interpolate estimates for intercensal years

```{r generate data frame for interpolation}
# Take all unique tract/age-group combinations from the 2010/2020 data,
# create a frame with all years from 2010 to 2020, and merge in endpoint data.
interp_frame <- 
  pop_2010_2020_tract %>% 
  reframe(year = min(year):max(year),
          .by = c(GEOID_TR20, agegroup)) %>% 
  merge(pop_2010_2020_tract,
        by = c("GEOID_TR20", "agegroup", "year"),
        all.x = TRUE)
```


```{r Check for tracts with no data for interpolatee}
insufficient_interp_tracts <-
  interp_frame %>% 
  mutate(n = sum(!is.na(pop_est)))

if (mean(insufficient_interp_tracts$n < 2) != 0) {
  # Identify insufficient tracts
  insufficient_interp_tracts %>% 
    filter(n < 2) %>% 
    pull(GEOID_TR20) %>% 
    unique()
  
  insufficient_interp_tracts <-
    insufficient_interp_tracts %>% 
    filter(n < 2)  
}
```


```{r perform interpolation}
# na.interp is from forecast package
ests_interp <-
  interp_frame %>% 
  group_by(GEOID_TR20, agegroup) %>% 
  mutate(pop_interp = na.interp(pop_est))

# Examine structure
if (FALSE) {
  head(ests_interp, 12)  
}


```

### Use the forecast package to get 2021 estimates 

```{r get next year estimate}
# Make a tibble
ests_interp_ts <- 
  ests_interp %>%
  ungroup() %>% 
  #filter(GEOID_TR20 == GEOID_TR20[1], agegroup == 0) %>% 
  as_tsibble(key = c(GEOID_TR20, agegroup),
             index = year)

# Forecasts for 2021 generated from Holt's method
system.time({
  fit <- 
    ests_interp_ts %>%
    model(
      AAN = ETS(pop_interp ~ error("A") + trend("A") + season("N")) 
    )
})

# Damped Holt's method
# model(
#     AAN = ETS(pop_interp ~ error("A") + trend("Ad", phi = 0.9) + season("N")) 
#   )

fc <- fit %>% forecast(h = max(1, base_year + 2 - 2020))

# We end up with some negative values here - 190 observations (<5%)
# These are tracts with no kids in that age group in ACS - I think this is okay - we'll round up to 0
```


```{r examine number of estimates that go below zero}
est_forecast <-
  as.data.frame(fc)

est_forecast %>% 
  summarize(pct_neg = mean(.mean < 0),
            .by = agegroup)

est_forecast <-
  est_forecast %>%
  mutate(pop_interp = ifelse(.mean < 0, 0, floor(.mean))) %>%
  select(GEOID_TR20, agegroup, year, pop_interp)

```

### Reshape the estimates and export

```{r reshape and export to H drive}
# Round interpolated estimates
ests_20102020 <-
  as.data.frame(ests_interp) %>%
  mutate(pop_interp = round(pop_interp, 0)) %>% 
  select(GEOID_TR20, agegroup, year, pop_interp)

ests_with_forecast <- 
  bind_rows(ests_20102020, 
            est_forecast)

```

```{r examine forecast estimates}
ests_with_forecast_change <- 
  ests_with_forecast %>% 
  mutate(pop_interp_pct_change = 
           (pop_interp[year == base_year + 1] - pop_interp[year == 2010]) / pop_interp[year == 2010],
         change_cat = 
           case_when(pop_interp_pct_change < 0.3 ~ "down30pct",
                     pop_interp_pct_change > 0.3 ~ "up30pct",
                     TRUE                        ~ "mid"),
         .by = c(GEOID_TR20, agegroup)) %>% 
  mutate(agegroup = sort_by_char_nums(agegroup))

ests_with_forecast_change %>% 
  filter(GEOID_TR20 %in% sample(GEOID_TR20, 200)) %>% 
  ggplot(aes(x = year,
             y = pop_interp,
             group = GEOID_TR20,
             color = change_cat)) +
  geom_line(alpha = 0.1) +
  geom_vline(xintercept = 2020.5,
             color = "red") +
  geom_hline(yintercept = 0,
             color = "red") +
  scale_x_continuous(breaks = 2010:(base_year+1),
                     labels = 2010:(base_year+1)) +
  scale_color_manual(breaks = c("down30pct", "mid", "up30pct"),
                     values = c("red", "black", "green")) +
  facet_wrap(~ agegroup,
             scales = "free") +
  theme_minimal()

# Examine distribution of amounts of change from 2010 to 
ests_with_forecast_change %>% 
  select(GEOID_TR20, agegroup, pop_interp_pct_change) %>% 
  unique() %>% 
  ggplot(aes(x = pop_interp_pct_change,
             color = agegroup)) +
  geom_density() + 
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent,
                     limits = c(-1.0, 1.0)) +
  labs(title = glue("Distribution of Changes in Overall Population Between 2010 and {base_year+1}, by Age"),
       x = "Percent Change",
       y = "") +
  theme_minimal()
```

```{r examine time path of pct 0-2 out of under 6}
pcts_0to5 <-
  ests_with_forecast %>% 
  filter(agegroup %in% as.character(0:5)) %>% 
  mutate(pct = pop_interp / sum(pop_interp),
         .by = c(GEOID_TR20, year))

pcts_0to5 %>%
  filter(agegroup %in% as.character(c(0:2))) %>%
  summarize(pct_02of0to5 = sum(pct),
            .by = c(GEOID_TR20, year)) %>% 
  ggplot(aes(x = year,
             y = pct_02of0to5,
             group = GEOID_TR20)) +
  geom_line(alpha = 0.1) +
  scale_y_continuous(labels = percent) +
  theme_minimal()

```

```{r examine breakdown of ages based on size of the under 6 population}
breakdown_02 <- 
  pcts_0to5 %>%
  filter(agegroup %in% 0:2,
         year %in% base_year:(base_year+1)) %>% 
  summarize(pop_interp = sum(pop_interp),
            pct = sum(pct),
            .by = c(GEOID_TR20, year))

# Examine breakdown vs population for base year and year after
breakdown_02 %>% 
  ggplot(aes(x = pop_interp,
             y = pct,
             color = factor(year))) +
  geom_point(alpha = 0.2) +
  geom_smooth() +
  scale_y_continuous(labels = percent) +
  theme_minimal()

# Examine in base year vs year after
breakdown_02 %>% 
  pivot_wider(values_from = c("pop_interp", "pct"),
              names_from = "year") %>% 
  ggplot(aes(x = get(glue("pct_{base_year}")),
             y = get(glue("pct_{base_year+1}")))) +
  geom_point(alpha = 0.2) +
  geom_smooth() +
  scale_y_continuous(labels = percent) +
  labs(title = "Age 0-2 as % of All Ages <5",
       x = base_year,
       y = base_year + 1) +
  theme_minimal()

```

```{r reshape long by age and save with GEOID_tr20}
# Generate a cut of population data wide by year, long by age
ests_with_forecast_wide <-
  ests_with_forecast %>% 
  pivot_wider(id_cols = c(GEOID_TR20, agegroup), 
              names_from = year,
              names_prefix = "est",
              values_from = pop_interp)

write.csv(ests_with_forecast_wide,
           glue("{output_path}est_age0017_2010_{base_year + 1}_{my_output_tag}.csv"), 
           row.names = FALSE)

```

```{r reshape long by year and save with GEOID_tr20}
# Generate a cut of population data wide by age, long by year
pop_by_age <- 
  ests_with_forecast %>% 
  mutate(GEOID_TR20 = as.character(GEOID_TR20),
         age        = case_when(agegroup == "0"    ~ "age_0_count",
                                agegroup == "1"    ~ "age_1_count",
                                agegroup == "2"    ~ "age_2_count",
                                agegroup == "3"    ~ "age_3_count",
                                agegroup == "4"    ~ "age_4_count",
                                agegroup == "5"    ~ "age_5_count",
                                agegroup == "612"  ~ "age_6to12_count",
                                agegroup == "1317" ~ "age_13to17_count")) %>% 
  summarize(pop_interp = sum(pop_interp),
            .by = c(GEOID_TR20, year, age)) %>% 
  pivot_wider(names_from  = "age",
              values_from = "pop_interp") %>% 
  mutate(age_0to5_count = age_0_count + age_1_count + age_2_count + age_3_count + age_4_count + age_5_count,
         age_3to5_count = age_3_count + age_4_count + age_5_count)

```

```{r compare these population estimates to those in ACS5, eval = developer_mode}
load(glue("{output_path}acs5_data_{my_output_tag}.Rda"))

comp_pop <- 
  pop_by_age %>% 
  filter(year == acs5_year - 2) %>% # midpoint of the ACS5 data that currently have been pulled
  pivot_longer(cols = -c(GEOID_TR20, year)) %>% 
  merge(acs5tract %>% 
          select(GEOID_TR20 = GEOID, age_0to5_count, age_6to12_count) %>% 
          pivot_longer(cols = - GEOID_TR20),
        by = c("GEOID_TR20", "name"),
        suffixes = c(".pop", ".acs5"))

ggplot(comp_pop,
       aes(x = value.acs5,
           y = value.pop)) +
  geom_point(alpha = 0.3) + 
  geom_abline(color = "blue") +
  geom_smooth(color = "red") +
  facet_wrap(~name) +
  theme_minimal()
```

```{r save long-by-year population data}
save(pop_by_age,
     file = glue("{output_path}pop_data_{my_output_tag}.Rda"))
```

```{r census tract10 to tract20 crosswalk}
# See this link, and search for "Census Tract Relationship Files":
#   https://www.census.gov/geographies/reference-files/time-series/geo/relationship-files.html
# Documentation is here:
#   https://www2.census.gov/geo/pdfs/maps-data/data/rel2020/tract/explanation_tab20_tract20_tract10.pdf
rel_tr2020_tr2010 <- 
  fread("https://www2.census.gov/geo/docs/maps-data/data/rel2020/tract/tab20_tract20_tract10_natl.txt") %>% 
  mutate(GEOID_TR20 = str_pad(GEOID_TRACT_20, width = 11, side = "left", pad = "0"),
         GEOID_TR10 = str_pad(GEOID_TRACT_10, width = 11, side = "left", pad = "0"),
         statefip   = substr(GEOID_TR20, 1, 2)) %>%
  filter(statefip == my_state_fip) %>% 
  select(GEOID_TR20, GEOID_TR10, AREALAND_TRACT_20, AREALAND_TRACT_10) %>% 
  mutate(GEOID_TR20        = as.character(GEOID_TR20),
         GEOID_TR10        = as.character(GEOID_TR10),
         AREALAND_TRACT_20 = as.numeric(AREALAND_TRACT_20),
         AREALAND_TRACT_10 = as.numeric(AREALAND_TRACT_10)) %>% 
  mutate(pct_10_in_20 = AREALAND_TRACT_10 / sum(AREALAND_TRACT_10),
         .by = GEOID_TR20) %>% 
  mutate(pct_20_in_10 = AREALAND_TRACT_20 / sum(AREALAND_TRACT_20),
         .by = GEOID_TR10)
```


```{r reapportion population estimates to 2010 census geographies if the base year is 2021 or before}

# A base year of 2021 or earlier implies use of 2010 census geographies, given 
# that ACS1 data--the key driver in the data pulls--only changed to 2020 geographies
# in 2022.
if (base_year <= 2021) {
  rel_tr2010_tr2020 <- 
    fread("https://www2.census.gov/geo/docs/maps-data/data/rel2020/tract/tab20_tract20_tract10_natl.txt", sep = "|") %>% 
    mutate(GEOID_TR10        = str_pad(GEOID_TRACT_10, width = 11, side = "left", pad = "0"),
           GEOID_TR20        = str_pad(GEOID_TRACT_20, width = 11, side = "left", pad = "0"),
           statefip          = substr(GEOID_TR20, 1, 2),
           AREALAND_PART     = as.numeric(AREALAND_PART),
           AREALAND_TRACT_20 = as.numeric(AREALAND_TRACT_20)
            # Note -- the `as.numeric()` functions are necessary to convert values
            # from integer64 values, which can cause errors in calculation
           ) %>% 
    filter(statefip == my_state_fip) %>% 
    mutate(part_of_20 = AREALAND_PART / AREALAND_TRACT_20) %>% 
    select(GEOID_TR10, GEOID_TR20, part_of_20)
  
  if (FALSE) {
    intersected_geos <- 
      rel_tr2010_tr2020 %>% 
      filter(0 < part_of_20 & part_of_20 < 1) %>% 
      pull(GEOID_TR20)
    
    rel_tr2010_tr2020 %>% 
      filter(GEOID_TR20 %in% intersected_geos)
  }
  
  pop_by_age <- 
    pop_by_age %>% 
    pivot_longer(cols = -c(GEOID_TR20, year),
                 names_to = "age") %>% 
    merge(rel_tr2010_tr2020 %>% select(GEOID_TR20, GEOID_TR10, part_of_20),
          by = "GEOID_TR20",
          all.x = TRUE) %>% 
    mutate(value = value * part_of_20) %>% 
    summarize(value = sum(value),
              .by = c(GEOID_TR10, age, year)) %>% 
      pivot_wider(names_from = age)

  save(pop_by_age,
       file = glue("{output_path}pop_data_{my_output_tag}.Rda"))
}

```


```{r inspect crosswalk NAs, eval = developer_mode}
(na_pcts <- 
   rel_tr2020_tr2010 %>% 
   filter(is.na(pct_10_in_20) | is.na(pct_20_in_10)))

with(na_pcts, all(c(AREALAND_TRACT_20, AREALAND_TRACT_10) == 0))
# In these cases, seems that the areas are all 0. 
```

