
<!-- This .Rmd file is set up to run either independently by checking for 
the presence of necessary objects in the global environment and running 
related scripts if not, or also as a child to the "main-doc". For that latter
reason, comments and headings that are not relevant to a final report to
pubic audiences are suppressed or moved to code chunks that can optionally be 
`echo`ed as desired. -->

```{r}
# set flags for running this script
print_documentation <- FALSE
```

```{r}
# run scripts for necessary packages and objects as necessary
if (!"meanNA"        %in% objects()) source("settings--main.R", echo = FALSE)
if (!"my_state_abbr" %in% objects()) source("method--read-customization-file.R", echo = FALSE)
if (!"bin_age"       %in% objects()) source("method--general-helper-functions.R", echo = FALSE)

load(glue("{output_path}geo_data_{my_output_tag}.Rda"))

source("method--pull-and-process-acs5.R")

```


# Pull and Merge ACS5 Tables for Auxiliary Predictions in the SAE

```{r}

if (!exists("my_county_fip")) {
  county_arg <- NULL
} else {
  county_arg <- my_county_fip
}

pull_my_table <- 
  function(
    my_table) {
    pull_table(
      my_table,
      state = my_state_abbr, 
      county = county_arg,
      year = acs5_year
    )
  }
```


## Total Population

```{r}
acs5_pop_pull <- pull_my_table("B01003")
    
inspect_fields(
  acs5_pop_pull, 
  show_all_combos = TRUE
)

acs5_pop <- 
  acs5_pop_pull %>% 
  select(
    GEOID,
    tot_pop    = estimate,
    tot_pop_se = se
  )

```


## Sex by Age

```{r}
acs5_sex_by_age_pull <- pull_my_table("B01001")
    
inspect_fields(
  acs5_sex_by_age_pull, 
  show_all_combos = TRUE
)

acs5_pop_by_age <- 
  acs5_sex_by_age_pull %>% 
  filter(
    age != "All"
  ) %>% 
  construct_fields(
    numerator = "age"
  )
  
```


## Population Under 18 Years of Age

```{r}

acs5_pop_lt18_pull <- pull_my_table("B09001")
    
inspect_fields(
  acs5_pop_lt18_pull, 
  show_all_combos = TRUE
)

acs5_pop_by_age_lt18 <- 
  acs5_pop_lt18_pull %>% 
  filter(
    age != "All",
    residence_type != "InGQ"
  ) %>% 
  construct_fields(
    numerator = "age"
  )

```


## Poverty Status in Past 12 Months by Sex by Age

```{r}
acs5_pov_bySexAge_pull <- pull_my_table("B17001")
    
inspect_fields(
  acs5_pov_bySexAge_pull, 
  show_all_combos = TRUE
)

acs5_pov_bySexAge <- 
  acs5_pov_bySexAge_pull %>% 
  filter(
    age != "All",
  ) %>% 
  construct_fields(
    numerator = "pov_status",
    by_vars = c("sex", "age")
  )

# Check
acs5_pov_bySexAge %>% 
  select(matches("^r.+Female_Age0to5")) %>% 
  head()

```


## Poverty status in past 12 months by household type by number of related children under 18

```{r}

acs5_pov_byNumKids_pull <- pull_my_table("B17012")

inspect_fields(
  acs5_pov_byNumKids_pull, 
  show_all_combos = TRUE
)

acs5_hhtype <- 
  acs5_pov_byNumKids_pull %>% 
  filter(
    own_kids_under18 == "All",
    pov_status != "All",
    !family_type %in% c("All", "Unmarried")
  ) %>% 
  construct_fields(
    numerator = "family_type"
  )

```


## Age by Ratio of Income to Poverty

```{r}

acs5_incpov_byage_pull <- pull_my_table("B17024")
    
inspect_fields(
  acs5_incpov_byage_pull, 
  show_all_combos = TRUE
)

acs5_incpov_byage_prep <- 
  acs5_incpov_byage_pull %>% 
  mutate(
    age =
      case_when(
        age == "Age0to6"                         ~ "Age0to6",
        str_detect(age, "Age(6to11|12to17)")     ~ "Age6to17",
        str_detect(age, "Age(18|25|35|45|55)to") ~ "Age18to64",
        str_detect(age, "Age(65|75)to")          ~ "AgeGe65",
        TRUE                                     ~ age
      )
  )

acs5_incpov_byage <- 
  acs5_incpov_byage_prep %>% 
  mutate(
    inc_to_pov_ratio = 
      case_when(
        str_detect(inc_to_pov_ratio, "Pov(50|75)to") ~ "IncPov50to100",
        TRUE ~ inc_to_pov_ratio
      )
  ) %>% 
  filter(
    age != "All",
    inc_to_pov_ratio != "All"
  ) %>% 
  construct_fields(
    numerator = "inc_to_pov_ratio",
    by_vars = "age"
  )

#stopifnot(all(acs5_incpov_byage %>% select(matches("^r.+_Age0to6")) %>% apply(1, sum) == 1))

# Create a different partition
acs5_incpov_byage_alt <- 
  acs5_incpov_byage_prep %>% 
  filter(
    age != "All",
    inc_to_pov_ratio != "All"
  ) %>% 
  mutate(
    inc_to_pov_ratio_alt = 
      case_when(
        str_detect(inc_to_pov_ratio, "Pov(0|50|75)to")          ~ "IncPov0to100",
        str_detect(inc_to_pov_ratio, "(100|125|150|175|185)to") ~ "IncPov100to199",
        str_detect(inc_to_pov_ratio, "(200|300)to")             ~ "IncPov200to399",
        str_detect(inc_to_pov_ratio, "(400to|500)")             ~ "IncPov400plus"
      )
  )

# Check the reassignment
if (FALSE) {
  acs5_incpov_byage_alt %>% select(matches("inc_to")) %>% unique()
}

acs5_incpov_byage_alt <- 
  acs5_incpov_byage_alt %>% 
  construct_fields(
    numerator = "inc_to_pov_ratio_alt",
    by_vars = "age"
  )

#stopifnot(all(acs5_incpov_byage_alt %>% select(matches("^r.+_Age0to6")) %>% apply(1, sum) == 1))

# Combine the different partitions
acs5_incpov_byage_out <- 
  merge(
    x = acs5_incpov_byage,
    y = acs5_incpov_byage_alt,
    by = "GEOID"
  )

```

## Ratio of Income to Poverty Level of Families in the Last 12 Months

```{r}

acs5_incpov_fam_pull <- pull_my_table("B17026")
    
inspect_fields(
  acs5_incpov_fam_pull, 
  show_all_combos = TRUE
)

acs5_incpov_byage <- 
  acs5_incpov_fam_pull %>% 
  filter(
    inc_to_pov_ratio != "All"
  ) %>% 
  construct_fields(
    numerator = "inc_to_pov_ratio"
  )

# Create an alternate partition
acs5_incpov_byage <- 
  acs5_incpov_fam_pull %>% 
  filter(
    inc_to_pov_ratio != "All"
  )

```

## Hispanic or Latino Origin by Race

```{r}
acs5_raceeth_pull <- pull_my_table("B03002")
    
inspect_fields(
  acs5_raceeth_pull, 
  show_all_combos = TRUE
)

acs5_raceeth4 <- 
  acs5_raceeth_pull %>% 
  filter(
    race != "All",
    hispanic != "Hisp"
  ) %>% 
  mutate(
    raceeth4 = 
      case_when(
        hispanic == "Hisp" ~ "Hisp",
        race     == "Wh"   ~ "White",
        race     == "Aa"   ~ "Black",
        TRUE               ~ "Other"
      )
  ) %>% 
  construct_fields(
    numerator = "raceeth4"
  )


```

<!-- ## Sex of Workers by Means of Transportation to Work -->

<!-- ```{r} -->
<!-- B08006 -->
<!-- ``` -->

<!-- ## Aggregate travel time to work of Workers by Sex -->

<!-- ```{r} -->
<!-- B08013 -->
<!-- ``` -->

<!-- ## Grandparents Living with Own Grandchildren Under 18 by Responsibility for Own Grandchildren by Presence of Parent of Grandchildren and Age of Grandparent -->

<!-- ```{r} -->
<!-- B10051 -->
<!-- ``` -->

<!-- ## Households with grandparent living with own grandchildren under 18 years by responsibility for own grandchildren by presence of grandchildren and presence of parent of grandchildren -->

<!-- ```{r} -->
<!-- B10063  -->
<!-- ``` -->


## Sex by Age by Employment Status for the Population 16 and Over

```{r}
acs5_empl_pull <- pull_my_table("B23001")
    
inspect_fields(
  acs5_empl_pull, 
  show_all_combos = TRUE
)

acs5_empl_prep_Age22to64 <- 
  acs5_empl_pull %>% 
  filter(
    sex != "All",
    #str_detect(age, "Age(22|25|30|35|45|55|60|62)to")
    str_detect(age, "Age25|Age30")
    # /!\ Need to remove this after performing checks against the old acs5 constructions
  )

acs5_empl <- 
  acs5_empl_prep_Age22to64 %>% 
  filter(
    lfp == "InLF",
    pop == "Civilian",
    status != "All"
  ) %>% 
  construct_fields(
    numerator = "status", 
    by_vars = c("sex")
  ) %>% 
  select(
    -matches("Unempl")
  )

acs5_empl_inclMilit <- 
  acs5_empl_prep_Age22to64 %>% 
  mutate(
    status = if_else(pop == "Military", "Empl", status),
    status = 
      case_match(
        status, 
        "Empl" ~ "EmplInclMilit", 
        .default = status
      )
  ) %>% 
  filter(
    lfp == "InLF",
    pop %in% c("Civilian", "Military"),
    status != "All"
  ) %>% 
  construct_fields(
    numerator = "status", 
    by_vars = c("sex")
  ) %>% 
  select(
    -matches("Unempl")
  )

acs5_lfrate <- 
  acs5_empl_prep_Age22to64 %>% 
  filter(
    (lfp == "InLF" & pop == "Civilian") |
    (lfp == "NotInLF"),
    status == "All"
  ) %>% 
  select(
    -pop, -status
  ) %>% 
  construct_fields(
    numerator = "lfp", 
    by_vars = c("sex")
  )

acs5_lfrate_inclMilit <- 
  acs5_empl_prep_Age22to64 %>% 
  filter(
    lfp != "All",
    pop == "All"
  ) %>%
  mutate(
    lfp = 
      case_match(
        lfp,
        "InLF" ~ "InLFOrMilit",
        "NotInLF" ~ "NotInLFOrMilit"
      )
  ) %>% 
  construct_fields(
    numerator = "lfp", 
    by_vars = c("sex")
  ) %>% 
  select(
    -matches("NotIn")
  )

```

## Sex by Educational Attainment for Population 25 Years and Older

```{r}
acs5_edattain_pull <- pull_my_table("B15002")
    
inspect_fields(
  acs5_edattain_pull, 
  show_all_combos = TRUE
)

acs5_edattain_bySex <- 
  acs5_edattain_pull %>% 
  filter(
    sex != "All"
  ) %>% 
  construct_fields(
    numerator = "ed_attain",
    by_vars = "sex"
  )

acs5_edattain <- 
  acs5_edattain_pull %>% 
  filter(
    sex != "All"
  ) %>% 
  construct_fields(
    numerator = "ed_attain"
  )

```


```{r collect}
acs5_tomerge <- 
  list(
    acs5_pop_by_age, 
    acs5_pop_by_age_lt18, 
    #acs5_pov_bySexAge, 
    acs5_incpov_byage_out, 
    acs5_raceeth4, 
    acs5_hhtype,
    acs5_empl, 
    acs5_empl_inclMilit,
    acs5_lfrate, 
    acs5_lfrate_inclMilit, 
    acs5_edattain,
    acs5_edattain_bySex
  )

# Retain only rate and std err of rate calculations
acs5_tomerge <- lapply(acs5_tomerge, \(x) select(x, matches("GEOID|^(r|se_r|w|n)")))

merge_reduce <- function(x, y) merge(x, y, by = "GEOID")

acs5 <- Reduce(merge_reduce, acs5_tomerge)
```

```{r}
save(acs5tract, acs5puma,
     file = glue("{output_path}acs5_data_{my_output_tag}.Rda"))
```

# Prepare Tables Used for Correlation of Income and Work Eligibility

```{r prepare county argument for fresh pull of acs5 data}
if (exists("my_county_fip")) county_val <- my_county_fip else county_val <- NULL
```

```{r fresh pull of both income and work status tables}
# "Age by Ratio of Income to Poverty Level In the Past 12 Months"
acs5_incpov_byage_raw    <- pull_table("B17024", state = my_state_abbr, county = county_val, year = acs5_year)

# "Presence of Own Children Under 18 Years by Family Type by Employment Status"
acs5_famconfig_wKids_raw <- pull_table("B23007", state = my_state_abbr, county = county_val, year = acs5_year)

```

```{r determine closest fpl cutoff to ccdf eligibility threshold}
ccdf_inc_thresh_fpl <- get_fpl_thresh_for_ccdf()

# Determine which inc-to-pov value from the tables is closest to the ccdf fpl
# cutoff
acs5_income_cutpoints <- c(0, 50, 75, 100, 125, 150, 175, 185, 200, 300, 400, 500)
dev <- 
  (acs5_income_cutpoints - ccdf_inc_thresh_fpl) %>% 
  abs()

nearest_incpov_cutpoint_to_ccdf <- 
  acs5_income_cutpoints[which(dev == min(dev))]
```

```{r perform basic incpov calculations}
acs5_incpov_byage_wide <- 
  construct_fields(
    df = acs5_incpov_byage_raw,
    numerator = "inc_to_pov_ratio",
    by_vars = "age",
    subset_cond = "age %in% c('Age0to6', 'Age6to11')",
    subset_descr = "")

acs5_incpov_byage <- 
  construct_fields(
    df = acs5_incpov_byage_raw,
    numerator = "inc_to_pov_ratio",
    by_vars = "age",
    subset_cond = "age %in% c('Age0to6', 'Age6to11')",
    subset_descr = "", 
    wide = FALSE)
```

```{r construct desired work eligibility field}
inspect_fields(acs5_famconfig_wKids_raw)

# /!\ These constructions have problems with respect handling complicated
# and non-parallel hierarchies in the "InLfp" field
# acs5_workelig_withKids_old_wide <- 
#   construct_fields(
#     df = acs5_famconfig_wKids_raw,
#     subset_cond = "own_kids_under18 == 'SomeKidsUnder18'",
#     #denom_subset = "status == 'All'",
#     numerator = "status", 
#     numerator_vals = c("HusbandEmplWifeEmpl", "Empl"),
#     numerator_lab  = c("WorkEligFam"),
#     subset_descr = "")
# 
# acs5_workelig_withKids_old <- 
#   construct_fields(
#     df = acs5_famconfig_wKids_raw,
#     subset_cond = "own_kids_under18 == 'SomeKidsUnder18' & !(family_type == 'Married' & lfp %in% c('HusbandInLfp', 'HusbandNotInLfp'))",
#     #denom_subset = "status == 'All'",
#     numerator = "status", 
#     numerator_vals = c("HusbandEmplWifeEmpl", "Empl"),
#     numerator_lab  = c("WorkEligFam"),
#     subset_descr = "",
#     wide = FALSE)

# Calculating work eligibility by hand
acs5_workelig_withKids_denom <- 
  acs5_famconfig_wKids_raw %>% 
  filter(
    own_kids_under18 == "SomeKidsUnder18",
    family_type %in% c("Married", "UnmarriedMaleHh", "UnmarriedFemaleHh"),
    lfp == "All",
    status == "All"
  )

acs5_workelig_withKids_num <- 
  acs5_famconfig_wKids_raw %>% 
  filter(
    own_kids_under18 == "SomeKidsUnder18",
    (family_type == "Married" & status == "HusbandEmplWifeEmpl") | 
      (str_detect(family_type, "Unmarried") & status == "Empl")
  )

acs5_workelig_withKids <- 
  merge(
    acs5_workelig_withKids_num   %>% summarize(nEmpl = sum(estimate), .by = GEOID),
    acs5_workelig_withKids_denom %>% summarize(nAll  = sum(estimate), .by = GEOID),
    by = "GEOID"
  ) %>% 
  mutate(
    r = nEmpl / nAll,
    n = nEmpl,
    w = nAll,
    status = "WorkEligFam"
  )

acs5_workelig_withKids <- 
  bind_rows(
    acs5_workelig_withKids,
    acs5_workelig_withKids %>% mutate(r = 1 - r, n = w - n, status = "NotWorkEligFam")
  ) 

```


```{r merge together data sets intended for estimating ccdf eligibility}

save(list = c("acs5_incpov_byage", "acs5_workelig_withKids"), 
     file = glue("{output_path}acs5_ccdf_{my_output_tag}.Rda"))
```


