# Background

This R script is designed to read all of the customized settings that a user has provided in a given Excel interface to ELPEP, and to set off programming code.

To run this script--and consequently ELPEP:

1. provide the name of Excel file that contains your customizations in the indicated area of the gray box below, 
2. make sure that you have taken all other steps to download necessary files described at https://www.github.com/chapinhall/elpep, and then
3. in the menu above go to "Code >> Run Region >> Run All"

```{r user specified-elpep customization file}

elpep_customization_file <- "<your/excel/specfication/file/here/with/full/path.xlsm>"

```

```{r}
# These lines reset the run and load all packages necessary for further steps
rm(list = setdiff(ls(), "elpep_customization_file"))
source("settings--main.R")
```


```{r}
# This line runs a script to harvest all details specified in the customization file
source("method--read-customization-file.R")
```

```{r}
# This line loads functions used by multiple other scripts
source("method--general-helper-functions.R")
```


```{r}

# Running the command in the following `if (FALSE)` block will run all of 
# ELPEP's code and output all of the diagnostic checks in a stand-alone html file
# However, we recommend running each ELPEP script file in seequence--i.e. 01a, 
# 01b, ..., 02a, 02b, 03a, 03b, 03c--to pace out and monitor the run, and to
# ensure clarity on the location of an issue if one arises

if (FALSE) {
  rmarkdown::render(
    input = "run--00--main-doc.Rmd",
    output_file = glue("{output_path}ELPEP Technical Report -- {my_state} -- {my_output_tag}.html")
  )  
}

```


