
<!-- This .Rmd file is set up to run either independently by checking for 
the presence of necessary objects in the global environment and running 
related scripts if not, or also as a child to the "main-doc". For that latter
reason, comments and headings that are not relevant to a final report to
pubic audiences are suppressed or moved to code chunks that can optionally be 
`echo`ed as desired. -->

```{r}
# run scripts for necessary packages and objects as necessary
if (!"meanNA"        %in% objects()) source("settings--main.R", echo = FALSE)
if (!"my_state_abbr" %in% objects()) source("method--read-customization-file.R", echo = FALSE)
if (!"bin_age"       %in% objects()) source("method--general-helper-functions.R", echo = FALSE)
if (!"calc_cps_transitions" %in% objects()) source_rmd("method--nowcasting-functions.Rmd", echo = FALSE)
```

```{r load final results from now-casting and select a sensitivity}
load(file = glue("{output_path}Eligibility estimates using conditional transition ratio - {my_output_tag}.Rda"))
load(file = glue("{output_path}pop_data_{my_output_tag}.Rda"))
load(file = glue("{output_path}geo_data_{my_output_tag}.Rda"))
load(file = glue("{output_path}acs5_data_{my_output_tag}.Rda"))
load(file = glue("{output_path}cps_data_{my_output_tag}.Rda"))
```

```{r select a sensitivity}

# Below, there are several `if` clauses that already implement--and describe--
# logic for selecting a sensitivity specific for each of several run specifications

# If a county has been provided, we assume that it is for a higher density area,
# and that the use of the 'metropolitan areas' subset of CPS data is appropriate
nowcast_selected_sens <-
  nowcast_out_trunc[cps_geo_subsample == ifelse(exists("my_county"), "metros", "none")]

```


```{r generate parallel constructions for base (sae) and nowcast}
# Establish a general setup of parallel field names

nowcast_parallel_setup <- 
  nowcast_selected_sens %>%
  # /!\ Need to produce/bring in standard errors for the SAE. Assigning these 0
  # as a placeholder.
  mutate(
    base_share_se    = 0,
    nowcast_share    = elig_share,
    nowcast_share_se = elig_share_se
  )

# For each output, select the sensitivity and (calculation of) related measure
# /!\ These related `base_share` measures are, in many cases, not aligned with
# the estimated measures themselves (and so we set them as NA).
# This is because the only `share_#_#` predictors that are carried along are 
# those that were predicted in the SAE estimation. The most direct updated
# step would be to produce different runs of the SAE, although this is currently
# highly time-consuming.

# nowcast_parallel_incpov_019_le130 <-
#   nowcast_parallel_setup %>%
#   filter(
#     outcome_var == "bIncpov_le130",
#     str_detect(sae_spec, "019_inc$"),
#     age == "Age0to19"
#   ) %>%
#   mutate(base_share = share_0_75 + share_75_130)
# 
# nowcast_parallel_incpov_019_le205 <-
#   nowcast_parallel_setup %>%
#   filter(
#     outcome_var == "bIncpov_le205",
#     str_detect(sae_spec, "019_inc$"),
#     age == "Age0to19"
#   ) %>%
#   mutate(base_share = share_0_75 + share_75_130 + share_130_200)

nowcast_parallel_incpov_2064_le130 <- 
  nowcast_parallel_setup %>% 
  filter(
    outcome_var == "bIncpov_le130",
    str_detect(sae_spec, "inc$"),
    age == "Age20to64"
  ) %>% 
  mutate(
    base_share = share_0_75 + share_75_130
  )

nowcast_parallel_incpov_2064_le138 <- 
  nowcast_parallel_setup %>% 
  filter(
    outcome_var == "bIncpov_le138",
    str_detect(sae_spec, "inc$"),
    age == "Age20to64"
  ) %>% 
  mutate(
    # This is approximate
    base_share = share_0_75 + share_75_130
  )

bind_list <- 
  list(
    # nowcast_parallel_incpov_019_le130,
    # nowcast_parallel_incpov_019_le205,
    nowcast_parallel_incpov_2064_le130,
    nowcast_parallel_incpov_2064_le138
  )

```

```{r add all relevant prog sensitivities}

incwork_specs <- nowcast_parallel_setup$outcome_var %>% str_subset("bProg_") %>% unique()

for (incwork_spec in incwork_specs) {
  
  sensitivity_to_add <- 
    nowcast_parallel_setup %>% 
    filter(
      outcome_var == incwork_spec,
      str_detect(sae_spec, "incwork")
    )
 
  # /*\ This may need to be updated, depending on how categories are set in the
  # SAE data
  if (str_detect(incwork_spec, as.character(local_prog_incratio_base))) {
    # get the name of the "share_WorkElig_100_(prog thresh in FPL units)
    hs_prog_field <- 
      sub_cn(
        nowcast_parallel_setup, 
        "share_WorkElig_100_"
      )
    sensitivity_to_add <- 
      sensitivity_to_add %>% 
      mutate(
        base_share = share_WorkElig_0_100 + get(hs_prog_field)
      )
  } else {
    sensitivity_to_add <- 
      sensitivity_to_add
      mutate(
        base_share = NA
      )
  }
  
  bind_list <- 
    append(
      bind_list, 
      list(sensitivity_to_add)
    )
}

```



```{r combined the parallel constructions for base (sae) and nowcast}

# Generate parallel base/nowcast constructions wide by base/now measures 
nowcast_parallel_preshape <- 
  bind_rows(bind_list) %>% 
  select(
    GEOID, cps_base_recency, outcome_var, age, 
    base_share, base_share_se, 
    nowcast_share, nowcast_share_se
  ) %>% 
  # /!\ ** This unique() should not be necessary. However, it's occurring because
  # there are duplicates resulting from a merge of the crosswalk file, due to
  # overlaps with ZCTAs. There should be a cleaner, unique crosswalk of census
  # shapes--tract, PUMA, and County--with other crosswalks occurring later, as needed.
  unique()

# Reshape to long format, with only different stats wide
nowcast_parallel <- 
  nowcast_parallel_preshape %>% 
  pivot_longer(
    cols = matches("share")
  ) %>% 
  separate(
    col = name, 
    into = c("pd", "stat"),
    sep = "_",
    extra = "merge"
  ) %>% 
  pivot_wider(
    names_from = stat,
    values_from = value
  )
```

```{r merge population stats to calculate counts}
# Identify the year of the latest CPS data
latest_cps_year <- max(cps_post$YEAR)

# /!\ The new strategy for calibrating overall populations currently only produces
# `base_year` population estimates. Some further adaptation needs to be made to
# adapt this strategy to a second year, in order to produce estimates that would
# variously apply to the base or nowcast years.
# Despite this limitation, we note that this method (for the single year) very
# likely produces estimates that are overall more principled than the prior method

pop_by_age_long <- 
  pop_age_t_calib %>% 
  rename(
    pop_count = calib,
    age = age_var
  ) %>% 
  mutate(
    age = str_replace(age, "^n", ""),
    # pd = case_when(year == latest_cps_year - 1 ~ "base",
    #                year == latest_cps_year     ~ "nowcast")) %>% 
    # /!\ Here again is where we need to bring in a proper standard error for
    # population count estimates
    pop_count_se = 0
  )

# /!\ As in the note above in this chunk we also lack the ability to create this
# the school-year aligned blend of multiple years, when only a single (calendar)
# year has been estimates.
# Thus: throw an error if `sy` recency is requested
stopifnot(!any("sy" %in% nowcast_parallel$cps_base_recency))

# Create a school-year aligned blend of population
# pop_by_age_long_sy <- 
#   pop_by_age_long %>% 
#   arrange(GEOID, age, year) %>% 
#   mutate(
#     .by = c(GEOID, age),
#     pop_count_lag1    = shift(pop_count,    type = "lag"),
#     pop_count_se_lag1 = shift(pop_count_se, type = "lag")) %>% 
#   # To calculate a school-year aligned population count, we recognize that the 
#   # age data are reported by calendar year, that we assume that birthdays are
#   # uniformly distributed across the calendar year, and that 6 year olds in the
#   # 2024-25 school year--for example--are 2/3 those who turn 6 in 2024 (i.e. the
#   # 8 months before September 1 2024, and 1/3 of those who turned 6 in the 4
#   # months after September 1, 2023. We carry this calculation to all years and
#   # ages.
#   mutate(
#     pop_count_sy    = (2/3)*pop_count    + (1/3)*pop_count_lag1,
#     pop_count_se_sy = (2/3)*pop_count_se + (1/3)*pop_count_se_lag1) 

pop_by_age_long_recency <- 
  bind_rows(
    pop_by_age_long %>% mutate(cps_base_recency = "allbase"),
    pop_by_age_long %>% mutate(cps_base_recency = "most_recent")
    # pop_by_age_long_sy %>% 
    #   select(GEOID, year, age, pd, pop_count = pop_count_sy, pop_count_se = pop_count_se_sy) %>% 
    #   mutate(cps_base_recency = "sy")
  )

nowcast_parallel_counts <- 
  nowcast_parallel %>% 
  
  merge(
    pop_by_age_long_recency,
    by = c("GEOID", "age", "cps_base_recency"), # "pd"
    all.x = TRUE) %>% 
  data.table() %>%
  mutate(
    count    = share*pop_count,
    count_se = se_product(share, pop_count, share_se, pop_count_se)
  )
```

```{r save results}
save(
  nowcast_parallel_counts,
  most_recent_months, most_recent_sy_months, 
  pop_by_age_long_recency,
  file = glue("{output_path}Now-cast counts at the tract level, pre-disaggregation - {my_output_tag}.Rda")
)
```

```{r reshape measures long}
share_pre_post <- 
  nowcast_parallel_counts %>% 
  select(-year) %>% 
  pivot_longer(
    cols = matches("share|count")
  ) %>% 
  unite(
    wide_name, name, pd, sep = "_"
  ) %>% 
  pivot_wider(
    names_from = wide_name,
    values_from = value
  )
```

### Map Now-cast Estimates

```{r generate maps for now-cast estimates, fig.height = 12}
tractShp %>% 
  merge(share_pre_post, 
        by = "GEOID") %>%
  #filter(outcome_var %like% "le50",
  filter(grepl(paste("le50|le100|", local_ccdf_incratio_base, "$", sep = ""), outcome_var),
         cps_base_recency == "most_recent",
         age == "age_0to5") %>%
  ggplot(aes(fill = share_nowcast)) +
  geom_sf(color = NA) +
  facet_wrap(~ outcome_var) +
  theme_void() +
  theme(strip.text = element_text(size = 14))

```



### Examine Now-cast Estimates versus Base-Year (SAE) Estimates

We compare now-cast estimates to baseline SAE estimates for only Head Start eligibility, because in the SAE estimates we do not currently estimate <50% as its own threshold, nor income measures directly connected to CCDF eligibility.

```{r function to compare now-cast vs SAE}
comp_nowcast_vs_sae <- function(share_ests, title, xlab, ylab, save_tag) {
  
  my_plot <- 
    ggplot(share_ests %>% filter(cps_base_recency == "allbase"),
           aes(x = share_base,
               y = share_nowcast)) +
    geom_point(alpha = 0.2) +
    geom_abline(color = "red") +
    geom_smooth(se = FALSE,
                color = "blue") +
    # facet_wrap(~ sae_spec) +
    scale_x_continuous(labels = percent) +
    scale_y_continuous(labels = percent) +
    labs(title = title,
         x = xlab,
         y = ylab) +
    theme_minimal() +
    theme(legend.position = "bottom",
          axis.text = element_text(size = 11))
  
  if (save_tag != "") {
    ggsave(plot = my_plot,
           filename = glue("{output_path}nowcast_vs_sae_{my_output_tag}_{save_tag}.png"))
  }
  
  return(my_plot)
}
```

```{r compare now-cast vs SAE for deep poverty}
comp_nowcast_vs_sae(share_ests = share_pre_post %>% filter(str_detect(outcome_var, "incpov_le50")),
                    title = case_when(my_output_tag == "IL" ~ "Tract-Level Now-Cast Estimates are Generally Above Baseline",
                                      TRUE ~ ""),
                    xlab = glue("Baseline (SAE) - {base_year}"),
                    ylab = glue("Now-Cast - {base_year+1}"),
                    save_tag = "incpov_le50")
```

```{r compare now-cast vs SAE for HS}
comp_nowcast_vs_sae(share_ests = share_pre_post %>% filter(str_detect(outcome_var, "incpov_le100")),
                    title = case_when(my_output_tag == "IL" ~ "Tract-Level Now-Cast Estimates are Generally Above Baseline",
                                      TRUE ~ ""),
                    xlab = glue("Baseline (SAE) - {base_year}"),
                    ylab = glue("Now-Cast - {base_year+1}"),
                    save_tag = "incpov_le100")
```

```{r compare now-cast vs SAE for CCAP}
comp_nowcast_vs_sae(share_ests = share_pre_post %>% filter(str_detect(outcome_var, glue("{local_ccdf_incratio_base}$"))),
                    title = case_when(my_output_tag == "IL" ~ "Tract-Level Now-Cast Estimates are Generally Above Baseline",
                                      TRUE ~ ""),
                    xlab = glue("Baseline (SAE) - {base_year}"),
                    ylab = glue("Now-Cast - {base_year+1}"),
                    save_tag = "ccdf_elig")
```


```{r add community characteristics}
share_pre_post_chars <- 
  left_join(share_pre_post, 
            acs5tract,
            by = "GEOID")
```

```{r function to plot diffs vs community characteristics}
plot_elig_diff_vs_char <- 
  function(outcome_string,
           outcome_desc,
           char_field,
           char_desc,
           save_tag = "") {
    dt_plot <-
      share_pre_post_chars %>% 
      filter(str_detect(outcome_var, outcome_string),
             cps_base_recency == "allbase")

    # If all y values are NAs--which can occur if the base share value has not
    # been specified--then return 0 and exit
    if (with(dt_plot, mean(is.na(share_nowcast - share_base)) == 1)) return(NULL)

    my_plot <- 
      ggplot(dt_plot,
             aes(x = get(char_field), # ed_lths
                 y = share_nowcast - share_base)) +
      geom_point(alpha = 0.2) +
      geom_hline(yintercept = 0,
                 color = "darkblue",
                 linewidth = 0.75) +
      geom_smooth(color = "red",
                  se = FALSE) +
      scale_x_continuous(label = percent) +
      scale_y_continuous(label = percent) +
      facet_wrap(~age) +
      labs(x = char_desc,
           y = glue("Change in {outcome_desc} - {base_year} to {base_year + 1}")) +
      theme_minimal()
    if (save_tag != "") {
      ggsave(plot = my_plot,
             filename = glue("{output_path}Difference in Eligibility in {outcome_desc} {save_tag}_{my_output_tag}.png"),
             width = 6,
             height = 4,
             units = "in")
    }
    print(my_plot)
  }
```


```{r}
plot_elig_diff_vs_char(outcome_string = "incpov_le100",
                       outcome_desc   = "HS Eligibility", 
                       char_field     = "raceeth_wh_nonh_est",
                       char_desc      = "% White Non-Hisp in Tract",
                       save_tag       = "by white residence")
```

```{r}
plot_elig_diff_vs_char(outcome_string = glue("ccdf_elig_incratio_{local_ccdf_incratio_base}"),
                       outcome_desc   = glue("{local_ccdf_name_short} Eligibility"), 
                       char_field     = "raceeth_wh_nonh_est",
                       char_desc      = "% White Non-Hisp in Tract",
                       save_tag       = "by white residence")
```

