
<!-- This .Rmd file is set up to run either independently by checking for 
the presence of necessary objects in the global environment and running 
related scripts if not, or also as a child to the "main-doc". For that latter
reason, comments and headings that are not relevant to a final report to
pubic audiences are suppressed or moved to code chunks that can optionally be 
`echo`ed as desired. -->

```{r}
# run scripts for necessary packages and objects as necessary
if (!"meanNA"        %in% objects()) source("settings--main.R", echo = FALSE)
if (!"my_state_abbr" %in% objects()) source("method--read-customization-file.R", echo = FALSE)
if (!"bin_age"       %in% objects()) source("method--general-helper-functions.R", echo = FALSE)
if (!"direct_est_tract"     %in% objects()) source_rmd("method--small-area-estimation-functions.Rmd", echo = FALSE)
```

```{r load data for SAE runs}
# Load prepped data
for (f in c("acs1", "acs5", "pop", "geo")) {
  load(file = glue("{output_path}{f}_data_{my_output_tag}.Rda"))
}
```

```{r function to show distribution}
show_acs1_cat_density <- function(my_cat, my_subtitle) {
  acs1_elig %>% 
    ggplot() +
    aes(
      x = get(my_cat)
    ) +
    geom_bar() +
    facet_wrap(
      ~ cAge,
      scales = "free"
    ) +
    labs(
      title = "Number of ACS1 Sample Observations by Category Scheme",
      subtitle = my_subtitle,
         x = ""
    ) +
    theme_minimal() + 
    theme(
      axis.text.x = element_text(angle = 90, hjust = 1)
    )
}

if (FALSE) {
  show_acs1_cat_density(
    "cFam_incpov_ratio_cat_with130",
    "Income-to-Poverty including 130%")
  show_acs1_cat_density(
    "cWorkThresh_incpov_status130", 
    "Combo of Family Work Eligibility and Income-to-Poverty Aligned with Program Eligibility Thresholds")
}
```


```{r function examine PUMA-level counts of each category}
show_acs1_cat_density_by_puma <- function(my_cat, my_subtitle) {
  acs1_elig %>% 
    mutate(
      cAge = sort_by_char_nums(cAge)
    ) %>% 
    ggplot() +
    aes(
      x = PUMA
    ) +
    geom_bar() +
    facet_wrap(
      ~ cAge + get(my_cat),
      #scales = "free_y"
    ) +
    labs(
      title = "Number of ACS1 Sample Observations by PUMA, by Age Group and Category",
      subtitle = my_subtitle,
      caption = "(Note: scale of y-axis varies to show detail)",
      y = "Count of Observations in ACS1 Sample"
    ) +
    theme_minimal() + 
    theme(
      axis.text.x = element_text(angle = 90, hjust = 1)
    )  
}

if (FALSE) {
  show_acs1_cat_density_by_puma(
    "cFam_incpov_ratio_cat_with130",
    "Income-to-Poverty Ratio including 130% Cuts")
  show_acs1_cat_density_by_puma(
    "cWorkThresh_incpov_status130", 
    "Combo of Family Work Eligibility and Income-to-Poverty Aligned with Program Eligibility Thresholds")
}
```


### Examine pattern contrasts between ACS1 and ACS5 measures

```{r compare the distribution of values}
# ACS1 data are naturally less variable than ACS5 because they reflect averages 
# up to the PUMA level. Thus, the red line below has "density" to the left of the 
# blue peak, and a longer trail of high values at the right. Those reflect tracts
# with values of poverty that are respectively lower and higher than the overall 
# range of PUMA-level values.
# 
# The orange line--representing PUMA-level aggregates of the ACS5 data--is closer 
# to the blue in the overall distribution. However, the fact that the blue line 
# is slightly shifted left captures the fact that PUMA-level poverty rates for 
# young children in `r base_year` are slightly lower than those in prior years.

acs1_puma_stats <- 
  acs1_elig %>% 
  summarize(
    .by = c(PUMA, cAge),
    rIncPov0to75_Age18to64_acs1 = sum(PWGTP[fam_incpov_ratio <= 0.75]) / sum(PWGTP)
  )
  
acs5puma <- 
  acs5tract %>% 
  merge(
    geo_crosswalk %>% select(GEOID, PUMA) %>% unique(),
    by = "GEOID"
  ) %>% 
  summarize(
    .by = PUMA,
    rIncPov0to75_Age18to64_acs5 = sum(nIncPov0to75_Age18to64) / sum(wIncPov0to75_Age18to64)
  )

ggplot() +
  # geom_density(
  #   data = acs1_puma_stats,
  #   aes(x = pct_pov),
  #   color = "blue"
  # ) +
  geom_density(
    data = acs5puma,
    aes(x = rIncPov0to75_Age18to64_acs5),
    color = "red"
  ) +
  geom_density(
    data = acs1_puma_stats,
    aes(
      x = rIncPov0to75_Age18to64_acs1,
      color = cAge
    )
  ) +
  scale_x_continuous(
    labels = percent
  ) + 
  labs(
    title = "Comparing Distributions of Income <75% FPL for Individuals Aged 18-64",
    # subtitle = glue("<span style='color:blue'>PUMA-level ACS1-year Data for {base_year}</span><br>",
    #                 "<span style='color:red'>Tract-level ACS5-year Data for {acs5_year-4}-{acs5_year}</span><br>",
    #                 "<span style='color:orange'>PUMA-level ACS5-year Data for {acs5_year-4}-{acs5_year}</span>"),
    # subtitle = glue("ACS1 data reflects PUMA-level values for {base_year}\n",
    #                 "ACS5 data reflects tract-level values for 2015-2019"),
    x = "Poverty Rate for Individuals Age 18-64",
    y = "Density of the Distribution"
  ) +
  theme_minimal() +
  theme(
    plot.subtitle = element_markdown(lineheight = 1.1)
  )
```


### Results of SAE Estimation

```{r set specifications for sae}

# /*\ Note that there is significant discretion in choices that can be made in
# these specifications, both for how ACS5 measures and crosstabbing with ages,
# as well as the age partitions for ACS1 data are set

sae_controls_incpov_stems <- 
  c(
    "rIncPov0to75",
    "rIncPov75to125",
    "rIncPov125to200",
    "rIncPov200to400"
  )

# /!\ These ages may not line up directly given limitations of reporting in ACS5 
# income-to-poverty by age tables. Because these are general predictors, that is
# not necessary
sae_controls_incpov_Age0to19 <-
  paste0(sae_controls_incpov_stems, "_Age0to17")

sae_controls_incpov_Age20to64 <- 
  paste0(sae_controls_incpov_stems, "_Age18to64")

sae_controls_incpov_Age65plus <- 
  paste0(sae_controls_incpov_stems, "_AgeGe65")

sae_controls_ed <- 
  c("rEduc_LtHs", "rEduc_SomeColl", "rEduc_Assoc", "rEduc_Coll", "rEduc_Grad") # reference: "rEduc_Hs"

sae_controls_workstatus <- 
  c("rEmpl_Male", "rEmpl_Female",
    "rUnmarriedFemaleHh", "rUnmarriedMaleHh") # reference: "rMarried", 

sae_controls_incwork_Age0to19 <- 
  c(sae_controls_incpov_Age0to19, sae_controls_ed, sae_controls_workstatus)

sae_controls_incwork_Age20to64 <- 
  c(sae_controls_incpov_Age20to64, sae_controls_ed, sae_controls_workstatus)


stopifnot(all(c(sae_controls_incpov_Age0to19,  sae_controls_incwork_Age0to19)  %in% colnames(acs5tract)))
stopifnot(all(c(sae_controls_incpov_Age20to64, sae_controls_incwork_Age20to64) %in% colnames(acs5tract)))
stopifnot(all(c(sae_controls_incpov_Age65plus)                                 %in% colnames(acs5tract)))

sae_controls_018_inc        <- c(sae_controls_incpov_Age0to19, sae_controls_ed)
sae_controls_018_incwork    <- c(sae_controls_incpov_Age0to19, sae_controls_ed, sae_controls_workstatus)

sae_controls_1925_inc       <- c(sae_controls_incpov_Age20to64, sae_controls_ed)
sae_controls_1925_incwork   <- c(sae_controls_incpov_Age20to64, sae_controls_ed, sae_controls_workstatus)

sae_controls_2644_inc       <- c(sae_controls_incpov_Age20to64, sae_controls_ed)
sae_controls_2644_incwork   <- c(sae_controls_incpov_Age20to64, sae_controls_ed, sae_controls_workstatus)

sae_controls_4564_inc       <- c(sae_controls_incpov_Age20to64, sae_controls_ed)
sae_controls_4564_incwork   <- c(sae_controls_incpov_Age20to64, sae_controls_ed, sae_controls_workstatus)

sae_controls_65_inc     <- c(sae_controls_incpov_Age65plus, sae_controls_ed)
sae_controls_65_incwork <- c(sae_controls_incpov_Age65plus, sae_controls_ed, sae_controls_workstatus)

```

```{r subset acs1 and acs5 data for the SAE}
acs1_elig <- mutate(acs1_elig, PUMA = pad_num_left(PUMA, 5))
stopifnot(all(geo_crosswalk$PUMA %in% acs1_elig$PUMA))

acs1_elig018_sae    <- filter(acs1_elig, between(AGEP,  0, 18))
acs1_elig1925_sae   <- filter(acs1_elig, between(AGEP, 19, 25))
acs1_elig2644_sae   <- filter(acs1_elig, between(AGEP, 26, 44))
acs1_elig4564_sae   <- filter(acs1_elig, between(AGEP, 45, 64))
acs1_elig65plus_sae <- filter(acs1_elig, AGEP >= 65)

acs5tract_sae <- 
  acs5tract %>% 
  select(
    all_of(
      c("GEOID",
        sae_controls_018_inc,
        sae_controls_018_incwork,
        sae_controls_1925_inc,
        sae_controls_1925_incwork,
        sae_controls_2644_inc,
        sae_controls_2644_incwork,
        sae_controls_4564_inc,
        sae_controls_4564_incwork,
        sae_controls_65_inc,
        sae_controls_65_incwork
      )
    )
  )

# If a specific county has been specified, subset data to it
if (exists("my_county_fip")) {
  my_pumas <- 
    geo_crosswalk %>% 
    filter(
      COUNTYFIP == my_county_fip
    ) %>% 
    pull(PUMA) %>% 
    unique()
  
  acs1_elig018_sae    <- filter(acs1_elig018_sae,    PUMA %in% my_pumas)
  acs1_elig1925_sae   <- filter(acs1_elig1925_sae,   PUMA %in% my_pumas)
  acs1_elig2644_sae   <- filter(acs1_elig2644_sae,   PUMA %in% my_pumas)
  acs1_elig4564_sae   <- filter(acs1_elig4564_sae,   PUMA %in% my_pumas)
  acs1_elig65plus_sae <- filter(acs1_elig65plus_sae, PUMA %in% my_pumas)
  
  acs5tract_sae <- filter(acs5tract_sae, COUNTYFIP == my_county_fip)
}

```

```{r bring in calibrated base year population estimates}
# Select specific age ranges of interest
pop_by_age_base <- 
  pop_age_t_calib_wide %>% 
  # filter(year == base_year) %>% 
  # Rename population values to avoid conflict with equivalent ACS5 counts, which
  # are for the prior 5 year period, not estimated for the base year as these are
  select(GEOID, 
         nAge0to18, nAge19to25, nAge26to44, nAge45to64, nAge65plus)
         #nAge0to19, nAge20to64, 

# Merge to the ACS5-year data
acs5tract_sae_counts <- 
  acs5tract_sae %>% 
  merge(
    pop_by_age_base,
    by = "GEOID",
    all.x = TRUE
  ) %>% 
  # /!\ These are placeholder values, which of course improperly assume that the
  # base-year estimates are perfectly precise. This must be replaced when possible.
  mutate(
    #  nAge0to19_se = 0,
    # nAge20to64_se = 0,
    nAge0to18_se  = 0,
    nAge19to25_se = 0,
    nAge26to44_se = 0,
    nAge45to64_se = 0,
    nAge65plus_se = 0)

stopifnot(nrow(acs5tract_sae_counts) == nrow(acs5tract))
```

```{r establish function to run SAE method}
run_saes_byCtrls <- function(vul_vars, sae_input_data, my_controls) {
  
  ### Determine which age count variables should used
  # Note: there are other ways to check against the second argument, such as
  # deparse(substitute(sae_input_data)) to get the character input from the
  # function call, but that approach wouldn't work from the parallelized 
  # function calls
  
  pop_n_var <- 
    case_when(
      # identical(sae_input_data, acs1_elig019_sae)    ~ "nAge0to19",
      # identical(sae_input_data, acs1_elig2064_sae)   ~ "nAge20to64",
      identical(sae_input_data, acs1_elig018_sae)    ~ "nAge0to18",
      identical(sae_input_data, acs1_elig1925_sae)   ~ "nAge19to25",
      identical(sae_input_data, acs1_elig2644_sae)   ~ "nAge26to44",
      identical(sae_input_data, acs1_elig4564_sae)   ~ "nAge45to64",
      identical(sae_input_data, acs1_elig65plus_sae) ~ "nAge65plus"
    )
  pop_n_se_var <- glue("{pop_n_var}_se")
   
  run_sae_combos(
    vul_vars       = vul_vars,
    sae_input_data = sae_input_data,
    sae_controls   = my_controls,
    aux_data       = acs5tract_sae_counts,
    aux_n_var      = pop_n_var,
    aux_n_se_var   = pop_n_se_var,
    verbose = TRUE
  )
}
```


```{r run SAE method}

parallelize_sae <- FALSE

inc_cat_field     <- "cFam_incpov_ratio_cat_with130"
incwork_cat_field <- "cWork_incpov_status130"
# Check that these workhorse fields have been described property within the ACS1
# data that each separate subset used in the SAE is drawn from
stopifnot(all(c(inc_cat_field, incwork_cat_field) %in% colnames(acs1_elig)))


if (parallelize_sae) {
  
  runlist <- 
    list(
      # sae_results_019_inc    = list(inc_cat_field, acs1_elig019_sae,    sae_controls_019_inc),
      # sae_results_2064_inc   = list(inc_cat_field, acs1_elig2064_sae,   sae_controls_2064_inc)
      # sae_results_65_incwork = list(inc_cat_field, acs1_elig65plus_sae, sae_controls_65plus_inc),
      sae_results_018_inc  = list(inc_cat_field, acs1_elig018_sae,    sae_controls_018_inc),
      sae_results_1925_inc = list(inc_cat_field, acs1_elig1925_sae,   sae_controls_1925_inc),
      sae_results_2644_inc = list(inc_cat_field, acs1_elig2644_sae,   sae_controls_2644_inc),
      sae_results_4564_inc = list(inc_cat_field, acs1_elig4564_sae,   sae_controls_4564_inc),
      sae_results_65_inc   = list(inc_cat_field, acs1_elig65plus_sae, sae_controls_65plus_inc)
      
      # sae_results_019_incwork    = list(incwork_cat_field, acs1_elig019_sae,    sae_controls_019_incwork),
      # sae_results_2064_incwork   = list(incwork_cat_field, acs1_elig2064_sae,   sae_controls_2064_incwork),
      # sae_results_65_incwork = list(incwork_cat_field, acs1_elig65plus_sae, sae_controls_65plus_incwork),
    )
  
  # Code to recruit (almost) as many core processors as are available (but not more than we need)
  cores <- detectCores() - 1 # not to overload your computer
  cores <- min(cores, length(runlist))
  cl <- makeCluster(cores) 
  registerDoParallel(cl)
  
  sae_results <- foreach (r = seq_along(runlist)) %dopar% {
    source("settings--main.R")
    
    run_saes_byCtrls(
      runlist[[r]][[1]], 
      runlist[[r]][[2]],
      runlist[[r]][[3]]
    )
  }
  stopCluster(cl)
  
  # Separate parallelized results to conform to downstream code
  for (r in seq_along(sae_results)) {
    assign(
      names(runlist)[r],
      sae_results[[r]]
    )
  }
  
} else {
  Sys.time()
  sae_results_018_inc  = run_saes_byCtrls(inc_cat_field, acs1_elig018_sae,    sae_controls_018_inc)
  sae_results_1925_inc = run_saes_byCtrls(inc_cat_field, acs1_elig1925_sae,   sae_controls_1925_inc)
  sae_results_2644_inc = run_saes_byCtrls(inc_cat_field, acs1_elig2644_sae,   sae_controls_2644_inc)
  sae_results_4564_inc = run_saes_byCtrls(inc_cat_field, acs1_elig4564_sae,   sae_controls_4564_inc)
  sae_results_65_inc   = run_saes_byCtrls(inc_cat_field, acs1_elig65plus_sae, sae_controls_65_inc)
  Sys.time()
  
  # sae_results_019_inc  = run_saes_byCtrls(inc_cat_field, acs1_elig019_sae,    sae_controls_019_inc)
  # sae_results_2064_inc = run_saes_byCtrls(inc_cat_field, acs1_elig2064_sae,   sae_controls_2064_inc)
  # sae_results_65_inc   = run_saes_byCtrls(inc_cat_field, acs1_elig65plus_sae, sae_controls_65plus_inc)
  
  # sae_results_019_incwork  = run_saes_byCtrls(incwork_cat_field, acs1_elig019_sae,    sae_controls_019_incwork)
  # sae_results_2064_incwork = run_saes_byCtrls(incwork_cat_field, acs1_elig2064_sae,   sae_controls_2064_incwork)
  # sae_results_65_incwork   = run_saes_byCtrls(incwork_cat_field, acs1_elig65plus_sae, sae_controls_65plus_incwork)
  
}

results <- str_subset(ls(), "^sae_results")

specs <- str_replace(results, "sae_results_", "")

```

```{r}
# Organize contents
sae_aux_data_acs5 <- acs5tract_sae
sae_controls_list <- 
  lapply(
    str_subset(
      ls(), "^sae_controls.+inc(work)?$"
    ), 
    \(x) get(x)
  )

# Save the bundle of objects
save(
  list = c(results, "specs", "sae_controls_list", "sae_aux_data_acs5"),
  file = glue("{output_path}sae_sensitivity_estimates_interim_{my_output_tag}.Rda")
)

if (FALSE) {
  load(
    file = glue("{output_path}sae_sensitivity_estimates_interim_{my_output_tag}.Rda"), 
    verbose = TRUE
  ) 
}
```


#### Examine the Estimated Composition of Tracts

```{r examine SAE share composition by tract -- FH estimates}
plot_sae_comp_by_tract <- function(sae_est) {
  
  tract_order <- 
    sae_est %>% 
    mutate(
      vc_value = sort_by_char_nums(vc_value)
    )
  base_cat <- levels(tract_order$vc_value)[1]
  
  tract_order <- 
    tract_order %>% 
    filter(vc_value == base_cat) %>% 
    arrange(-share_fh_trunc) %>%  
    mutate(
      rank := 1:n()
    )
  
  sae_est %>% 
    merge(
      select(tract_order, GEOID, rank), 
      by = "GEOID"
    ) %>% 
    ggplot() +
    aes(
      x = reorder(GEOID, rank),
      y = share_fh_trunc,
      color = vc_value) +
    geom_point(
      alpha = 0.3
    ) +
    geom_hline(
      yintercept = 0
    ) +
    scale_y_continuous(
      labels = percent
    ) +
    scale_color_discrete(
      name = "Vulnerability Category"
    ) +
    labs(
      title = glue("Distribution of SAE Faye-Herriot Estimates for `{deparse(substitute(sae_est))}`"),
      x = glue("Tracts, in order of pop'n share in {base_cat}"),
      y = "SAE estimated share (Faye-Herriot)"
    ) +
    theme(
      axis.text.x = element_blank()
    )
}
```


```{r plot the distribution of estimated SAE values}

for (r in results) {
  my_sae <- get(r)

  my_plot <- 
    my_sae$sae_out %>% 
    plot_sae_comp_by_tract()
  
  print(my_plot)
}

```

#### Examine Aggregate Comparison Plots

```{r compare sums of estimates to PUMA-level with observed PUMA values}

for (r in results) {
  my_sae <- get(r)
  
  fh_plot <- 
    my_sae[["agg_comp_fh"]]$agg_comp_plot +
    labs(
      title = "PUMA-level SAE Estimates vs ACS1 Counts",
      subtitle = glue("From specification `{r}`"),
      x = "Observed ACS 1-year Counts",
      y = "Fay Herriott Estimates"
    )
  
  model_plot <- 
    my_sae[["agg_comp_model"]]$agg_comp_plot +
    labs(
      title = "PUMA-level SAE Estimates vs ACS1 Counts",
      subtitle = glue("From specification `{r}`"),
      x = "Observed ACS 1-year Counts",
      y = "`Model-based` Estimates"
    )
  
  print(fh_plot)
  print(model_plot)
}

```


#### Redistribute SAE

Our non-canonical application of the SAE method requires several adjustments. First, the PUMA-level means are imprecise. In part, it is not guaranteed from the SAE method itself, although the diagnostics above suggest that the counts are closer. But also, our use of the ACS 1-year microdata is thin, and there are cases--notably for income bands--where ACS 1-year 5% data are available (i.e. the aggregate tables) and we have better anchors. 

Second, because our model makes use of left-hand side quantities that have reduced variance, as PUMA-level aggregates rather than truly tract-level estimates, our SAE estimates become compressed. See below. 

```{r compare SAE estimate to acs5}

# /*\ This is (currently) a highly bespoke comparison of SAE estimates to equivalent
# values in the ACS5. In contrast to the comparisons above--of the SAE estimates to 
# ACS1 values at the PUMA level, from which they are calibrated--this comparison
# is intended to motivate the need to "decompress" the SAE estimates. To this
# point, the ACS5 data have been used in an "auxiliary" role, i.e. of bringing
# correlations between ACS5 measures and the larger ACS1 categories down to the
# tract level. Now, we wish to build comparison to the values of the ACS5 fields
# (not just rely on their correlations). However, this may require some manual
# matching between the categories constructed in the ACS1 data and to those
# reported in the ACS5 tables, both to find equivalent income cut points as well
# as age ranges. 
# Note -- this comparison will only be possible for income-only comparisons, as the 
# ACS5 data does not have income-by-work status measures.

compare_sae_lt125fpl <- function(sae_spec, title, xlab, ylab) {
  
  # To handle the fact that different age runs of the SAE use different age-specific
  # income-to-poverty constructions, we remove the age-related part of the field name
  old_incpov_names <- str_subset(cn(sae_spec), "rIncPov.+")
  new_incpov_names <- str_replace(old_incpov_names, "(rIncPov\\d+to\\d+)_Age.+", "\\1")
  
  comp_data <-
    sae_spec[vc_value %in% c("0%-75%", "75%-130%")] %>% 
    setnames(
      old_incpov_names,
      new_incpov_names
    ) %>% 
    # Build up ACS5 measure for comparison
    mutate(
      rIncPov0to125 = rIncPov0to75 + rIncPov75to125
    ) %>% 
    select(GEOID, share_fh_trunc, rIncPov0to125) %>% 
    # Sum across SAE estimates, within tract
    summarize(
      .by = GEOID,
      share_fh_trunc = sum(share_fh_trunc),
      rIncPov0to125  = unique(rIncPov0to125)
    ) %>% 
    mutate(
      label = paste0("GEOID: ", GEOID)
    )
  
  rho <- with(comp_data, cor(share_fh_trunc, rIncPov0to125, use = "pairwise")) %>% round(2)
  
  # If tracts within a specific auxiliary geography are of interest, merge that
  # information in and style the plotted points
  if ("my_aux_geo_focal_val" %in% objects()) {
    comp_data <- 
      comp_data %>% 
      merge(
        select(geo_crosswalk, GEOID, aux_geo_label) %>% unique(),
        by = "GEOID",
        all.x = TRUE
      )
    
    plot_base <- 
      comp_data %>% 
      ggplot() +
      aes(
        x = rIncPov0to125,
        y = share_fh_trunc,
        #group = label,
        color = aux_geo_label == my_aux_geo_focal_val
      ) + 
      scale_color_manual(
        breaks = c(FALSE, TRUE),
        values = c("gray", "blue"),
        labels = c(paste0("Non-", my_aux_geo_focal_val), 
                   my_aux_geo_focal_val)
      )
  } else {
    plot_base <- 
      comp_data %>% 
      ggplot() +
      aes(
        x = rIncPov0to125,
        y = share_fh_trunc
      ) #,#group = label
  }
  
  # Generate the plot
  sae_lt125fpl_comp_plot <- 
    plot_base +
    geom_point(
      alpha = 0.1
    ) +
    geom_abline(
      color = "red"
    ) +
    geom_smooth(
      color = "blue"
    ) + 
    scale_x_continuous(
      labels = percent
    ) +
    scale_y_continuous(
      labels = percent
    ) +
    labs(
      title = title,
      x = xlab,
      y = ylab
    ) +
    annotate(
      "text", x = 0.1, 
      y = 0.6, 
      label = glue("rho = {rho}")
    ) +
    theme_minimal() +
    theme(
      legend.position = "none",
      title = element_text(size = 10)
    )
  
  sae_lt125fpl_comp_plot
  
  #ggplotly(sae_lt100fpl_comp_plot, tooltip = "group")
}
```

<!-- Next, we want to understand the source of these idiosyncracies. Direct inspection suggested that our first handful of outlier tracts had very low poverty but also very low rates of labor force participation and employment.  -->

```{r build plot of comparisons}

# /!\ Note -- by and large, the SAE estimates are notably compressed relative to
# the ACS5 measures. The reason for this is that the SAE estimates are anchored
# on PUMA-level values from the ACS1. Although the model component of the SAE
# estimates uses ACS5 measures for x_g, which capture the higher level of variation,
# the fact that the model is predicting s_G (i.e., large geographic measures that
# have some variation averaged away) mean that the estimated betas will put
# the SAE predictions into a narrower space. While using x_G for estimate would
# yield unbiased betas, the use of x_g to predict those betas would likely yield
# unstable predictions, e.g. ones that could range below 0% or above 100%. The
# current modeling choice substitutes a certain amount of compression (and thus 
# bias) for stability. The GMM method described in the "00" script would solve
# the need to make this tradeoff, giving a more natural structure to the relationship
# of PUMA-level measures, and tract-level predictors.

diagnostic_note <- 
  glue("NOTE: This comparison is not expected to show consistency, given\n",
       "our expectation of the SAE method showing compression")

acs5_compression_measure <- "Observed ACS 5-year Inc-to-Pov <130% FPL"
sae_measure_label <- "SAE Estimate of Inc-to-Pov < 130% FPL"

compare_sae_lt125fpl(
  sae_results_018_inc$sae_out,
  title = diagnostic_note,
  xlab = glue("{acs5_compression_measure}, Age 0-17"),
  ylab = glue("{sae_measure_label}, Age 0-18")
) +
  theme_minimal()

compare_sae_lt125fpl(
  sae_results_2644_inc$sae_out,
  title = diagnostic_note,
  xlab = glue("{acs5_compression_measure}, Age 18-64"),
  ylab = glue("{sae_measure_label}, Ages 25-44")
) +
  theme_minimal()

compare_sae_lt125fpl(
  sae_results_65_inc$sae_out,
  title = diagnostic_note,
  xlab = glue("{acs5_compression_measure}, Ages 65+"),
  ylab = glue("{sae_measure_label}, Ages 65+")
) +
  theme_minimal()

```


Thus, we undertake a further adjustment, by:

1. aligning our SAE estimates for each income-to-poverty category to the ACS 1-year 5% sample values for each PUMA, and
2. expanding the variance of the SAE estimates to equal the variance of ACS 5-year analogs.

In this way, we anchor the distribution of our new estimates in the most reliable and most recent values that are available.

```{r function to select relevant income-to-poverty measures}
incpovs <- 
  str_subset(
    acs5_incpov_byage_granular$inc_to_pov_ratio,
    "^IncPov") %>% 
  unique() %>% 
  sort_by_char_nums() %>% 
  sort()

incpov_bounds <- str_extract_all(incpovs, "\\d+") %>% unique()

dfIncPovCutoffs <- 
  data.frame(
    incpov = incpovs,
    left  = sapply(incpov_bounds, function(x) x[1]) %>% as.numeric(),
    right = sapply(incpov_bounds, function(x) x[2]) %>% as.numeric()
  )

get_closest <- function(val, ref) {
  ref <- setdiff(ref, NA) # This addresses NAs in second value from e.g. "400plus"
  absdev <- abs(val - ref)
  ref[which(absdev == min(absdev))]
}

return_incpov_fields_bounds <- function(low, high) {
  # browser()
  closest_low  <- get_closest(low,  dfIncPovCutoffs$left)
  closest_high <- get_closest(high, dfIncPovCutoffs$right)
  
  out <- filter(dfIncPovCutoffs, left >= closest_low)
  if (!is.na(high) & !is.infinite(high)) {
    out <- filter(out, right <= closest_high)
  }
  return(out$incpov %>% as.character())
}

if (FALSE) {
  return_incpov_fields_bounds(0, 100)
  return_incpov_fields_bounds(1, 99)
  return_incpov_fields_bounds(0, 101)
  return_incpov_fields_bounds(400, NA)
  return_incpov_fields_bounds(500, NA)
  return_incpov_fields_bounds(600, NA)
}
```

```{r notes for calculating program eligibility below}
# Because we do not know the joint distribution of income- and work-eligibility
# rates at the tract level from the ACS5 itself, we use microdata for calibration.
# We use the phi calculation of correlation for bernoulli random variables, which 
# is just the pearson correlation. We first confirm that.

if (FALSE) {
  if (!"psych" %in% installed.packages()[, "Package"]) install.packages("psych")
  
  library(psych)
  df <- data.frame(
    x = c(1, 1, 0, 1),
    y = c(1, 0, 0, 1)
  )
  
  spearman_cor <- with(df, cor(x, y))
  
  mat <- matrix(c(2, 1, 0, 1), ncol = 2, byrow = TRUE)
  phi_stat <- phi(mat, digits = 7)
  
  stopifnot(abs(spearman_cor - phi_stat) < 0.0001) 
}

```

```{r results = 'asis'}
# This functions takes sae estimates and information about the context, including 
# the ages and presence of kids
# It returns a set of ACS5 values for each vc value, representing corresponding
# income thresholds for each vc categories and, if relevant, the related 
# work status
# In In cases of VCs involving work eligibility, it also gets these work measures 
# from the ACS5 as well as a "phi" measure for each PUMA and thus the tracts 
# inside of it which is used to capture the correlation between income and work status

make_acs5_equiv <- function(sae_ests, sae_age, only_hh_with_kids, verbose = FALSE) {
  
  ### Read SAE elements
  # vc values to match
  vc_vals <- unique(sae_ests$vc_value)
  
  # Set ages for pulls and subsetting
  # /*\ This mapping involves some discretion for how age groups estimated in
  # the SAE are connected to ACS5 values. Even though the ACS5 may have 
  # more granular measures, we 
  acs5_ages <- 
    case_when(
      # sae_age == "019"    ~ "Age0to17",
      # sae_age == "2064"   ~ "Age18to64",
      sae_age == "018"    ~ "Age0to17",
      sae_age == "1925"   ~ "Age18to64",
      sae_age == "2644"   ~ "Age18to64",
      sae_age == "4564"   ~ "Age18to64",
      sae_age == "65plus" ~ "Age65plus"
    )
  acs1_ages <- 
    case_when(
      # sae_age == "019"  ~ c( 0, 19),
      # sae_age == "2064" ~ c(20, 64),
      sae_age == "018"  ~ c( 0, 18),
      sae_age == "1925" ~ c(19, 25),
      sae_age == "2644" ~ c(26, 44),
      sae_age == "4564" ~ c(45, 64),
      sae_age == "65"   ~ c(65, NA)
    )
  
  acs5_ests <- NULL
  for (vc in vc_vals) {
    
    if (verbose) print(glue("\n\nvc -- {vc}\n"))
    # Parse income values
    # <move left/right function to the ACS5 function methods>
    incpov_bounds <- str_extract_all(vc, "\\d+") %>% unlist() %>% as.numeric()
    incpov_left  <- incpov_bounds[1]
    incpov_right <- incpov_bounds[2] %>% replace_na(Inf)
    
    # Aggregate incpov values in the acs5 data as relevant to the vc bounds
    incpov_cat_keep <- return_incpov_fields_bounds(incpov_left, incpov_right)
    acs5_incpov_vc <- 
      acs5_incpov_byage_granular %>% 
      filter(
        inc_to_pov_ratio %in% incpov_cat_keep,
        age_agg == acs5_ages
      ) 
    
    if (verbose) {
      print(
        glue("  ACS5 income cats are: {paste(levels(sort_by_char_nums(acs5_incpov_vc$inc_to_pov_ratio)), collapse = ', ')}, and ages are {paste(unique(acs5_incpov_vc$age_agg), collapse = ',')}.\n")
        )
    }
    acs5_incpov_vc <- 
      acs5_incpov_vc %>% 
      summarize(
        .by = GEOID,
        # Sum rates across incpov categories relevant to the vc income bounds
        rInc = sum(r),
        # Sum population weights used for those same measures
        wAcs5 = sum(w),
      )
    
    ### Calculate joint income-and-work status work eligibility is relevant ###
    # The measures that we have calculated from pulls of the ACS 5-year data are
    # only marginal distributional values. However, we want estimates of the joint
    # value, i.e. individuals in families based on both income and work eligibility status.
    # We can use calculations from the phi coefficient (https://en.wikipedia.org/wiki/Phi_coefficient)
    # in the microdata above with these marginal values to estimate the likelihood of 
    # the joint work eligible x income eligible condition.
    
    # Using notation from that wikipedia article, note that the n11, n01, n10, n00
    # values could be considered rates instead of counts, where n11 is the value
    # of interest, and n1., n0., n.1, and n.0 are the marginal values that we
    # obtain from the ACS 5-year data. Call these n1. = p, n0. = (1-p), n.1 = q,
    # n.0 = (1-q), and note that n = 1, as the sum of marginal probabilities
    # must equal 100% probability. Then, the second equation for phi under the 
    # "Definition" section which reads as follow, can be reduced:
    #   phi = (n11 - n1.*n.1) / sqrt( n1.*n.1*(n - n1.)*(n - n.1) )
    #       = (1*n11 - p*q) / sqrt(p*q*(1-p)*(1-q))
    # And thus:
    #   n11 = phi * sqrt(p*q*(1-p)*(1-q)) + pq
    # Here, n11 is the quantity of interest--the joint probability of income and
    # work eligibility status--and where we have phi calculated. Note that phi=0 
    # corresponds to the case of zero correlation, and would result in n11 = pq
    # which--as the joint probability case where both random variables are 
    # independent--confirms common expectations.
    
    if (str_detect(vc, "Elig")) {
      # Map SAE vulnerability category to values of ACS5 work status field
      vc_elig <- 
        case_when(
          str_detect(vc, "NotWorkElig")     ~ "AllAdultsEmpl",
          str_detect(vc, "(^|\\W)WorkElig") ~ "NotAllAdultsEmpl"
        )
      
      # Use argument to subset to only households with kids. 
      # We want to do this when, e.g., the age focus is on school-aged individuals
      # (i.e. the kids whose program eligibility we are evaluating via parent work
      # and income)
      kids_suffix <- if_else(only_hh_with_kids == TRUE, "withKids", "allHhs")
      
      # Filter to relevant ACS5 data
      acs5_workelig <- 
        acs5_workelig_long %>% 
        filter(
          status == glue("{vc_elig}_{kids_suffix}")
        )
      
      if (verbose) cat(glue("  ACS5 work elig status is: {paste(unique(acs5_workelig$status), collapse = ', ')}.\n"))
      
      acs5_workelig <- 
        acs5_workelig %>%
        select(GEOID, rWork = r)
      
      # Calculate phi by PUMA for relevant incpov and work elig
      prog_elig_field <- glue("prog_elig_incratio_{local_prog_incratio_base}")
      acs1_forPhi <-
        copy(acs1_elig) %>% 
        # Subset to relevant ages
        .[acs1_ages[1] <= AGEP & AGEP < acs1_ages[2],
          # calculate flags for income and work matching the `vc` value
          j = .(AGEP, PUMA, fam_incpov_ratio, bAdults_all_workThresh_sch,
                inc_measure  = 1*(between(fam_incpov_ratio*100, incpov_left, incpov_right)),
                work_measure = 
                  case_match(
                    rep(vc_elig, .N),
                    "NotAllAdultsEmpl" ~ 1 - bAdults_all_workThresh_sch,
                    "AllAdultsEmpl"    ~     bAdults_all_workThresh_sch))]
      
      if (verbose) {
        print("Stats for the acs1 data for calculating phi--\n")
        range_paste <- function(x) paste0(range(x, na.rm = T), collapse = "-")
        ranges_forPhi <- 
          acs1_forPhi %>% 
          .[j = .(vc = vc,
                  incpov_range = range_paste(fam_incpov_ratio),
                  is_work_elig = range_paste(bAdults_all_workThresh_sch),
                  age_range    = range_paste(AGEP)),
            by = .(inc_measure, work_measure)] %>% 
          arrange(-inc_measure, -work_measure)
        print(ranges_forPhi)
      }
      
      # Calculate `phi` by PUMA (and replace missings with mean Phi values)
      phi_p <- 
        acs1_forPhi %>% 
        .[j = .(phi_p = cor(inc_measure, work_measure)),
          by = PUMA] %>% 
        .[j = phi_p := replace_na(phi_p, meanNA(phi_p))]
      
      # For comparison, calculate `phi` across all PUMAs
      phi <- 
        acs1_forPhi %>% 
        .[j = .(phi = cor(inc_measure, work_measure))] %>% 
        .[j = phi := replace_na(phi, meanNA(phi))] %>% 
        pull(phi)
      
      # Estimate combo
      acs5_est_vc <- 
        acs5_incpov_vc %>% 
        merge(acs5_workelig, by = "GEOID") %>% 
        merge(geo_crosswalk %>% select(GEOID, PUMA) %>% unique(), by = "GEOID") %>% 
        merge(phi_p, by = "PUMA") %>% 
        as.data.table() %>% 
        .[j = .(GEOID,
                vc_value = vc,
                wAcs5,
                # Create calculation using puma-specific Phi
                share_acs5 = 
                  phi_p * sqrt(rInc*rWork*(1-rInc)*(1-rWork)) +
                  rInc*rWork,
                # As a sensitivity, same calculation using a pooled phi
                share_acs5_phi = 
                  phi   * sqrt(rInc*rWork*(1-rInc)*(1-rWork)) +
                  rInc*rWork,
                # As another sensitivity, a calculation assuming independence of income and work measures
                share_acs5_indep = rInc*rWork)]
    } else {
      acs5_est_vc <- 
        acs5_incpov_vc %>% 
        as.data.table() %>% 
        .[j = .(GEOID,
                vc_value = vc,
                share_acs5 = rInc)]
    }
    acs5_ests <- bind_rows(acs5_ests, acs5_est_vc)
  }
  sae_ests_aug <- 
    sae_ests %>% 
    merge(
      acs5_ests,
      by = c("GEOID", "vc_value"),
      all.x = TRUE
    )
  
  return(sae_ests_aug)
}
```

```{r run test of calculation of decompression statistics}
if (FALSE) {
  # Some suppressed code to make interactive troubleshooting easier
  if (FALSE) {
      debug(make_acs5_equiv)
    undebug(make_acs5_equiv)
  }
  sae_results_test_inc <- make_acs5_equiv(sae_results_2644_inc$sae_out, "2644", only_hh_with_kids = FALSE, verbose = TRUE)
  # sae_results_test_incwork <- make_acs5_equiv(sae_results_2064_incwork$sae_out, "2064", only_hh_with_kids = FALSE, verbose = TRUE)
} 
```

```{r how much difference does use of phi vs phi_p make}
if (FALSE) {
  
  # Compare the results from using phi_p and phi
  # Hypothesis is that for smaller cells, the phi-derived estimates will be more stable
  # /!\ This `sae_result` object needs to be set when income-by-work categories
  # are estimated
  sae_results_test_incwork %>% 
    ggplot() +
    aes(
      x = share_acs5, 
      y = share_acs5_phi
    ) +
    geom_abline() + 
    geom_point(
      alpha = 0.1
    ) + 
    geom_smooth() +
    facet_wrap(
      ~vc_value
    ) +
    labs(
      title    = "Comparison of ACS5 Estimates Derivations",
      subtitle = "Use of PUMA-specific calcs of Phi vs Full-state"
    )
    # Result: seems that the results are fairly stable
  
}
```


```{r compare acs5 estimates with sae estimates}
if (FALSE) {
  
  # Point is: the values should hopefully be basically consistent, but the 
  # variance of the acs5 should be substantially higher, which is what we rely
  # on for decompressing the sae estimates
  # /!\ This `sae_result` object needs to be set when income-by-work categories
  # are estimated
  sae_results_test_incwork %>% 
    mutate(
      .by = vc_value,
      label = glue("{vc_value}\nrho = {round(cor(share_model_trunc, share_acs5, use = 'pairwise'), 2)}\nratio of ",
                   "var = {round(varNA(share_acs5)/varNA(share_model_trunc), 2)}")) %>% 
    ggplot() +
    aes(
      x = share_model_trunc,
      y = share_acs5
    ) +
    geom_abline() + 
    geom_point(
      alpha = 0.1
    ) +
    geom_smooth() + 
    facet_wrap(
      ~ label
    ) +
    labs(
      title    = "Comparison of Tract-Level ACS5 Estimates vs SAE",
      subtitle = glue("Expectations: disagreements due to lag of ACS5 and other assumptions\n",
                      "but higher variance of ACS5, which is the key to decompression")
    )
}
```


```{r prepare population data for merging to estimates}
pop_long <- 
  pop_age_t_calib %>% 
  pivot_longer(
    cols = -c(GEOID, year, age_var)
  ) %>% 
  mutate(
    age = str_replace(age_var, "nAge", "")
  ) %>% 
  select(
    GEOID, 
    year, 
    age, 
    pop = value
  )

```

```{r misc functions for use in redistribution}
bound <- function(x, lower = 0, upper = 1) {
  x[x < lower] <- lower
  x[x > upper] <- upper
  return(x)
}

if (FALSE) {
  bound(c(-1, 0.2, 0.8, 5))
}
```

```{r function for performing redistribution}
# This function performs the redistribution of values based on the ACS5 values
# above that provide the variance for equivalent "vc" values

# Values for easy interactive debugging
if (FALSE) {
  debug(redis_sae)
  undebug(redis_sae)
 
  sae_redis_incpov <- redis_sae(sae_results_2644_inc, "2644", only_hh_with_kids = FALSE)
  
  View(sae_redis_incpov$sae_out_decompress, "redis_inc")
  sae_redis_incpov$sae_out_decompress %>% 
    select(GEOID, vc_value, matches("^share|^infl")) %>% 
    View("check_sae_redis")
  # sae_redis_incwork <- redis_sae(sae_results_2644_incwork, "2644");
  #   View(sae_redis_incwork$sae_out_decompress, "redis_incwork")
}

redis_sae <- function(sae_to_redis, sae_age, only_hh_with_kids) {
  
  sae_to_redis_aug <- make_acs5_equiv(sae_to_redis$sae_out, sae_age, only_hh_with_kids)
  
  pop_age <- 
    case_match(
      sae_age,
      # Prior age distinctions
      "019"  ~ "0to19", 
      "2064" ~ "20to64",
      
      # More recent specifications
      "018"  ~ "0to18",
      "1925" ~ "19to25",
      "2644" ~ "26to44",
      "4564" ~ "45to64",
      "65"   ~ "65plus"
    )
  
  redis_out <- 
    sae_to_redis_aug %>% 
    merge(
      pop_long %>% filter(age == pop_age, year == base_year),
      by = "GEOID",
      all.x = TRUE) %>% 
    mutate(
      .by = c(PUMA, vc_value),
      # This mutate() step performs redistribution of the SAE estimates via an
      # "affine" transformation (i.e. adding/subtract/multiplication), as:
      #   new = (sae - mean(sae))*(acs5_sd/sae_sd) + mean(old)

      # We attempt this both in "levels", i.e. the existing percentage-based units
      # and with values transformed to the logistic scale. The theory for using the
      # logistic-transformed values is that they exist on the full real number
      # line, and thus would avoid issues of values being redistributed below 0%
      # and above 100%.
      
      ### Set up affine transformation
      # Center values to have mean 0
      share_model_trunc_m0 = share_model_trunc - mean(share_model_trunc),
      share_fh_trunc_m0    = share_fh_trunc    - mean(share_fh_trunc),
      share_acs5_m0        = share_acs5        - mean(share_acs5),
      
      # Calculate std-deviations of shares
      share_model_trunc_sd = sdNA(share_model_trunc),
      share_fh_trunc_sd    = sdNA(share_fh_trunc),
      share_acs5_sd        = sdNA(share_acs5),
      
      ## Perform logistic transformation, and get sd's
      # For some reason, it's producing NAs to combine the separate calculations
      # below. Separating them, as we have, avoids this.
      share_model_trunc_log      = qlogis(share_model_trunc),
      share_model_trunc_log_mean = meanNA(share_model_trunc_log),
      share_model_trunc_log_m0   = share_model_trunc_log - share_model_trunc_log_mean,
      share_model_trunc_log_sd   = sdNA(share_model_trunc_log_m0),
      
      share_fh_trunc_log      = qlogis(share_fh_trunc),
      share_fh_trunc_log_mean = meanNA(share_fh_trunc_log),
      share_fh_trunc_log_m0   = share_fh_trunc_log - share_fh_trunc_log_mean,
      share_fh_trunc_log_sd   = sdNA(share_fh_trunc_log_m0),
      
      share_acs5_log      = qlogis(share_acs5),
      share_acs5_log_mean = meanNA(share_acs5_log),
      share_acs5_log_m0   = share_acs5_log - share_acs5_log_mean,
      share_acs5_log_sd   = sdNA(share_acs5_log_m0),
      
      # Build variance inflation factors for decompressing the estimates
      infl_model_pct = share_acs5_sd     / share_model_trunc_sd,
      infl_model_log = share_acs5_log_sd / share_model_trunc_log_sd,
      infl_fh_pct    = share_acs5_sd     / share_fh_trunc_sd,
      infl_fh_log    = share_acs5_log_sd / share_fh_trunc_log_sd,
      
      # Redistribute using variance and mean adjustment
      share_model_redis_pct = 
        (infl_model_pct * share_model_trunc_m0) + mean(share_model_trunc),
      
      share_fh_redis_pct    =
        (infl_fh_pct    * share_fh_trunc_m0)    + mean(share_fh_trunc),
      
      share_model_redis_log = 
        
        plogis(infl_model_log * share_model_trunc_m0  + share_model_trunc_log_mean),
      
      share_fh_redis_log    = 
        plogis(infl_fh_log    * share_fh_trunc_m0     + share_fh_trunc_log_mean),
      
      # Bound results within the interval [0,1]
      share_model_redis_pct01 = bound(share_model_redis_pct),
      share_fh_redis_pct01    = bound(share_fh_redis_pct),
      share_model_redis_log01 = bound(share_model_redis_log),
      share_fh_redis_log01    = bound(share_fh_redis_log)
    ) %>% 
    # Within tract, inflate each type of estimate so that they all add up to 100
    # by dividing by the in-tract sum
    mutate(
      .by = GEOID,
      share_model_redis_pct01_infl = share_model_redis_pct01 / sum(share_model_redis_pct01),
      share_fh_redis_pct01_infl    = share_fh_redis_pct01    / sum(share_fh_redis_pct01),
      share_model_redis_log01_infl = share_model_redis_log01 / sum(share_model_redis_log01),
      share_fh_redis_log01_infl    = share_fh_redis_log01    / sum(share_fh_redis_log01),
    ) %>% 
    as.data.table()
  
  # Output the results to the `sae_out` slot of the input SAE
  sae_to_redis[["sae_out_decompress"]] <- redis_out
  
  return(sae_to_redis)
}
```


```{r implement redistributions}
for (spec in specs) {
  #print(spec)
  sae_name <- glue("sae_results_{spec}")
  # The age is given by the final numbers in the name of the spec
  sae_age <- str_extract(spec, "\\d+")
  
  assign(glue("sae_results_{spec}"),
         redis_sae(get(sae_name), sae_age))
}

# Check on success
if (FALSE) {
  sub_cn(sae_results_2644_inc$sae_out_decompress, "_infl$")
  sae_results_2644_inc$sae_out_decompress %>% 
    select(
      GEOID, vc_value, 
      share_model_trunc, share_model_redis_pct, share_model_redis_pct01_infl
    )
  
  # sub_cn(sae_results_2064_incwork$sae_out_decompress, "_infl$")
  # sae_results_2064_incwork$sae_out_decompress %>% 
  #   select(GEOID, vc_value, 
  #          share_model_trunc, share_model_redis_pct, share_model_redis_pct01_infl)
}

```

```{r save SAE ingredients}
sae_out_file <- glue("{output_path}sae_sensitivity_estimates_{my_output_tag}.Rda")

if (rerun_sae | !file.exists(sae_out_file)) {
  # Organize contents
  sae_aux_data_acs5 <- acs5tract_sae
  sae_controls_list <- 
    lapply(
      glue("sae_controls_{specs}"),
        \(x) get(x))
  names(sae_controls_list) <- glue("sae_controls_{specs}")
  results <- paste0("sae_results_", specs)
  
  # Save the bundle of objects
  save(
    list = c(results, "specs", "sae_controls_list", "sae_aux_data_acs5"),
    file = sae_out_file
  )
  
} else {
  load(
    file = sae_out_file,
    verbose = TRUE
  ) 
}
```

```{r extract estimate tables from sae output}
for (spec in specs) {
  stem <- glue("sae_results_{spec}")
  assign(glue("{stem}_out"),
         get(stem)[["sae_out_decompress"]])
}
```

```{r pick a single SAE sensitivity to investigate}
check_redis_sae <- sae_results_incpov_ctrls_100_05$sae_out_decompress
check_stats_puma <- 
  acs1_elig %>% 
  .[between(AGEP, 0, 5),
    j = .(wgt = sum(PWGTP)),
    by = .(PUMA, vc_value = fam_incpov_ratio_cat_by100)] %>% 
  .[j = share_acs1 := wgt / sum(wgt),
          by = PUMA] %>% 
  select(-wgt)
```

```{r examine overages}
# Examine how the sums look
overs <- 
  check_redis_sae %>% 
  group_by(GEOID, PUMA) %>% 
  summarize(sums = sum(share_model_redis_pct01),
            check = sum(share_model_redis_pct01_infl))

ggplot(overs,
       aes(x = sums)) +
  geom_density()

# Concentrated in smaller sets of PUMAs?
overs %>% 
  group_by(PUMA) %>% 
  summarize(pct_over = mean(sums>1.5))

```

```{r calculate percentages of estimates falling outside of [0,1], eval = developer_mode}
check_redis_sae %>% 
  group_by(vc_value) %>% 
  summarize(
    share_model_redis_pct_lt0 = meanNA(share_model_redis_pct < 0) %>% percent(1),
    share_model_redis_pct_gt1 = meanNA(share_model_redis_pct > 1) %>% percent(1),
    
    share_model_redis_log_lt0 = meanNA(share_model_redis_log < 0) %>% percent(1),
    share_model_redis_log_gt1 = meanNA(share_model_redis_log > 1) %>% percent(1),
    
    share_fh_redis_pct_lt0    = meanNA(share_fh_redis_pct    < 0) %>% percent(1),
    share_fh_redis_pct_gt1    = meanNA(share_fh_redis_pct    > 1) %>% percent(1),
    
    share_fh_redis_log_lt0    = meanNA(share_fh_redis_log    < 0) %>% percent(1),
    share_fh_redis_log_gt1    = meanNA(share_fh_redis_log    > 1) %>% percent(1)
  ) %>% 
  pivot_longer(
    cols = -vc_value
  ) %>% 
  pivot_wider(
    names_from = vc_value,
    values_from = value
  )
```



```{r check the results -- final versus acs5, eval = developer_mode}
# This is done to see if we obtain something relatively close to the 45
check_redis_sae %>% 
  ggplot(aes(x = share_acs5,
             y = share_model_redis_pct)) +
  geom_abline() + 
  geom_point(alpha = 0.1) + 
  geom_smooth() +
  geom_hline(yintercept = 0, color = "red") +
  geom_hline(yintercept = 1, color = "red") +
  facet_wrap(~vc_value)

check_redis_sae %>% 
  ggplot(aes(x = share_acs5,
             y = share_model_redis_log)) +
  geom_abline() + 
  geom_point(alpha = 0.1) +
  geom_smooth() +
  geom_hline(yintercept = 0, color = "red") +
  geom_hline(yintercept = 1, color = "red") +
  facet_wrap(~vc_value)

# Check the correlations between each adjustment type and the acs5 -- seems that
# the pct adjustment -- despite violating [0,1] bounds -- respects

check_redis_sae %>% 
  group_by(vc_value) %>% 
  summarize(cor_acs5_pct = cor(share_acs5, share_model_redis_pct, use = "pairwise"),
            cor_acs5_log = cor(share_acs5, share_model_redis_log, use = "pairwise"))
  # True -- they are often clearly better. This is never mind the fact that the 
  # slopes of the former are also closer to 1.
```

```{r check the results -- final_bounded versus acs5, eval = developer_mode}
# This is done to see if we obtain something relatively close to the 45
check_redis_sae %>% 
  ggplot(aes(x = share_acs5,
             y = share_model_redis_pct01_infl)) +
  geom_abline() + 
  geom_point(alpha = 0.1) + 
  geom_smooth() +
  geom_hline(yintercept = 0, color = "red") +
  geom_hline(yintercept = 1, color = "red") +
  facet_wrap(~vc_value)

check_redis_sae %>% 
  ggplot(aes(x = share_model_redis_pct,
             y = share_model_redis_pct01_infl)) +
  geom_abline() + 
  geom_point(alpha = 0.1) +
  geom_smooth() +
  geom_hline(yintercept = 0, color = "red") +
  geom_hline(yintercept = 1, color = "red") +
  facet_wrap(~vc_value)

# Check the correlations between each adjustment type and the acs5 -- seems that
# the pct adjustment -- despite violating [0,1] bounds -- respects

check_redis_sae %>% 
  group_by(vc_value) %>% 
  summarize(cor_acs5_pct = cor(share_acs5,            share_model_redis_pct01_infl, use = "pairwise"),
            cor_acs5_log = cor(share_model_redis_pct, share_model_redis_pct01_infl, use = "pairwise"))
  # True -- they are often clearly better. This is never mind the fact that the 
  # slopes of the former are also closer to 1.
```

```{r how does the adjusted values compare with the original, eval = developer_mode}
check_redis_sae %>% 
  ggplot(aes(x = share_model_trunc,
             y = share_model_redis_pct01_infl)) +
  geom_abline() + 
  geom_point(alpha = 0.1) +
  geom_smooth() +
  facet_wrap(~vc_value)
  # In short -- on average, they're close to the 45

```

```{r examine distributions and correlations of original and final SAE vs acs5}
comp_plot <- function(field1, field2) {
  check_redis_sae %>% 
  filter(!is.na(get(field1)),
         !is.na(get(field2))) %>% 
  ggplot(aes(x = get(field1),
             y = get(field2))) +
  geom_abline() + 
  geom_point(alpha = 0.1) +
  geom_smooth() + 
  scale_y_continuous(limits = c(0, 1)) +
  labs(x = field1, y = field2) +
  facet_wrap(~vc_value)
}

comp_plot("share_acs5", "share_model_trunc")
comp_plot("share_acs5", "share_model_redis_pct")
comp_plot("share_acs5", "share_model_redis_pct01_infl")

check_redis_sae %>% 
  group_by(vc_value) %>% 
  summarize(cor_acs5_sae  = cor(share_acs5, share_model_trunc,            use = "pairwise") %>% round(3),
            cor_acs5_pct = cor(share_acs5, share_model_redis_pct, use = "pairwise") %>% round(3),
            cor_acs5_infl = cor(share_acs5, share_model_redis_pct01_infl, use = "pairwise") %>% round(3),
            
            var_acs5 = varNA(share_acs5) %>% round(3),
            var_sae  = varNA(share_model_trunc) %>% round(3),
            var_pct = varNA(share_model_redis_pct) %>% round(3),
            var_infl = varNA(share_model_redis_pct01_infl) %>% round(3)) %>% 
  ungroup()
  # Shows that correlations have dropped somewhat with each manipulation, but 
  # the variances are substantially more realistic, which is critical
  # Note -- these comparisons don't capture the greater alignment with ACS 1
```

```{r check final accordance with PUMA-level statistics, eval = developer_mode}
# Here, we calculate population-weighted averages, for comparison with PUMA-level
# averages directly from the ACS 1
est_vs_acs1 <- 
  check_redis_sae %>% 
  ungroup() %>%
  select(GEOID, PUMA, vc_value, pop, 
         share_acs5, share_model_trunc, share_model_redis_pct,
         share_model_redis_pct01_infl) %>% 
  pivot_longer(cols = -c(GEOID, PUMA, vc_value, pop),
               names_to = "method",
               values_to = "estimate") %>% 
  group_by(PUMA, vc_value, method) %>% 
  summarize(
    # Checking: this should be unique
    estimate_puma = weighted.mean(x = estimate, w = pop)
    ) %>% 
  mutate(
    method = factor(method,
                    levels = c("share_acs5", 
                               "share_model_trunc", 
                               "share_model_redis_pct",
                               "share_model_redis_pct01_infl"))
  ) %>% 
  merge(check_stats_puma,
        by = c("PUMA", "vc_value"))

ggplot(est_vs_acs1,
       aes(x = share_acs1,
           y = estimate_puma,
           color = method)) +
  geom_abline() + 
  geom_point() + 
  geom_smooth() +
  facet_grid(vc_value ~ method) +
  theme(legend.position = "bottom")

  # ACS5 (red) is inconsistent -- which makes sense because they are lagged!
  # The original SAE estimates (yellow) show clear compression
  # The raw redistributed estimates (green) are highly consistent for each band
  # The truncated/reinflated estimates (blue) are also highly consistent for
  #   each band, but of course also respect 0% floor and 100% ceiling for each 
  #   tract. Seem that this advantage did not create problems for PUMA-level 
  #   aggregates.
  # The estimates taken directly from the ACS5 (purple) are also impressively 
  #   consistent with the ACS1

```


#### Compare Tract-Level SAE Estimates to the ACS 5-year


```{r compare measure variance in acs5 vs sae by PUMA, eval = developer_mode}
var_prop_acs5_sae <- 
  sae_results_incpov_ctrls_100_05$sae_out %>% 
  filter(vc_value == "0%-100%") %>% 
  mutate(acs5_pov = incpov_lt6_r0to50_est + incpov_lt6_r50to100_est) %>% 
  group_by(PUMA) %>% 
  summarize(var_acs5_pov = varNA(acs5_pov),
            var_sae_pov  = varNA(share_model_trunc),
            avg_acs5_pov = meanNA(acs5_pov),
            avg_sae_pov  = meanNA(share_model_trunc)) %>% 
  mutate(ratio_var_acs5_sae = var_acs5_pov / var_sae_pov)

ggplot(var_prop_acs5_sae,
       aes(x = reorder(PUMA, ratio_var_acs5_sae),
           y = ratio_var_acs5_sae)) + 
  geom_bar(stat = "identity") +
  geom_hline(yintercept = 1, 
             color = "red") +
  labs(x = "PUMA",
       y = "Ratio of ACS5 Variance to SAE") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

ggplot(var_prop_acs5_sae,
       aes(x = avg_acs5_pov,
           y = ratio_var_acs5_sae,
           label = PUMA)) + 
  geom_point() + 
  geom_text(vjust = 1) +
  labs(x = "ACS5 Poverty Rate",
       y = "Ratio of ACS5 Variance to SAE") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
  
ggplot(var_prop_acs5_sae,
       aes(x = avg_acs5_pov,
           y = avg_sae_pov,
           label = PUMA)) + 
  geom_point() + 
  geom_abline() +
  geom_text(vjust = 1) +
  labs(title = "Comparison of PUMA-Level ACS5 and SAE Estimates (Simple averages)",
         x = "ACS5 Poverty Rate",
       y = "SAE Poverty Rate") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
  # NOTE -- this isn't what we're worried about. We're worried about the ACS1 comparison.
  # See e.g. acs1_elig[between(AGEP, 0, 5), j = sum(PWGTP[fam_incpov_ratio_cat_by100 == "0%-100%"])/sum(PWGTP), by = PUMA]
```



#### Map Components of the SAE Estimates

```{r set up comparisons of data}
pov_p <- 
  lapply(c("05", "612"),
         function(a) {
           get(glue("sae_results_incpov_ctrls_mix_{a}"))$sae_out %>% 
             filter(vc_value %in% c("0%-50%", "50%-100%")) %>% 
             group_by(GEOID) %>% 
             summarize(acs1_pov       = sum(share_direct),
                       sae_pov_fh     = sum(share_fh_trunc),
                       sae_pov_model  = sum(share_model_trunc))
         }
  )

tractShp_pov <- 
  tractShp %>% 
  left_join(pov_p[[1]] %>% rename(acs1_pov_05      = acs1_pov,
                                  sae_pov_fh_05    = sae_pov_fh,
                                  sae_pov_model_05 = sae_pov_model),
            by = "GEOID") %>% 
  left_join(pov_p[[2]] %>% rename(acs1_pov_612      = acs1_pov,
                                  sae_pov_fh_612    = sae_pov_fh,
                                  sae_pov_model_612 = sae_pov_model),
            by = "GEOID") %>% 
  left_join(acs5tract %>% select(GEOID, acs5_pov = incpov_r0to100_est),
            by = "GEOID")

```

```{r set color scale}
map_sae_components <- function(dt, fill_field, field_label, val_limits, save_label) {
  
  pumas_to_keep <-
    geo_crosswalk[GEOID %in% dt$GEOID] %>% 
    .[["PUMA"]] %>% 
    unique()
  
  pumaShp_sub <-
    pumaShp %>% 
    filter(PUMA %in% pumas_to_keep)
  
  my_plot <- 
    ggplot() +
    geom_sf(data = dt,
            aes_string(fill = fill_field),
            linewidth = 0.025,
            color = "black") +
    geom_sf(data = pumaShp_sub,
            color = "red",
            linewidth = 0.75,
            fill = NA) +
    scale_fill_viridis_c(name   = field_label,
                         limits = val_limits,
                         option = "viridis", #"plasma", # 
                         trans  = "identity",
                         labels = percent,
                         alpha  = .4) +
    theme_void() +
    theme(legend.position = "none")
  
  ggsave(plot = my_plot,
         filename = glue("{output_path}Map of Base Year {save_label}_{my_output_tag}.png"),
         #width = 7,
         height = 7,
         units = "in")
  
  print(my_plot)
}
```


```{r set value scales}
limits_05  <- range(with(tractShp_pov, c(acs1_pov_05)),  # sae_pov_fh_05, sae_pov_model_05
                    na.rm = TRUE)
limits_612 <- range(with(tractShp_pov, c(acs1_pov_612)), # sae_pov_fh_612, sae_pov_model_612
                    na.rm = TRUE)
```

```{r generate maps}
# /!\ Look into why some geographies are displaying as "NA". Must of course do with underlying data
# In Chicago, O'Hare is a valid missing. However, others shouldn't be.
# /*\ It may be desirable to filter these maps to a sub-state geography because,
# at the state level, more dense areas are simultaneously often those with higher
# poverty values, and also areas that won't show up clearly on a state-wide map
my_dt <- tractShp_pov #%>% filter(str_detect(GEOID, "17031"))

map_sae_components(my_dt, "acs1_pov_05",      "", val_limits = limits_05, save_label = "Poverty (ACS1), age 0-5")
map_sae_components(my_dt, "acs5_pov",         "", val_limits = limits_05, save_label = "Poverty (ACS5), age 0-5")
map_sae_components(my_dt, "sae_pov_model_05", "", val_limits = limits_05, save_label = "Poverty (SAE), age 0-5")

```

```{r build comparison of selected SAE with ACS1, eval = developer_mode}
# Build 
(puma_agg_sae <- 
  sae_results_ccdf_wk_pov_05$sae_out %>% 
   as.data.table() %>%
  .[j = PUMA := as.numeric(PUMA)] %>% 
  .[str_detect(vc_value, "^WorkElig_(0%|75%|150%).+"),
    .(n_p = sum(n_pt),
      n_p_elig    = sum(vc_count),
      n_p_elig_fh    = sum(vc_fh_count_trunc),
      n_p_elig_model = sum(vc_model_count_trunc)),
    by = PUMA] %>% 
  .[j = `:=`(pct_elig       = n_p_elig       / n_p,
             pct_elig_fh    = n_p_elig_fh    / n_p,
             pct_elig_model = n_p_elig_model / n_p)] %>% 
   arrange(PUMA) %>% 
  select(PUMA, n_sae = n_p, 
         n_ccap_elig_fh = n_p_elig_fh, 
         n_ccap_elig_model = n_p_elig_model,
         pct_ccap_elig       = pct_elig,
         pct_ccap_elig_fh    = pct_elig_fh, 
         pct_ccap_elig_model = pct_elig_model))
  # aggregate counts across vc_values and puma
  # compare with puma aggregate calcs

(puma_agg_acs1 <- 
   acs1_elig[between(AGEP, 0, 5),
              .(sample_n = .N,
                n_acs1 = sum(PWGTP),
                  n_lt225fpl         = sum(PWGTP[fam_incpov_ratio <= 2.25]),
                pct_lt225fpl         = sum(PWGTP[fam_incpov_ratio <= 2.25]) / sum(PWGTP),
                  n_lt225fpl_worksch = sum(PWGTP[fam_incpov_ratio <= 2.25 & bAdults_all_workThresh_sch == 1]),
                pct_lt225fpl_worksch = sum(PWGTP[fam_incpov_ratio <= 2.25 & bAdults_all_workThresh_sch == 1]) / sum(PWGTP)),
              by = .(PUMA = as.numeric(PUMA))] %>% 
   arrange(PUMA))

puma_agg_comp <- 
  merge(puma_agg_acs1,
        puma_agg_sae,
        by = "PUMA")
```


```{r visualize comparison of selected SAE with ACS1, eval = developer_mode}
# Compare counts
plot_puma_aggs_ns <- 
  ggplot(puma_agg_comp,
       aes(x = n_lt225fpl_worksch,
           group = PUMA)) +
  geom_point(aes(y = n_ccap_elig_fh),
             color = "blue") +
  geom_point(aes(y = n_ccap_elig_model),
             color = "green") +
  geom_point(data = puma_agg_comp %>% filter(PUMA == 02100),
             aes(y = n_ccap_elig_fh),
             color = "orange") +
  geom_point(data = puma_agg_comp %>% filter(PUMA == 02100),
             aes(y = n_ccap_elig_model),
             color = "red") +
  geom_abline() +
  scale_x_continuous(limits = c(0, NA)) +
  scale_y_continuous(limits = c(0, NA)) +
  theme_minimal()

ggplotly(plot_puma_aggs_ns, tooltip = "group")

# Compare shares
plot_puma_aggs_pcts <- 
  ggplot(puma_agg_comp,
       aes(x = pct_lt225fpl_worksch,
           group = PUMA)) +
  geom_point(aes(y = pct_ccap_elig),
             color = "black") +
  geom_point(aes(y = pct_ccap_elig_fh),
             color = "blue") +
  geom_point(aes(y = pct_ccap_elig_model),
             color = "green") +
  geom_point(data = puma_agg_comp %>% filter(PUMA == 02100),
             aes(y = pct_ccap_elig_fh),
             color = "orange") +
  geom_point(data = puma_agg_comp %>% filter(PUMA == 02100),
             aes(y = pct_ccap_elig_model),
             color = "red") +
  geom_abline() +
  scale_x_continuous(limits = c(0, NA)) +
  scale_y_continuous(limits = c(0, NA)) +
  theme_minimal()

ggplotly(plot_puma_aggs_pcts, tooltip = "group")

```


```{r check consistency of base population measures, eval = developer_mode}
# /!\ Consider moving this to 01e if it's interesting

puma_agg_pop <- 
  pop_by_age %>% 
  rename(GEOID = GEOID_TR20) %>% 
  merge(geo_crosswalk[j = .(GEOID, PUMA = as.numeric(PUMA))] %>% unique(),
        by = "GEOID") %>% 
  as.data.table() %>% 
  .[year == base_year,
    j = .(n_pop = sum(age_0to5_count)),
    by = PUMA] %>% 
  arrange(PUMA)

puma_agg_comp_pop <- 
  puma_agg_comp %>% 
  merge(puma_agg_pop,
        by = "PUMA")

plot_puma_pops <- 
  ggplot(puma_agg_comp_pop,
         aes(x = n_acs1,
             y = n_pop,
             group = PUMA)) +
  geom_point() + 
  geom_point(data = puma_agg_comp_pop %>% filter(PUMA == "02100"),
             color = "red") + 
  geom_abline() +
  scale_x_continuous(limits = c(0, NA)) +
  scale_y_continuous(limits = c(0, NA)) +
  theme_minimal()


ggplotly(plot_puma_pops, tooltip = "group")
```

```{r investigate the amount of noise in the ACS1 sample}
# The counts of young children (age 0-5) are very low
acs1_elig[between(AGEP, 0, 5), 
           .N, 
           by = PUMA] %>% 
  .[order(PUMA)] %>% 
  ggplot(aes(x = N)) + 
  geom_histogram() +
  labs(title = "")

# Bootstrapping values for each PUMA
```

