
<!-- This .Rmd file is set up to run either independently by checking for 
the presence of necessary objects in the global environment and running 
related scripts if not, or also as a child to the "main-doc". For that latter
reason, comments and headings that are not relevant to a final report to
pubic audiences are suppressed or moved to code chunks that can optionally be 
`echo`ed as desired. -->

```{r}
# set flags for running this script
print_documentation <- FALSE
```

```{r}
# run scripts for necessary packages and objects as necessary
if (!"meanNA"        %in% objects()) source("settings--main.R", echo = FALSE)
if (!"my_state_abbr" %in% objects()) source("method--read-customization-file.R", echo = FALSE)
if (!"bin_age"       %in% objects()) source("method--general-helper-functions.R", echo = FALSE)

load(glue("{output_path}geo_data_{my_output_tag}.Rda"))

source("method--pull-and-process-acs5.R")

```

# Pull and Merge ACS5 Tables for Auxiliary Predictions in the SAE

```{r}

if (!exists("my_county_fip")) {
  county_arg <- NULL
} else {
  county_arg <- my_county_fip
}

pull_my_table <- 
  function(
    my_table) {
    pull_table(
      my_table,
      state = my_state_abbr, 
      county = county_arg,
      year = acs5_year,
      use_url_pull = TRUE,
      key = census_key
    )
  }
```


## Total Population

```{r}
acs5_pop_pull <- pull_my_table("B01003")
    
inspect_fields(
  acs5_pop_pull, 
  show_all_combos = TRUE
)

acs5_pop <- 
  acs5_pop_pull %>% 
  select(
    GEOID,
    tot_pop    = estimate,
    tot_pop_se = se
  )

```


## Sex by Age

```{r}
acs5_sex_by_age_pull <- pull_my_table("B01001")
    
inspect_fields(
  acs5_sex_by_age_pull, 
  show_all_combos = FALSE
)

acs5_pop_by_age <- 
  acs5_sex_by_age_pull %>% 
  filter(
    !str_detect(age, "All")
  ) %>% 
  construct_fields(
    numerator = "age"
  )
```


```{r split ages 18 to 19 and add to existing population pull}
# Split the age18to19 group in half
acs5_pop_by_age_split1819 <- 
  acs5_sex_by_age_pull %>% 
  filter(
    age == "Age18to19"
  ) %>% 
  mutate(
    estimate = estimate / 2,
    moe      =      moe / 2,
    se       =       se / 2
  )

acs5_pop_by_age_split1819 <- 
  bind_rows(
    acs5_pop_by_age_split1819 %>% mutate(age = "Age18"),
    acs5_pop_by_age_split1819 %>% mutate(age = "Age19")
  )

stopifnot(
  all(
    with(
      acs5_pop_by_age_split1819,
      estimate[age == "Age18"] == estimate[age == "Age19"]
    )
  )
)

# Add these values to the existing data
acs5_pop_by_age_aug <- 
  bind_rows(
    acs5_sex_by_age_pull,
    acs5_pop_by_age_split1819
  )
  
# Check that this is as expected
if (FALSE) {
  acs5_pop_by_age_custom %>% 
    filter(
      GEOID == GEOID[1]
    ) %>% 
    filter(
      age %in% c("Age18to19", "Age18", "Age19")
    )  
}
```


```{r build custom aggregations of ages}
# Examine range of ages in naturally sorted order
if (FALSE) {
  sort(sort_by_char_nums(acs5_pop_by_age_aug$age %>% unique())) %>% as.character()  
}

# Add key population ranges
acs5_pop_by_age_custom <- 
  acs5_pop_by_age_aug %>% 
  mutate(
    age_agg = 
      case_when(
        age %in% c("Age0to5",   "Age5to9",   "Age10to14", "Age15to17", "Age18to19") ~ "Age0to19",
        age %in% c("Age20to20", "Age21to21", "Age22to24", "Age25to29", "Age30to34", 
                   "Age35to39", "Age40to44", "Age45to49", "Age50to54", "Age55to59", 
                   "Age60to61", "Age62to64")                                        ~ "Age20to64",
        age %in% c("Age65to66", "Age67to69", "Age70to74", "Age75to79", "Age80to85", 
                   "Age85to85")                                                     ~ "Age65plus"
      )
    ) %>% 
  filter(
    age_agg %in% c("Age0to19", "Age20to64", "Age65plus")
  )

if (FALSE) {
  acs5_pop_by_age_custom %>% 
    select(age, age_agg) %>% 
    mutate(
      age = sort_by_char_nums(age)
    ) %>% 
    unique() %>% 
    arrange(age)
}


acs5_pop_by_age_agg <- 
  acs5_pop_by_age_custom %>% 
  construct_fields(
    numerator = "age_agg"
  )
```


## Population Under 18 Years of Age

```{r}

acs5_pop_lt18_pull <- pull_my_table("B09001")
    
inspect_fields(
  acs5_pop_lt18_pull, 
  show_all_combos = TRUE
)

acs5_pop_by_age_lt18 <- 
  acs5_pop_lt18_pull %>% 
  filter(
    !str_detect(age, "All"),
    residence_type != "InGQ"
  ) %>% 
  construct_fields(
    numerator = "age"
  )

```


## Poverty Status in Past 12 Months by Sex by Age

```{r}
acs5_pov_bySexAge_pull <- pull_my_table("B17001")
    
inspect_fields(
  acs5_pov_bySexAge_pull, 
  show_all_combos = TRUE
)

acs5_pov_bySexAge <- 
  acs5_pov_bySexAge_pull %>% 
  filter(
    !str_detect(age, "All")
  ) %>% 
  construct_fields(
    numerator = "pov_status",
    by_vars = c("sex", "age")
  )

# Check
acs5_pov_bySexAge %>% 
  select(matches("^r.+Female_Age0to5")) %>% 
  head()

```


## Poverty status in Past 12 Months by Household Type by Number of Related Children Under 18

```{r}

acs5_pov_byNumKids_pull <- pull_my_table("B17012")

inspect_fields(
  acs5_pov_byNumKids_pull, 
  show_all_combos = TRUE
)

acs5_hhtype <- 
  acs5_pov_byNumKids_pull %>% 
  filter(
     str_detect(own_kids_under18, "All"),
    !str_detect(pov_status, "All"),
    !str_detect(family_type, "All|Unmarried")
  ) %>% 
  construct_fields(
    numerator = "family_type"
  )

```


## Age by Ratio of Income to Poverty

```{r}
acs5_incpov_byage_pull <- pull_my_table("B17024")
    
inspect_fields(
  acs5_incpov_byage_pull, 
  show_all_combos = TRUE
)

### Build age and poverty categories as close to the ACS1 income and age 
# partitions as possible

# Aggregate ages, and income to a key partition of c(0, 0.75, 1.30, 2.00, 4.00)),
# which aligns with our targets to include specific policy targets of
# 130, 138, and 205 (or at least nearby values)
acs5_incpov_byage_prep <- 
  acs5_incpov_byage_pull %>% 
  filter(
    !str_detect(age, "All"),
    !str_detect(inc_to_pov_ratio, "All")
  ) %>% 
  mutate(
    age_agg =
      case_when(
        str_detect(age, "Age(0to|6to|12to)")     ~ "Age0to17",
        str_detect(age, "Age(18|25|35|45|55)to") ~ "Age18to64",
        str_detect(age, "Age(65|75)to")          ~ "AgeGe65",
        TRUE                                     ~ NA
      ),
    inc_to_pov_ratio_agg = 
      case_when(
        str_detect(inc_to_pov_ratio, "IncPov(0to|50to)")                ~ "IncPov0to75", 
        str_detect(inc_to_pov_ratio, "IncPov(75to|100)")                ~ "IncPov75to125",
        str_detect(inc_to_pov_ratio, "IncPov(125to|150to|175to|185to)") ~ "IncPov125to200",
        str_detect(inc_to_pov_ratio, "IncPov(200to|300to)")             ~ "IncPov200to400",
        str_detect(inc_to_pov_ratio, "IncPov(400to|500plus)")           ~ "IncPov400plus"
      )
  )

# Examine output mappings
acs5_incpov_byage_prep %>% 
  select(age, age_agg) %>% 
  unique() %>% 
  mutate(age = sort_by_char_nums(age)) %>% 
  arrange(age)

acs5_incpov_byage_prep %>% 
  select(inc_to_pov_ratio, inc_to_pov_ratio_agg) %>% 
  unique() %>% 
  mutate(inc_to_pov_ratio = sort_by_char_nums(inc_to_pov_ratio)) %>% 
  arrange(inc_to_pov_ratio)

# produce estimates
acs5_incpov_byage <- 
  acs5_incpov_byage_prep %>% 
  construct_fields(
    numerator = "inc_to_pov_ratio_agg",
    by_vars = "age_agg"
  )
```


## Ratio of Income to Poverty Level of Families in the Last 12 Months

```{r}

acs5_incpov_fam_pull <- pull_my_table("B17026")
    
inspect_fields(
  acs5_incpov_fam_pull, 
  show_all_combos = TRUE
)

acs5_incpov_byage <- 
  acs5_incpov_fam_pull %>% 
  filter(
    !str_detect(inc_to_pov_ratio, "All")
  ) %>% 
  construct_fields(
    numerator = "inc_to_pov_ratio"
  )

# Create an alternate partition
acs5_incpov_byage <- 
  acs5_incpov_fam_pull %>% 
  filter(
    str_detect(inc_to_pov_ratio, "All")
  )

```

## Hispanic or Latino Origin by Race

```{r}
acs5_raceeth_pull <- pull_my_table("B03002")
    
inspect_fields(
  acs5_raceeth_pull, 
  show_all_combos = TRUE
)

acs5_raceeth4 <- 
  acs5_raceeth_pull %>% 
  filter(
    !str_detect(race, "All"),
    hispanic != "Hisp"
  ) %>% 
  mutate(
    raceeth4 = 
      case_when(
        hispanic == "Hisp" ~ "Hisp",
        race     == "Wh"   ~ "White",
        race     == "Aa"   ~ "Black",
        TRUE               ~ "Other"
      )
  ) %>% 
  construct_fields(
    numerator = "raceeth4"
  )


```

<!-- ## Sex of Workers by Means of Transportation to Work -->

<!-- ```{r} -->
<!-- B08006 -->
<!-- ``` -->

<!-- ## Aggregate travel time to work of Workers by Sex -->

<!-- ```{r} -->
<!-- B08013 -->
<!-- ``` -->

<!-- ## Grandparents Living with Own Grandchildren Under 18 by Responsibility for Own Grandchildren by Presence of Parent of Grandchildren and Age of Grandparent -->

<!-- ```{r} -->
<!-- B10051 -->
<!-- ``` -->

<!-- ## Households with grandparent living with own grandchildren under 18 years by responsibility for own grandchildren by presence of grandchildren and presence of parent of grandchildren -->

<!-- ```{r} -->
<!-- B10063  -->
<!-- ``` -->


## Sex by Age by Employment Status for the Population 16 and Over

```{r}
acs5_empl_pull <- pull_my_table("B23001")
    
inspect_fields(
  acs5_empl_pull, 
  show_all_combos = TRUE
)

acs5_empl_prep_Age22to64 <- 
  acs5_empl_pull %>% 
  filter(
    !str_detect(sex, "All"),
    str_detect(age, "Age(22|25|30|35|45|55|60|62)to")
  )

acs5_empl <- 
  acs5_empl_prep_Age22to64 %>% 
  filter(
    lfp == "InLF",
    pop == "Civilian",
    !str_detect(status, "All")
  ) %>% 
  construct_fields(
    numerator = "status", 
    by_vars = c("sex")
  ) %>% 
  select(
    -matches("Unempl")
  )

acs5_empl_inclMilit <- 
  acs5_empl_prep_Age22to64 %>% 
  mutate(
    status = if_else(pop == "Military", "Empl", status),
    status = 
      case_match(
        status, 
        "Empl" ~ "EmplInclMilit", 
        .default = status
      )
  ) %>% 
  filter(
    lfp == "InLF",
    pop %in% c("Civilian", "Military"),
    !str_detect(status, "All")
  ) %>% 
  construct_fields(
    numerator = "status", 
    by_vars = c("sex")
  ) %>% 
  select(
    -matches("Unempl")
  )

acs5_lfrate <- 
  acs5_empl_prep_Age22to64 %>% 
  filter(
    (lfp == "InLF" & pop == "Civilian") |
    (lfp == "NotInLF"),
    status == "All"
  ) %>% 
  select(
    -pop, -status
  ) %>% 
  construct_fields(
    numerator = "lfp", 
    by_vars = c("sex")
  )

acs5_lfrate_inclMilit <- 
  acs5_empl_prep_Age22to64 %>% 
  filter(
    !str_detect(lfp, "All"),
    str_detect(pop, "All")
  ) %>%
  mutate(
    lfp = 
      case_match(
        lfp,
        "InLF" ~ "InLFOrMilit",
        "NotInLF" ~ "NotInLFOrMilit"
      )
  ) %>% 
  construct_fields(
    numerator = "lfp", 
    by_vars = c("sex")
  ) %>% 
  select(
    -matches("NotIn")
  )

```

## Sex by Educational Attainment for Population 25 Years and Older

```{r}
acs5_edattain_pull <- pull_my_table("B15002")
    
inspect_fields(
  acs5_edattain_pull, 
  show_all_combos = TRUE
)

acs5_edattain_bySex <- 
  acs5_edattain_pull %>% 
  filter(
    !str_detect(sex, "All")
  ) %>% 
  construct_fields(
    numerator = "ed_attain",
    by_vars = "sex"
  )

acs5_edattain <- 
  acs5_edattain_pull %>% 
  filter(
    !str_detect(sex, "All")
  ) %>% 
  construct_fields(
    numerator = "ed_attain"
  )

```

## Build All-Adults-Employed Status for Households, both Overall and Those with Kids

<!-- Note: the complex hierarchy of this table makes it worth being highly deliberate  -->
<!-- with calculations rather than seeking complex implementations of `construct_fields()` -->

```{r identify the denominator for all-adults-working status}
acs5_famconfig_wKids_raw <- pull_my_table("B23007")

inspect_fields(acs5_famconfig_wKids_raw)
inspect_fields(acs5_famconfig_wKids_raw, show_all_combos = TRUE)

# Calculating work eligibility by hand
acs5_workelig_withKids_denom <- 
  acs5_famconfig_wKids_raw %>% 
  filter(
    own_kids_under18 == "SomeKidsUnder18",
    family_type %in% c("Married", "UnmarriedMaleHh", "UnmarriedFemaleHh"),
    lfp == "All",
    status == "All"
  )

acs5_workelig_all_denom <- 
  acs5_famconfig_wKids_raw %>% 
  filter(
    !str_detect(own_kids_under18, "All"),
    family_type %in% c("Married", "UnmarriedMaleHh", "UnmarriedFemaleHh"),
    str_detect(lfp, "All"),
    str_detect(status, "All")
  )

# Ensure we have isolated the desired conditions
if (FALSE) {
  inspect_fields(acs5_workelig_withKids_denom, show_all_combos = TRUE)  
  inspect_fields(acs5_workelig_all_denom, show_all_combos = TRUE)  
}
```


```{r identify the numerators for all-adults-working status}
acs5_workelig_withKids_num <- 
  acs5_famconfig_wKids_raw %>% 
  filter(
    own_kids_under18 == "SomeKidsUnder18",
    (family_type == "Married" & status == "HusbandEmplWifeEmpl") | 
      (str_detect(family_type, "Unmarried") & status == "Empl")
  )

acs5_workelig_all_num <- 
  acs5_famconfig_wKids_raw %>% 
  filter(
    !str_detect(own_kids_under18, "All"),
    (family_type == "Married" & status == "HusbandEmplWifeEmpl") | 
      (str_detect(family_type, "Unmarried") & status == "Empl")
  )

# Ensure we have isolated the desired conditions
if (FALSE) {
  inspect_fields(acs5_workelig_withKids_num, show_all_combos = TRUE)  
}
```


```{r construct desired work eligibility field}
acs5_workelig <- 
  merge(
    acs5_workelig_withKids_num   %>% summarize(nEmpl_allHhs   = sum(estimate), .by = GEOID),
    acs5_workelig_withKids_denom %>% summarize(nAll_allHhs    = sum(estimate), .by = GEOID), by = "GEOID") %>% 
  merge(
    acs5_workelig_withKids_num   %>% summarize(nEmpl_withKids = sum(estimate), .by = GEOID), by = "GEOID") %>% 
  merge(
    acs5_workelig_withKids_denom %>% summarize(nAll_withKids  = sum(estimate), .by = GEOID), by = "GEOID") %>% 
  mutate(
    rAllAdultsEmpl_allHhs   = nEmpl_allHhs   / nAll_allHhs,
    rAllAdultsEmpl_withKids = nEmpl_withKids / nAll_withKids,
    nAllAdultsEmpl_allHhs   = nEmpl_allHhs,
    nAllAdultsEmpl_withKids = nEmpl_withKids,
    nAllAdultsEmpl_withKids = nAll_allHhs,
    nAllAdultsEmpl_withKids = nAll_withKids
  )

```


## Build Constructions of Veteran Status

```{r pull; inspect; and build constructions for veteran status}
acs5_vetstatus_bySexAge_raw <- pull_my_table("B21001")

inspect_fields(acs5_vetstatus_bySexAge_raw, show_all_combos = TRUE)

acs5_vetstatus <- 
  construct_fields(
    df = acs5_vetstatus_bySexAge_raw,
    numerator = "vet_status",
    subset_cond = "age %in% c('Age18to34', 'Age35to54', 'Age55to64')",
    subset_descr = "")

```

## Build Constructions of Disability Status

```{r pull; inspect; and build constructions for disability}
acs5_disab_bySexAge_raw <- pull_my_table("B18101")

inspect_fields(acs5_disab_bySexAge_raw, show_all_combos = TRUE)

acs5_disab <- 
  construct_fields(
    df = acs5_disab_bySexAge_raw,
    numerator = "disab_status",
    subset_cond = "age %in% c('Age18to34')", # , 'Age35to64'
    subset_descr = "")


```

# Build Constructions of Health Insurance Status

```{r pull; inspect; and build constructions for health insurance}
acs5_healthins_bySexAge_raw <- pull_my_table("B27001")

inspect_fields(acs5_healthins_bySexAge_raw, show_all_combos = TRUE)

acs5_healthins <- 
  construct_fields(
    df = acs5_healthins_bySexAge_raw,
    numerator = "health_ins_cov",
    subset_cond = "age %in% c('Age18to34', 'Age35to54', 'Age55to64')",
    subset_descr = "")


```


## Collect Results

```{r collect}
acs5_tomerge <- 
  list(
    acs5_pop_by_age, 
    acs5_pop_by_age_agg,
    #acs5_pop_by_age_lt18, # This includes duplicates to acs5_pop_by_age. Is left out until needed.
    #acs5_pov_bySexAge, 
    acs5_incpov_byage, 
    acs5_raceeth4, 
    acs5_hhtype,
    acs5_empl, 
    acs5_empl_inclMilit,
    acs5_lfrate, 
    acs5_lfrate_inclMilit, 
    acs5_edattain,
    acs5_edattain_bySex,
    acs5_workelig,
    acs5_vetstatus, 
    acs5_disab, 
    acs5_healthins
  )

# Retain only rate and std err of rate calculations
acs5_tomerge <- lapply(acs5_tomerge, \(x) select(x, matches("GEOID|^(r|se_r|w|n)")))

merge_reduce <- function(x, y) merge(x, y, by = "GEOID")

acs5tract <- Reduce(merge_reduce, acs5_tomerge)
```

```{r}
save(
  acs5tract,
  file = glue("{output_path}acs5_data_{my_output_tag}.Rda")
)
```

## Examine Maps of Selected ACS5 Measures

```{r map building code}
make_acs5_map <- function(my_dat, my_field, my_label, use_aux = TRUE) {
  
  if (use_aux) {
    myShp <- auxShp
  } else {
    myShp <- tractShp
  }
  
  bbox <- sf::st_bbox(myShp) 
  
  geo_data <- 
    tractShp %>% 
    merge(
      my_dat %>% select(all_of(c("GEOID", my_field))) %>% filter(get(my_field) < 1),
      by = c("GEOID")
    )
  
  base_plot <- 
    geo_data %>% 
    ggplot() +
    geom_sf(
      aes(
        fill = get(my_field)
      )
    )
  
  if (use_aux) {
    base_plot <- 
      base_plot + 
      geom_sf(
        data = auxShp,
        color = "white",
        fill = NA,
        linewidth = 1
      )
  }
  
  base_plot + 
    geom_sf(
      data = pumaShp,
      color = "orange",
      fill = NA,
      linewidth = 1
    ) +
    scale_fill_continuous(
      name = "",
      label = percent
    ) +
    labs(
      title = my_label
    ) +
    theme(
      plot.title = element_text(hjust = 0.5)
    ) +
    theme_void() +
    coord_sf(
      xlim = c(bbox["xmin"], bbox["xmax"]),
      ylim = c(bbox["ymin"], bbox["ymax"]),
      expand = FALSE
    )

}

make_acs5_map(acs5tract,      "rIncPov0to75_Age18to64",   "% < 75% FPL")
make_acs5_map(acs5tract,      "rIncPov400plus_Age18to64", "% over 400% FPL")

make_acs5_map(acs5tract,      "rEdLtHs", "% Less than HS Degree")
make_acs5_map(acs5tract,      "rEdColl", "% College Educated")

# make_acs5_map(acs5tract,      "raceeth_wh_nonh_est",    "% White (non-Hispanic)")
# make_acs5_map(acs5tract,      "raceeth_bl_nonh_est",    "% Black (non-Hispanic)")
# make_acs5_map(acs5tract,      "raceeth_h_est",          "% Hispanic")
# make_acs5_map(acs5tract,      "raceeth_amind_nonh_est", "% American Indian")

make_acs5_map(acs5_vetstatus, "rVet",         "% Veterans")
make_acs5_map(acs5_disab,     "rDisab",       "% Disabled")
make_acs5_map(acs5_healthins, "rNoHealthIns", "% Without Health Insurance")

```



